---
title: ""
author: ''
date: ""
classoption: twoside
output: 
  pdf_document:
    latex_engine: xelatex
    fig_height: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE, warning=FALSE, message=FALSE) #show only results
source("/Users/linlizhou/Documents/Rprojects/IR-Projects/theme_source.R") #run code from saved theme and library
```

```{r load survey data}
#read fis.origional (download from alchemer)
fis.original<-read_csv("/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Surveys/Lasell Internal/First Impressions/2022 Fall/20221013124928-SurveyExport.csv")

#look at the survey instruction using lapply(fis.s, unique)
#rename cols
fis.s<-fis.s%>%rename(
  RCstatus=`Which of the following describes your status for the 2022 fall semester?`,
#satisfaction 0-6 scale  
  satis.activity=`Campus-wide programs and activities (virtual or in-person)?:Please tell us how satisfied you are with…`,
  satis.activity.cm=`Comment or example::Please tell us how satisfied you are with…...58`,
  
  satis.overallcourse=`Your courses overall so far?:Please tell us how satisfied you are with…`,
  satis.majorcourse=`Your courses within your major so far? (If you are an undeclared major, please leave blank):Please tell us how satisfied you are with…`,
  satis.course.cm=`Comment or example::Please tell us how satisfied you are with…...61`,
  
  satis.acchallenge=`The degree of academic challenge in your courses?:Please tell us how satisfied you are with…`,
  satis.acchallenge.cm=`Comment or example::Please tell us how satisfied you are with…...63`,

  satis.accommit=`Other students' commitment to their studies?:Please tell us how satisfied you are with…`,
  satis.accommit.cm=`Comment or example::Please tell us how satisfied you are with…...65`,
  
  satis.foodav=`Food service availability on campus?:Please tell us how satisfied you are with…`,
  satis.foodav.cm=`Comment or example::Please tell us how satisfied you are with…...67`,
  
  satis.residstaff=`Residential Life staff?:Please tell us how satisfied you are with…`,
  satis.residstaff.cm=`Comment or example::Please tell us how satisfied you are with…...69`,
  
  satis.residhall=`Your living situation in the residence halls?:Please tell us how satisfied you are with…`,
  satis.residhall.cm=`Comment or example::Please tell us how satisfied you are with…...71`,

#connection 0-6 scale  
  connect.faculty=`Faculty?:How connected do you feel to…`,
  connect.faculty.cm=`Comment or example::How connected do you feel to…...73`,
  
  connect.stu=`Other students?:How connected do you feel to…`,
  connect.stu.cm=`Comment or example::How connected do you feel to…...75`,

#emphasis question: 4 text scale  
  emphasize.acsupport=`Using learning support services (tutoring services, writing center, etc):Based on your experience so far, how much does Lasell University emphasize the following?`,
  emphasize.socoppo=`Providing opportunities to be involved socially:Based on your experience so far, how much does Lasell University emphasize the following?`,
  emphasize.campactivity=`Attending campus activities and events (virtual or in-person):Based on your experience so far, how much does Lasell University emphasize the following?`,
  emphasize.issueevents=`Attending events that address important social, economic, or political issues:Based on your experience so far, how much does Lasell University emphasize the following?`,

#satisfaction 0-6 scale
  service.aac=`Academic Achievement Center:Please tell us how satisfied you are with…`,
  service.aac.cm=`Comment or Example::Please tell us how satisfied you are with…...81`,

  service.classtech=`Classroom Technology and Computer Labs:Please tell us how satisfied you are with…`,
  service.classtech.cm=`Comment or Example::Please tell us how satisfied you are with…...83`,

  service.counseling=`Counseling Center (Located at 18 Maple Terrace):Please tell us how satisfied you are with…`,
  service.counseling.cm=`Comment or Example::Please tell us how satisfied you are with…...85`,

  service.acadvisor=`Your academic advisor:Please tell us how satisfied you are with…`,
  service.acadvisor.cm=`Comment or Example::Please tell us how satisfied you are with…...87`,

  service.health=`Health Services (Located in Edwards Student Center):Please tell us how satisfied you are with…`,
  service.health.cm=`Comment or Example::Please tell us how satisfied you are with…...89`,

  service.techhelp=`Technology Help Desk:Please tell us how satisfied you are with…`,
  service.techhelp.cm=`Comment or Example::Please tell us how satisfied you are with…...91`,

  service.shuttle=`Lasell Shuttle:Please tell us how satisfied you are with…`,
  service.shuttle.cm=`Comment or Example::Please tell us how satisfied you are with…...93`,

  service.other=`Please type the service(s) in to the box (i.e. vending, mailroom, washing/drying etc.):Please provide feedback on any other services on campus we have not mentioned in the previous questions.`,
  service.other.cm=`Feedback::Please provide feedback on any other services on campus we have not mentioned in the previous questions.`,

#academic 0-6 scale
  meetacexpect=`Is the college meeting your expectations in terms of academic experience?:Please tell us a little bit about what you think of Lasell's academics.`,
  meetacexpect.cm=`Comment or example::Please tell us a little bit about what you think of Lasell's academics.`,

  faculty.orgmaterial=`Present material in a well-organized way?:How often do your faculty…`,
  faculty.explain=`Make good use of examples and illustrations to explain difficult points?:How often do your faculty…`,
  faculty.prep=`Come to class well prepared?:How often do your faculty…`,
  faculty.command=`Have a good command of what they are teaching?:How often do your faculty…`,

#outside class 0-6 agreement
  interact.outside=`I have had a positive interaction with at least one Lasell faculty or staff member outside of class.:How much do you agree…`,
  interact.cm=`How have you been able to effectively interact with others in the Lasell community in a safe manner so far this semester?`,
  interact.difficulty=`What are the difficulties you’re facing when interacting with others within the Lasell community this semester?`)

#write.xlsx(fis.s,"/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Surveys/Lasell Internal/First Impressions/2022 Fall/raw_renamed.xlsx")
```



# 2022 First Impression Survey

# Satisfaction
```{r create satis figure}
#satis.4: satis.acchallenge, satis.accommit, satis.majorcourse, satis.overallcourse
satis.aca.figure<-prtdf%>%filter(item%in%c("satis.overallcourse","satis.majorcourse", "satis.acchallenge", "satis.accommit"),year>2019)%>%
  group_by(item,year,prt)%>%summarise(cnt=n())%>%
  
  ggplot(aes(y = prt, x=year, fill=year ))+
  geom_bar(stat="identity",position = position_dodge(),width=0.9)+
  scale_fill_manual(values = c("Grey","Grey70","#69b3e7"))+
  labs(title=str_wrap("",40),x="",y="",fill="") +
  theme_lz()+
 # theme(legend.position = "top",plot.margin=unit(c(1.5,1,1,-1),"cm"))+
  geom_text(aes(label= ifelse(year==2022,as.character(round(prt,2)),"")),
            size=3,vjust=1.5,fontface="bold",position = position_dodge(0.9))+
  geom_text(aes(label= ifelse(year!=2022,as.character(round(prt,2)),"")),
            size=3,vjust=1.5,color="#6C6F70",fontface="bold",position = position_dodge(0.9))+
  
  facet_wrap(~factor(item,levels =c("satis.overallcourse","satis.majorcourse", "satis.acchallenge", "satis.accommit"),labels = c(str_wrap("Overall Courses",10),
                             str_wrap("Major Courses",10),
                             str_wrap("Academic Challenge",10),
                             str_wrap("Academic Commitment",10))),nrow=1,
             strip.position="bottom") +
  geom_line(aes(y = prt, x=year, group=item, 
                color=factor(item,levels =c("satis.overallcourse","satis.majorcourse", "satis.acchallenge", "satis.accommit")), 
                linetype=factor(item,levels =c("satis.overallcourse","satis.majorcourse", "satis.acchallenge", "satis.accommit"))),
            stat="identity", show.legend = F)+#
  scale_color_manual(name="",values=c("#6C6F70","#6C6F70","#6C6F70","#6C6F70"))+
  scale_linetype_manual(name="",values=c("dashed","dashed","dashed","dashed"))

#satis.4: satis.activity, satis.foodav, satis.residhall, satis.residstaff
satis.life.figure<-prtdf%>%filter(item%in%c("satis.activity", "satis.foodav", "satis.residstaff", "satis.residhall"),year>2019)%>%
  group_by(item,year,prt)%>%summarise(cnt=n())%>%
  
  ggplot(aes(y = prt, x=year, fill=year ))+
  geom_bar(stat="identity",position = position_dodge(),width=0.9)+
  scale_fill_manual(values = c("Grey","Grey70","#69b3e7"))+
  labs(title=str_wrap("",40),x="",y="",fill="") +
  theme_lz()+#theme(legend.position = "none")+
  geom_text(aes(label= ifelse(year==2022&prt>.8,as.character(round(prt,2)),"")),
            size=3,vjust=1.5,fontface="bold",position = position_dodge(0.9))+
  geom_text(aes(label= ifelse(year==2022&prt<.8,as.character(round(prt,2)),"")),
            size=3,color="#641F45",vjust=1.5,fontface="bold",position = position_dodge(0.9))+
  geom_text(aes(label= ifelse(year!=2022,as.character(round(prt,2)),"")),
            size=3,vjust=1.5,color="#6C6F70",fontface="bold",position = position_dodge(0.9))+
  
  facet_wrap(~factor(item,levels =c("satis.activity", "satis.foodav", "satis.residstaff", "satis.residhall"),labels = c(str_wrap("Campus Activity",10),
                             str_wrap("Food Availability",10),
                             str_wrap("Residential Staff",10),
                             str_wrap("Residence Hall",10))),nrow=1, strip.position="bottom") +
  geom_line(aes(y = prt, x=year, group=item, 
                color=factor(item,levels =c("satis.activity", "satis.foodav", "satis.residstaff", "satis.residhall")), 
                linetype=factor(item,levels =c("satis.activity", "satis.foodav", "satis.residstaff", "satis.residhall"))),
            stat="identity", show.legend = F)+#
  scale_color_manual(name="",values=c("#6C6F70","#6C6F70","#6C6F70","#6C6F70"))+#lightyellow#FFCB4F
  scale_linetype_manual(name="",values=c("dashed","dashed","dashed","dashed"))
```

## Academic Satisfaction

```{r display satis figure, include=TRUE}
satis.aca.figure
```

## Life Satisfaction

* An average of __82%__ first year students are satisfied with their life experiences.

* 37% first year students are __dissatisfied with food availability__. Some students hope for weekend and late night food hours.

```{r display satis.life figure, include=TRUE}
satis.life.figure
```

\newpage

# Services

```{r create service1-7.use/.satis figure}
#service.use: "service.aac.use", "service.acadvisor.use", "service.classtech.use", "service.techhelp.use","service.counseling.use", "service.health.use", "service.shuttle.use" 
service.use.figure<-prtdf%>%filter(item%in%c("service.aac.use", "service.acadvisor.use", "service.classtech.use", "service.techhelp.use","service.counseling.use", "service.health.use", "service.shuttle.use" ),year>2019)%>%
  group_by(item,year,prt)%>%summarise(cnt=n())%>%
  
  ggplot(aes(y = prt, x=year, fill=year ))+
  geom_bar(stat="identity",position = position_dodge(),width=0.9)+
  scale_fill_manual(values = c("Grey","Grey70","#69b3e7"))+
  labs(title=str_wrap("",40),x="",y="",fill="") +
  theme_lz()+
  #theme(legend.position = "top",plot.margin=unit(c(2,1,1,-1),"cm"))+
  geom_text(aes(label= ifelse(year==2022,as.character(round(prt,2)),"")),
            size=2.8,vjust=1.2,hjust=.4,fontface="bold",position = position_dodge(0.9))+
  geom_text(aes(label= ifelse(year!=2022,as.character(round(prt,2)),"")),
            size=2.8,vjust=1.2,hjust=.4,color="#6C6F70",fontface="bold",position = position_dodge(0.9))+
  
  facet_wrap(~factor(item,levels =c("service.aac.use", "service.acadvisor.use", "service.classtech.use", "service.techhelp.use","service.counseling.use", "service.health.use", "service.shuttle.use" ),
                     labels = c(str_wrap("Academic Achievement Center",10),
                                str_wrap("Academic Advisor",10),
                                str_wrap("Class Technology",10),
                                str_wrap("Tech HelpDesk",10),
                                str_wrap("Counseling Center",10),
                                str_wrap("Health Center",10),
                                str_wrap("Shuttle",10))),nrow=1,strip.position = "bottom") +
  geom_line(aes(y = prt, x=year, group=item, 
                color=factor(item,levels =c("service.aac.use", "service.acadvisor.use", "service.classtech.use", "service.techhelp.use","service.counseling.use", "service.health.use", "service.shuttle.use" )), 
                linetype=factor(item,levels =c("service.aac.use", "service.acadvisor.use", "service.classtech.use", "service.techhelp.use","service.counseling.use", "service.health.use", "service.shuttle.use" ))),
            stat="identity", show.legend = F)+#
  scale_color_manual(name="",values=c("#FFCB4F","#FFCB4F","#6C6F70","#6C6F70","#6C6F70","#641F45","#6C6F70"))+
  scale_linetype_manual(name="",values=c("solid","solid","dashed","dashed","dashed","solid","dashed"))

#service.satis:"service.aac.satis", "service.acadvisor.satis", "service.classtech.satis", "service.techhelp.satis","service.counseling.satis", "service.health.satis", "service.shuttle.satis" 
service.satis.figure<-prtdf%>%filter(item%in%c("service.aac.satis", "service.acadvisor.satis", "service.classtech.satis", "service.techhelp.satis","service.counseling.satis", "service.health.satis", "service.shuttle.satis" ),year>2019)%>%
  group_by(item,year,prt)%>%summarise(cnt=n())%>%
  
  ggplot(aes(y = prt, x=year, fill=year ))+
  geom_bar(stat="identity",position = position_dodge(),width=0.9)+
  scale_fill_manual(values = c("Grey","Grey70","#69b3e7"))+
  labs(title=str_wrap("",40),x="",y="",fill="") +
  theme_lz()+#theme(legend.position = "none",legend.direction = "vertical")+
  #theme(plot.title = element_text(hjust = 0, vjust = -1))+#,plot.margin = margin(1,0,0,0,"cm"))+
  geom_text(aes(label= ifelse(year==2022,as.character(round(prt,2)),"")),
            size=2.8,vjust=1.5,hjust=.4,fontface="bold",position = position_dodge(0.9))+
  geom_text(aes(label= ifelse(year!=2022,as.character(round(prt,2)),"")),
            size=2.8,vjust=1.5,hjust=.4,color="#6C6F70",fontface="bold",position = position_dodge(0.9))+
  
  facet_wrap(~factor(item,levels =c("service.aac.satis", "service.acadvisor.satis", "service.classtech.satis", "service.techhelp.satis","service.counseling.satis", "service.health.satis", "service.shuttle.satis" ),
                     labels = c(str_wrap("Academic Achievement Center",10),
                                str_wrap("Academic Advisor",10),
                                str_wrap("Class Technology",10),
                                str_wrap("Tech HelpDesk",10),
                                str_wrap("Counseling Center",10),
                                str_wrap("Health Center",10),
                                str_wrap("Shuttle",10))),nrow=1,strip.position = "bottom") +
  geom_line(aes(y = prt, x=year, group=item, 
                color=factor(item,levels =c("service.aac.satis", "service.acadvisor.satis", "service.classtech.satis", "service.techhelp.satis","service.counseling.satis", "service.health.satis", "service.shuttle.satis" )), 
                linetype=factor(item,levels =c("service.aac.satis", "service.acadvisor.satis", "service.classtech.satis", "service.techhelp.satis","service.counseling.satis", "service.health.satis", "service.shuttle.satis" ))),
            stat="identity", show.legend = F)+#
  scale_color_manual(name="",values=c("#6C6F70","#6C6F70","#6C6F70","#FFCB4F","#FFCB4F","#6C6F70","#6C6F70"))+
  scale_linetype_manual(name="",values=c("dashed","dashed","dashed","solid","solid","dashed","dashed"))
```

## Services Usage


```{r display service figure, include=TRUE}
service.use.figure
```


## Services Satisfaction

```{r display service.satis figure, include=TRUE}
service.satis.figure
```





```{r create faculty.connect fig}
#empashize4: "emphasize.acsupport", "emphasize.socoppo", "emphasize.campactivity", "emphasize.issueevents"
emp.figure<-prtdf%>%filter(item%in%c("emphasize.acsupport", "emphasize.socoppo", "emphasize.campactivity", "emphasize.issueevents","connect.faculty", "connect.stu"),year=="2022")%>%
  group_by(item,year,prt)%>%summarise(cnt=n())%>%
  
  ggplot(aes(x = prt, y=reorder(item,prt)))+
  geom_bar(fill="#69b3e7", stat="identity",position = position_dodge(),width=0.8)+
  labs(title=str_wrap("",40),x="",y="") +
  theme_lz()+theme(legend.position = "none",axis.text.y = element_text(),
                   plot.margin=unit(c(1,0,
                    1,0),"cm"))+
  geom_text(aes(label=if_else(prt>.8, as.character(round(prt,2)),"")),hjust=1.5,
            size=3,fontface="bold",position = position_dodge(0.9))+
  geom_text(aes(label=if_else(prt<.8, as.character(round(prt,2)),"")),hjust=1.5,
            size=3,color="#641F45",fontface="bold",position = position_dodge(0.9))+
  scale_y_discrete(labels=c("Issue-based Events","Connected to Faculty","Connected to Students","Social Opportunity","Campus Activity","Academic Support"))
  

#faculty4: "faculty.command", "faculty.explain", "faculty.orgmaterial", "faculty.prep"
faculty.figure<-prtdf%>%filter(item%in%c("faculty.command", "faculty.explain", "faculty.orgmaterial", "faculty.prep","meetacexpect","interact.outside"),year=="2022")%>%
  group_by(item,year,prt)%>%summarise(cnt=n())%>%
  
  ggplot(aes(x = prt, y=reorder(item,prt)))+
  geom_bar(fill="#69b3e7", stat="identity",position = position_dodge(),width=0.8)+
  labs(title=str_wrap("",40),x="",y="") +
  theme_lz()+theme(legend.position = "none",axis.text.y = element_text(),
                   plot.margin=unit(c(1,0,
                    1,0),"cm"))+
  geom_text(aes(label= as.character(round(prt,2))),hjust=1.2,
            size=3,fontface="bold",position = position_dodge(0.9))+
  scale_y_discrete(labels=c("Interact with Staff/Faculty Outside of Class","Meet Academic Expectation","Faculty Explain Materials Well","Faculty Command of Teaching","Faculty Well-Organized","Faculty Well-Prepared"))
```



```{r NUMERIC MEANS for survey items and SAVE fis.num}
#remove qual vars
fis.num<-fis.s[, !grepl("cm$",names(fis.s))]%>%select(Ethnicity,satis.activity:interact.outside)%>%select(-service.other)

#recode services/emphasize qual to quan/num
fis.num<-fis.num %>%mutate(
  #assign NA to "have not use" option
across(starts_with("service."),\(x) `is.na<-`(x, grepl("Have not use|Have not met with advisor", x))),
  #assign numeric to qual options
across(starts_with("emphasize"),~ case_when(. =="Very Little" ~ 1, . =="Some" ~ 2, . =="Quite a bit" ~ 3, . =="Very much" ~ 4)),
  #formart recoded vars as numeric
across(starts_with(c("emphasize.","service.")),as.numeric))

#check:lapply(fis.num, unique);
#str(fis.num)
```

```{r mutate aggregated NUMERIC MEAN}
#r aggregate items in fis.num
#aggregate satis, connect, faculty
fis.num<-fis.num%>%mutate(satis=rowSums(.[grepl("^satis.",names(.)) & !grepl(".cm$",names(.))]),
  #select[] vars based on & conditions; 
  #default: na.rm=false: one NA then NA so that only all answered are compared
  connect=rowSums(.[grepl("^connect.",names(.)) & !grepl(".cm$",names(.))]),
  emphasize=rowSums(.[grepl("^emphasize.",names(.)) & !grepl(".cm$",names(.))]),
  service=rowSums(.[grepl("^service.",names(.)) & !grepl(".cm$",names(.))]),
  faculty=rowSums(.[grepl("^faculty.",names(.)) & !grepl(".cm$",names(.))]))

#aggregate aca, life, soc
fis.num<-fis.num%>%mutate(
academic=satis.overallcourse+satis.majorcourse+satis.acchallenge+satis.accommit+emphasize.acsupport+service.aac+service.classtech+service.acadvisor+meetacexpect+faculty,
life=satis.foodav+satis.foodav+satis.residhall+service.counseling+service.health+service.techhelp+service.shuttle,
soc=satis.activity+connect+emphasize.socoppo+emphasize.campactivity+emphasize.issueevents+interact.outside)
#check: lapply(fis.num, unique)
```


```{r fis.num final touch - adding more vars}
#mutate more vars in fis.num
fis.num<-cbind(fis.num,fis.s[,c("RCstatus","gender","FT/PT","ppid")])
```


```{r cal current.num and merge historical.num SAVE numdf}

##calculate numeric means
current.num<-tibble(
faculty=round(mean(fis.num$faculty,na.rm=T)/length(fis.num[grepl("^faculty.",names(fis.num))]),digits = 2),
connect.faculty=round(mean(fis.num$connect.faculty,na.rm=T),digits = 2),
connect.stu=round(mean(fis.num$connect.stu,na.rm=T),digits = 2),
#emphasize previously only count 3 (without "emphasize.socoppo")
emphasize=round(mean(fis.num$emphasize,na.rm=T)/(length(fis.num[grepl("^emphasize.",names(fis.num))])-1),digits = 2))%>%
#transform tibble to match historical df
  mutate(year="2022")%>%
  pivot_longer(cols = c(faculty,connect.faculty,connect.stu,emphasize),names_to = "item",values_to = "prt")

##merge
#find/select numeric means in historical data: historical%>%arrange(-prt)%>%View()
historical.num<-historical%>%filter(item%in%c("faculty","emphasize") | grepl("^connect.",historical$item))

#row bind
numdf<-rbind(historical.num,current.num)%>%filter(!is.na(prt))%>%arrange(item)
```

```{r create numeric mean figure}
#viz aggregated numericn means in numdf
num.figure<-numdf%>%filter(year>2019)%>%
  #group_by(item,year,prt)%>%summarise(cnt=n())%>%
  
  ggplot(aes(y = prt, x=year, fill=year ))+
  geom_bar(stat="identity",position = position_dodge(),width=0.9)+
  scale_fill_manual(values = c("Grey","Grey70","#69b3e7"))+
  labs(title=str_wrap("",40),x="",y="",fill="") +
  theme_lz()+theme(legend.position = c(0.5,0.9),
                   plot.margin=unit(c(2.5,0,
                    0,0),"cm"))+
  geom_text(aes(label= ifelse(year==2022,as.character(round(prt,2)),"")),
            size=3,vjust=1.5,fontface="bold",position = position_dodge(0.9))+
  geom_text(aes(label= ifelse(year!=2022,as.character(round(prt,2)),"")),
            size=3,vjust=1.5,color="#6C6F70",fontface="bold",position = position_dodge(0.9))+
  
  facet_wrap(~factor(item,levels =c("faculty", "connect.faculty", "connect.stu","emphasize"),labels = c(str_wrap("Faculty Teaching",10),
                             str_wrap("Faculty Connection",10),
                             str_wrap("Student Connection",10),
                             str_wrap("Academic/Social Emphasis",10))),nrow=1,
             strip.position="bottom") +
  geom_line(aes(y = prt, x=year, group=item, 
                color=factor(item,levels =c("faculty", "connect.faculty", "connect.stu","emphasize")), 
                linetype=factor(item,levels =c("faculty", "connect.faculty", "connect.stu","emphasize"))),
            stat="identity", show.legend = F)+#
  scale_color_manual(name="",values=c("#FFCB4F","#6C6F70","#FFCB4F","#641F45"))+
  scale_linetype_manual(name="",values=c("solid","dashed","solid","solid"))
```

\newpage

# Academic and Social Support

## 2022 Academic and Social Support




```{r display empfaculty fig,include=TRUE, fig.height=3.5}
## 2022 Academic and Social Support
gridExtra::grid.arrange(faculty.figure,emp.figure, nrow=1, widths=c(1,1))
```

## Historical Academic and Social Support


```{r display numfigure, include=TRUE, fig.height=3}
## Historical Academic and Social Support (on scale of 1-6)
num.figure
```




```{r list/overview/notes of hypothesis test options}
#最严格
#cor.test(numeric, numeric)

##NumY
#t.test(NumY~ 2CatX) #Cat: category; num: numeric = continuous/ordinal
#wilcox.test(NumY~ 2CatX, paired=FALSE/TRUE)#not-normal distribution t.test
#aov(NumY~ 3+CatX) 
#kruskal.test(NumY, CatX) #not-normal distribution anova
#lm(NumY~anyX+..)

#CrossTable(propX, propY)
#CrossTable(CatX, CatY)
#glm(CatY~anyX, family = "binomial")# logistic regression: generalized linear model
```


```{r lm ethnicity on outcome vars}
#check N: fis.num%>%count(Ethnicity)
##summary(lm(service~Ethnicity,data=fis.num))
##summary(lm(life~Ethnicity,data=fis.num))
#viz the difference
#fis.num%>%group_by(Ethnicity)%>%summarise(svmn=mean(service,na.rm=TRUE))%>%
#  filter(svmn>0,!is.na(Ethnicity))%>%
#  ggplot(aes(x=Ethnicity,y=svmn))+geom_bar(stat="identity")
#viz together as points
#fis.num%>%filter(Ethnicity %in% c("Black or African American","Hispanic","White"))%>%
#  ggplot(aes(x=life,y=service))+geom_point(aes(color=Ethnicity))#+geom_line(aes(color=Ethnicity))

#further investigate which service/life: found conseling
##summary(aov(service.counseling~Ethnicity,data=fis.num))#different eth groups have different means
##mod<-lm(service.counseling~Ethnicity,data=fis.num)#how being in each of the eth change the mean (as show in each group's coefficient)
##summary(mod)#options(scipen=999)#options(scipen=0)
##jtools::summ(mod, digits = 1)#broom::tidy(mod, conf.int = TRUE)

#SET REFERENCE LEVEL IN LM
#make ordinal as a factor is more accurate when lm
#set the reference level of Ethnicity intentionally, to make the lm intercept that reference level 
##eth2<-relevel(factor(fis.num$Ethnicity),"White")#reference level change from alpabetic to white
##summary(lm(factor(service.counseling)~eth2,data=fis.num))
#coefficient and p value are interpreted compared to the reference level; 
#if not set reference level, then lm will auto-set the first reference level;
#if intentionally include all level in lm, then we are comparing whether each var is different from zero
#intentionally include all level (A,B,C): lm(y~I(1*(xvar=="A")+I(1*(xvar=="B"), data=data))#this set C as the reference level
#lm(y~I(1*(xvar=="A")+I(1*(xvar=="B")+I(1*(xvar=="C"), data=data))#this set no reference level


#MODEL SELECTION: use step-by-step nested model for variable selection:
#mod1<-lm(service.counseling~eth2,data=fis.num); summary(mod1)$coefficients
#mod2<-update(mod, service.counseling~eth2+gender); summary(mod2)$coefficients
#1.If the result is NA coefficient for newvar, then that newvar is a combination of the other vars already included
#2.anova(mod1,mod2)#if sig then adding additional var is meaningful for the y outcome

#USE THE LM FOR PREDICTION: predict(mod2,newdata=)


#viz the difference
#fis.num%>%filter(Ethnicity %in% c("Black or African American","Hispanic","White","Race and Ethnicity Unknown","Two or more Races"))%>%
#  ggplot(aes(x=Ethnicity,y=service.counseling,label=Ethnicity))+
#  geom_point()+geom_text()+
#  geom_jitter(aes(color=Ethnicity))
#  #+geom_line(aes(color=Ethnicity))
```


```{r create ethnicity on counseling figure}
ethdiff<-fis.num%>%group_by(Ethnicity)%>%summarise(svmn=mean(service.counseling,na.rm=TRUE))%>%
  filter(svmn>0,!is.na(Ethnicity))%>%
  ggplot(aes(x=reorder(Ethnicity,(-svmn)),y=svmn))+
  geom_point(aes(color=Ethnicity),size=10)+
  geom_text(aes(label=round(svmn,digits = 1)),fontface="bold")+
  theme_lz()+
  theme(axis.text.x =element_text(face = 'bold'),axis.text.y =element_text(face = 'bold'),legend.position = "none",plot.margin=unit(c(1.5,0,
                    1,0),"cm"))+
  labs(title=str_wrap("",40),x="",y="")+#caption="*Counseling service satisfaction is the only survey item significantly different by ethnicity"
  scale_x_discrete(labels=c(str_wrap("Hispanic (n=32)",10),str_wrap("Black (n=20)",10),
                            str_wrap("White (n=112)",10),str_wrap("Asian (n=6)",10),
                            str_wrap("Unknown (n=4)",10),str_wrap("Multi-races (n=4)",10)))+
  scale_y_continuous(limits = c(1,6), breaks=(seq(1, 6, 1)),
                     labels=c("Extremely Dissatisfied","2","3","4","5","Extremely Satisfied"))+
  scale_color_manual (values = c("grey70",mycolors[3],mycolors[3],"grey70","grey70",mycolors[3]),name="")




ethdiff2<-fis.num%>%group_by(Ethnicity)%>%summarise(
  counselmn=mean(service.counseling,na.rm=TRUE),
  aacmn=mean(service.aac,na.rm=TRUE),
  advmn=mean(service.acadvisor,na.rm=TRUE),
  overallmn=(counselmn+aacmn+advmn)/3) %>%
  filter(counselmn>0,aacmn>0,advmn>0,
         !is.na(Ethnicity),Ethnicity!="Race and Ethnicity Unknown")%>%arrange(overallmn)%>%
  pivot_longer(cols =c(counselmn:advmn), names_to = "mnitems",values_to = "meanvalue")%>%
  
  ggplot(aes(x=reorder(mnitems,(-meanvalue)),y=meanvalue))+
  geom_point(aes(color=mnitems,shape=mnitems),
             stat = "identity",position = position_dodge(width=0.9),size=10)+
  geom_text(aes(label=round(meanvalue,digits = 1)),fontface="bold")+
  theme_lz()+theme(axis.text.y =element_text(face = 'bold'))+labs(title="",x="",y="")+
  scale_color_manual(values=c("grey","grey70",mycolors[6]),name="",labels=c("AAC","Advisor","Counseling"))+
  scale_shape_manual(name = "", labels = c("AAC","Advisor","Counseling"), values = c(15,16,17))+
  scale_y_continuous(limits = c(1,6), breaks=(seq(1, 6, 1)),labels=c("Extremely Dissatisfied","2","3","4","5","Extremely Satisfied")) +
  facet_wrap(~factor(Ethnicity,levels = c("Two or more Races","Asian","White","Black or African American","Hispanic"),
labels=c(str_wrap("Multi-races (n=4)",10),
         str_wrap("Asian (n=6)",10),
         str_wrap("White (n=112)",10),
         str_wrap("Black (n=20)",10),
         str_wrap("Hispanic (n=32)",10))),nrow=1, strip.position="bottom") 
  
  #scale_y_continuous(breaks = seq(1, 6, by = 1) ,labels=scales::percent_format(accuracy = 1))
  #scale_y_discrete(labels=c("Extremly Dissatisfied","","","","","Extremly Satisfied"))
```
