---
title: "Review Core Curriculum"
author: ""
date: ""
output: 
  word_document:
    reference_docx: /Users/linlizhou/Documents/Rprojects/lasell.report.IN-USE.docx
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
#load all necessary packages and themes, global optin chunk
source("/Users/linlizhou/Documents/Rprojects/IR-Projects/theme_source.R")
```


# Core Course List (corelist)

```{r list of core courses}
corelist<-tibble(CourseCode=c("WRT101", "WRT102","ENG101","ENG102","MATH106", "MATH107", "MATH116", "MATH202", "MATH203", "MATH203", "MATH205", "MATH208", "MATH209", "FYS103", "HON101", "MDSC203", "HON205", "PHIL302", "ARTH107", "ARTS106", "ARTS126", "ARTS205", "ENG210", "ENG217", "ENG218", "ENG225", "MUS101", "MUS102", "MUS109", "MUS203", "PERF107", "PERF111", "PERF202", "PERF203", "HIST104", "SOC104", "ANTH101", "CJ101", "COM103", "ENV101", "LS101", "PSYC101", "SOC101", "SOC102", "BIO101", "BIO102", "BIO107", "BIO113", "CHEM105", "CHEM203", "ENV206", "ENV211", "ENV220", "MATH109", "PHYS111", "PHYS112", "SCI103", "SCI104", "SCI105", "SCI106", "SCI107", "SCI114", "SCI115", "SCI117", "SCI118", "SCI119", "BIO420", "BUSS497", "CHEM407", "COM400", "CJ443", "CJ444", "DSCI499", "ED496", "ED498", "ED482", "ED484", "ED427", "EXSC410", "EXSC425", "FASH415", "FSCI407", "GRAP400", "HS415", "HS425", "HUM400", "LS443", "LS444", "BIO430", "BUSS440", "CJ441", "CJ442", "COM495", "DSCI409", "ED494", "ENG402", "EXSC430", "FASH427", "FSCI480", "GLBS401", "GRAP404", "HIST401", "HS427", "HUM419", "HUM420", "LS441", "LS442", "MATH399")) %>%
mutate(CourseGroup=case_when(CourseCode%in%c("WRT101", "WRT102","ENG101","ENG102") ~"Writing", 
CourseCode%in%c("MATH106", "MATH107", "MATH116", "MATH202", "MATH203", "MATH203", "MATH205", "MATH208", "MATH209") ~"Math", 
CourseCode%in%c("FYS103", "HON101")  ~ "FYS", 
CourseCode%in%c("MDSC203", "HON205")  ~ "Multidisciplinary", 
CourseCode%in%c("PHIL302")  ~ "PHIL302", 
CourseCode%in%c("ARTH107", "ARTS106", "ARTS126", "ARTS205", "ENG210", "ENG217", "ENG218", "ENG225", "MUS101", "MUS102", "MUS109", "MUS203", "PERF107", "PERF111", "PERF202", "PERF203")  ~ "Aesthetics & Creativity", 
CourseCode%in%c("HIST104")  ~ "Global & Historical", 
CourseCode%in%c("SOC104", "ANTH101", "CJ101", "COM103", "ENV101", "LS101", "PSYC101", "SOC101", "SOC102")  ~ "Individuals & Society", 
CourseCode%in%c("BIO101", "BIO102", "BIO107", "BIO113", "CHEM105", "CHEM203", "ENV206", "ENV211", "ENV220", "MATH109", "PHYS111", "PHYS112", "SCI103", "SCI104", "SCI105", "SCI106", "SCI107", "SCI114", "SCI115", "SCI117", "SCI118", "SCI119")  ~ "Scientific Inquiry & Problem Solving",
CourseCode%in%c("BIO420", "BUSS497", "CHEM407", "COM400", "CJ443", "CJ444", "DSCI499", "ED496", "ED498", "ED482", "ED484", "ED427", "EXSC410", "EXSC425", "FASH415", "FSCI407", "GRAP400", "HS415", "HS425", "HUM400", "LS443", "LS444")  ~ "Internship", 
CourseCode%in%c("BIO430", "BUSS440", "CJ441", "CJ442", "COM495", "DSCI409", "ED494", "ENG402", "EXSC430", "FASH427", "FSCI480", "GLBS401", "GRAP404", "HIST401", "HS427", "HUM419", "HUM420", "LS441", "LS442", "MATH399")  ~ "Capstone"))

#Scientific Inquiry & Problem Solving KP
#sectiontally%>%filter(grepl("^SCI|^BIO|^CHEM|^ENV|^MATH|^PHYS", event_id), 
#                      grepl("KP$", section)) %>%count(event_id)
#added the last few; and removed:  "SCI117", "SCI118", "SCI119", "MATH109", "SCI107"  in Scientific Inquiry & Problem Solving KP


```

# Section Tally 2018-2022 (sectiontally\_)

```{r load crs data}
#download section tally for 2018 Fall, 2019 Spring, 2019 Fall, 2020 Spring, 2020 Fall, 2021 Spring, 2021 Fall, 2022 Spring
# var needed: coursecodes, sectiontimes, student enrollment, student grades

fa18.sec<-read_csv("/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Data and Analyses/Program Review/2022 Core Curriculum/data files/Section Tally18fall.csv", skip = 2)%>%mutate(term="2018 Fall")
sp19.sec<-read_csv("/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Data and Analyses/Program Review/2022 Core Curriculum/data files/Section Tally19sp.csv", skip = 2)%>%mutate(term="2019 Spring")
  
fa19.sec<-read_csv("/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Data and Analyses/Program Review/2022 Core Curriculum/data files/Section Tally19fall.csv", skip = 2)%>%mutate(term="2019 Fall")
sp20.sec<-read_csv("/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Data and Analyses/Program Review/2022 Core Curriculum/data files/Section Tally20sp.csv", skip = 2)%>%mutate(term="2020 Spring")

fa20.sec<-read_csv("/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Data and Analyses/Program Review/2022 Core Curriculum/data files/Section Tally20fall.csv", skip = 2)%>%mutate(term="2020 Fall")
sp21.sec<-read_csv("/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Data and Analyses/Program Review/2022 Core Curriculum/data files/Section Tally21sp.csv", skip = 2)%>%mutate(term="2021 Spring")

fa21.sec<-read_csv("/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Data and Analyses/Program Review/2022 Core Curriculum/data files/Section Tally21fall.csv", skip = 2)%>%mutate(term="2021 Fall")
sp22.sec<-read_csv("/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Data and Analyses/Program Review/2022 Core Curriculum/data files/Section Tally22sp.csv", skip = 2)%>%mutate(term="2022 Spring")



# solve NA problem in WRI in 18fall/19
#since we have NA section for WRI101/102 in 18fall/19spring, we investigated the raw data
sp19.sec%>%#filter(term=="2018 Fall")%>%
  #count(coursecode,event_long_name)
  filter(str_detect(event_long_name,"Writing"))%>%count(event_long_name,event_id)
#found ENG101/102 as writing course too -- edited corecourse list and everything else updated done


#merge
sectiontally_1822allcrs<-plyr::join_all(list(fa18.sec, sp19.sec, fa19.sec, sp20.sec, fa20.sec, sp21.sec, fa21.sec, sp22.sec), type="full")%>%#6246 rows
#exclude suffix in event_id: extract any number of LETTER followed by any number of NUMBER 
mutate(coursecode=str_extract(event_id,"[A-Z]+[0-9]+"))#check: %>%count(coursecode)

#only keep core courses
sectiontally_1822core<-sectiontally_1822allcrs%>%filter(sectiontally_1822allcrs$coursecode %in% corelist$CourseCode)%>%unique()%>%#check: %>%count(coursecode)#1338 rows
#add segment/coursegroup names col
left_join(corelist, by=c("coursecode"="CourseCode"))%>%unique()%>%#1338 rows
#remove invalid section (enrollment>0)
filter(Current_Enrollment>0)%>%
#factorize coursegroup for convinience showing
mutate(CourseGroup=factor(CourseGroup,levels = c("Writing","Math","FYS","Multidisciplinary","PHIL302","Aesthetics & Creativity","Global & Historical","Individuals & Society","Scientific Inquiry & Problem Solving","Internship","Capstone")))%>%
#factorize term for convinience showing
mutate(term=factor(term,levels = c("2018 Fall","2019 Spring","2019 Fall","2020 Spring","2020 Fall","2021 Spring","2021 Fall","2022 Spring")))

#check course and section combination is unique: sectiontally%>%count(coursecode,section,class_time,instructor,course_start_date,event_long_name)%>%filter(n>1)
```

# Stu Info by Course 2018-2022 (stucrs\_, stucrs.id)

```{r load student data}
# download stu info by course for 18-19, 19-20, 20-21, 21-22
# var needed: core course students' transfer status, unduplicated total enroll
crs18_19<-read_csv("/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Data and Analyses/Program Review/2022 Core Curriculum/data files/Student Info by Course and Fiscal Year18-19.csv")
crs19_20<-read_csv("/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Data and Analyses/Program Review/2022 Core Curriculum/data files/Student Info by Course and Fiscal Year19-20.csv")
crs20_21<-read_csv("/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Data and Analyses/Program Review/2022 Core Curriculum/data files/Student Info by Course and Fiscal Year20-21.csv")
crs21_22<-read_csv("/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Data and Analyses/Program Review/2022 Core Curriculum/data files/Student Info by Course and Fiscal Year21-22.csv")
#merge
stucrs_1822allcrs<-plyr::join_all(list(crs18_19,crs19_20,crs20_21,crs21_22), type="full")%>%#110588 rows
#only fall-spring term
filter(academic_term%in%c("FALL","SPRING"))%>%#101559
#exclude suffix in Course_ID: extract any number of LETTER followed by any number of NUMBER 
mutate(coursecode=str_extract(Course_ID,"[A-Z]+[0-9]+"))%>%#check: %>%count(coursecode)
#clean final grades: only kept valid grades
filter(Final_Grade%in%c("F", "W", "A", "A-", "B+", "B", "B-", "C+", "C", "P","D","D+","D-"))%>%
#regroup grades into groups
  mutate(grade=if_else(Final_Grade%in%c("A", "A-", "B+", "B", "B-", "C+", "C", "P"), "C or better",if_else(Final_Grade%in%c("D","D+","D-"),"D",Final_Grade)),
#convert letter grades to GPA        
GPA=case_when(Final_Grade=="F"~"0",Final_Grade=="A"~"4.0",Final_Grade=="A-"~"3.7",
Final_Grade=="B+"~"3.3",Final_Grade=="B"~"3",Final_Grade=="B-"~"2.7",
Final_Grade=="C+"~"2.3",Final_Grade=="C"~"2",Final_Grade=="C-"~"1.7",
Final_Grade=="D+"~"1.3",Final_Grade=="D"~"1",Final_Grade=="D-"~"0.7"),
GPA=as.numeric(GPA))%>%
# DO NOT only keep semester GPA>0 since people can fail all courses: filter(Semester_GPA>0)%>%
#exclude students who dropped the class from calculating/reporting enrollment or gpa
filter(Add_Drop!="D")
#check: stucrs_1822allcrs%>%count(Add_Drop)

#only keep core courses
stucrs_1822core<-stucrs_1822allcrs%>%filter(stucrs_1822allcrs$coursecode %in% corelist$CourseCode)%>%unique()%>%#check: %>%count(coursecode)#29424 rows
#add segment/coursegroup names col
left_join(corelist, by=c("coursecode"="CourseCode"))%>%unique()%>%#29424 rows
#factorize coursegroup for convinience showing
mutate(CourseGroup=factor(CourseGroup,levels = c("Writing","Math","FYS","Multidisciplinary","PHIL302","Aesthetics & Creativity","Global & Historical","Individuals & Society","Scientific Inquiry & Problem Solving","Internship","Capstone")))%>%
#mutate and factorize term for convinience showing
mutate(term=paste(academic_year,academic_term,sep=" "),
                        term=factor(term,levels = c("2018 FALL","2019 SPRING","2019 FALL","2020 SPRING","2020 FALL","2021 SPRING","2021 FALL","2022 SPRING")))

#check course and section combination is unique: stucrs_1822core%>%count(people_code_id,coursecode,Course_section,Course_Name,Instructor_ids,Add_Drop, term)%>%filter(n>1)%>%arrange(people_code_id)#appeared twice

#check one of those twice appearance: stucrs_1822core%>%filter(people_code_id=="P000046408",coursecode=="FASH427",Course_section=="A",term=="2019 SPRING")
##it's due to two different semester GPA (3.756 VS 4)
#check one of those twice appearance: stucrs_1822core%>%filter(people_code_id=="P000052536",coursecode=="CHEM203",Course_section=="B",term=="2019 FALL")
##it's due to event_sub_type is both L (lab) and B
#check one of those twice appearance: stucrs_1822core%>%filter(people_code_id=="P000050397",coursecode=="HUM400",Course_section=="A",term=="2022 SPRING")
##it's due to two different semester GPA (3.85 VS 4)

#still have 6 ppid with twice appreance (one duplication)
```

```{r unduplicated student list for transfer status}
#transfer status in dtm
#instead of reading dmt (huge file) every time, save a portion of it and read the smaller new data file
#dmt<-read_excel("/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Datamart Files/DataMart To Date/Final Datamart up to Date 09262022.xlsx")
#dmt.transfer<-dmt%>%select(PC_ID,TRANSFER_YN,GRADUATED_YN)
#write_xlsx(dmt.transfer,"/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Data and Analyses/Program Review/2022 AAC/data files/dmt.transfer.xlsx")

dmt.transfer<-read_excel("/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Data and Analyses/Program Review/2022 AAC/data files/dmt.transfer.xlsx")


#unduplicated student list: distinctive ppid for each term: 
stucrs.id<-stucrs_1822core%>%group_by(term)%>%distinct(people_code_id)%>%unique()%>%#check: unqiue now: stucrs.id%>%count(term,people_code_id)
#merge with dtm transfer status
left_join(dmt.transfer,by=c("people_code_id"="PC_ID"))
#not unique now: stucrs.id%>%count(term,people_code_id)


#deduplicate transfer status: once transfer then transfer
y<-stucrs.id%>%mutate(transfer=case_when(TRANSFER_YN=="Y"~TRANSFER_YN, TRANSFER_YN!="Y"~"N"))%>%select(people_code_id,transfer)%>%unique()%>%arrange(people_code_id)%>%filter(transfer =="Y")#keep any A values of new col
n<-stucrs.id%>%filter(! people_code_id%in% y$people_code_id)%>%mutate(transfer ="N")%>%select(people_code_id,transfer)%>%unique()%>%arrange(people_code_id)##for ppid not settled with y will be notA

#merge settled in y and n; #attach back (using transfer) to the original dataset
yn<-full_join(y,n) #check: indeed one time appearance: yn%>%count(people_code_id)%>%count(n)

stucrs.id<-left_join(stucrs.id,yn)%>%select(-TRANSFER_YN)%>% unique()%>%arrange(people_code_id)#remove used TRANSFER_YN (used transfer replace var)
#once again unique: stucrs.id%>%count(term,people_code_id)%>%count(n)
```

# Path of taking core courses (corepath.ls, corepath)

```{r corepath_ ppid and coursegroup as cols_ term as values}
#only those from 2018 cohort
corepath.ls<-stucrs_1822core%>%filter(cohort_id=="2018")%>%
#select relevant vars: ppid take which coursegroup & when
  select(people_code_id,term,CourseGroup)%>%unique()%>%
#which semester they take certain course: recode term for easier readability
  mutate(term=case_when(term=="2018 FALL"~1,term=="2019 SPRING"~2,term=="2019 FALL"~3,term=="2020 SPRING"~4,term=="2020 FALL"~5,term=="2021 SPRING"~6,term=="2021 FALL"~7,term=="2022 SPRING"~8))

#collapse the Same person taking the Same coursegroup (at the Same term) into one row
#each course, what terms
corepath<-corepath.ls%>%group_by(people_code_id,CourseGroup)%>%count(term)%>%select(-n)%>%
#approach 1-manual copy paste from pivot wider output
  pivot_wider(names_from = CourseGroup,values_from = term)%>%#%>%View()#united term together as vector; but need to manually copy View() to excel output
#approach 2-based on approach 1, convert list-col to string so that can auto export as normal cell into excel
  mutate(across(Writing:Internship, function(x) sapply(x, toString)))
#shorten from: mutate(Writing = sapply(Writing, toString),...)

#check for n-per-key is unique: corepath%>%count(people_code_id)%>%filter(n>1)

```

```{r corepath add matric col}
#merge more background vars to corepath
corepath<-left_join(corepath,dmt.transfer[c("PC_ID","GRADUATED_YN")],by=c("people_code_id"="PC_ID"))

#de-duplicate: any of the term is “1” then they are
y<-corepath%>%mutate(matric=case_when(GRADUATED_YN=="Y"~"Graduated",GRADUATED_YN!="Y"~"Not Graduate"))%>%
  select(people_code_id,matric)%>%unique()%>%arrange(people_code_id)%>%filter(matric =="Graduated")#keep any grad values of new col
n<-corepath%>%filter(! people_code_id%in% y$people_code_id)%>% #for people_code_id with not settled
  mutate(matric="Not Graduate")%>%#all not settled with y will be not grad
  select(people_code_id,matric)%>%unique()%>%arrange(people_code_id)
#merge settled in y and n
matric.df<-full_join(y,n)

#attach back (using matric) to the original dataset
corepath<-left_join(corepath,matric.df)%>%
  select(-GRADUATED_YN)%>% unique()%>%arrange(people_code_id)#remove used GRADUATED_YN (used matric replace GRADUATED_YN)


#merge more background vars to corepath.ls
corepath.ls<-left_join(corepath.ls,corepath[c("people_code_id","matric")])
```

# AAC Courses (aac.crs)

```{r aac.crs df created}
#based on 5 years stu info by course df
aac.crs<-stucrs_1822allcrs%>%
#only keep AAC courses
filter(coursecode %in% c("AAC102","AAC103","AAC104"))%>%unique()%>%#check: %>%count(coursecode)
#factorize term for convinience showing
mutate(coursecode=factor(coursecode,levels = c("AAC102","AAC103","AAC104")),
term=paste(academic_year,academic_term,sep=" "),
term=factor(term,levels = c("2018 FALL","2019 SPRING","2019 FALL","2020 SPRING","2020 FALL","2021 SPRING","2021 FALL","2022 SPRING")))%>%
#add category var (pass vs fail of aac course)
mutate(passfail=case_when(Final_Grade%in%c("P","A")~"Pass",Final_Grade%in%c("F","W")~"Fail"))%>%#check:%>%count(passfail)
#add category var (2.0 semester GPA)
mutate(semGPA=case_when(Semester_GPA>=2~"> 2",Semester_GPA<2~"< 2"),
       semGPA=factor(semGPA,levels = c("> 2","< 2")))%>%#check: %>%count(semGPA)
mutate(passfail=factor(passfail,levels = c("Pass","Fail")))#reorder
#check: aac.crs%>%count(Add_Drop); aac.crs%>%count(Final_Grade)

#rename to better format
aac.crs$term<-aac.crs$term%>%str_replace("FALL","Fall")%>%str_replace("SPRING","Spring")
```

## Retaking AAC103 (retake103df)

```{r retake103 student df}
#how Studentsretake AAC103 impacts their retakeAAC103grade & semester GPA

# who are retaking courses:
# for aac103, when ppid in more than one term (it will show as more than one row in ppid-term table), then count ppid in the table and filter apperance>1
retake103id<-aac.crs%>%filter(coursecode=="AAC103",!is.na(passfail))%>%
  count(people_code_id,term)%>%count(people_code_id)%>%filter(n>1)#90 students

#save these retake students group
retake103df<-aac.crs%>%filter(people_code_id%in%retake103id$people_code_id,!is.na(passfail),coursecode=="AAC103")%>%
  unique()%>%arrange(people_code_id)%>%
  #distinguish term sequence
  mutate(term=factor(term,levels = c("2018 Fall","2019 Spring","2019 Fall","2020 Spring","2020 Fall","2021 Spring","2021 Fall","2022 Spring")),
    term_num=case_when(term=="2018 Fall"~1,term=="2019 Spring"~2,term=="2019 Fall"~3,term=="2020 Spring"~4,
    term=="2020 Fall"~5,term=="2021 Spring"~6,term=="2021 Fall"~7,term=="2022 Spring"~8))
  #check:%>%count(people_code_id)

#transform term num
#retake103df%>%select(people_code_id,term_num,term)%>%pivot_wider(names_from = #term_num, values_from = term)%>%
#  select(which(colSums(is.na(.))<nrow(.)))%>%#remove NA values cols
#  unite(`1`,`2`,`3`,`4`,`5`,`6`,`7`,`8`, col = "counts", na.rm=TRUE, sep = #",")%>%#View()
#  #separate_rows(counts, sep = ",")#split into different rows
#  separate(counts,c("firstcount","secondcount","thirdcount","fourthcount","fifthcount"),sep=",")
```

## Viz pass/fail and gpa by term (retake.change)

```{r retake.change which map out grades AND gpa each term in time-order}
#transform pass/fail in term-order
grades.change.table<-retake103df%>%select(people_code_id,term_num,passfail)%>%pivot_wider(names_from = term_num, values_from = passfail)%>%
  select(which(colSums(is.na(.))<nrow(.)))%>%#remove NA values cols
  unite(`1`,`2`,`3`,`4`,`5`,`6`,`7`,`8`, col = "counts", na.rm=TRUE, sep = ",")%>%#View()
  #separate_rows(counts, sep = ",")#split into different rows
  separate(counts,c("grade_1sttime","grade_2ndtime","grade_3rdtime","grade_4thtime","grade_5thtime"),sep=",")


#transform semGPA for each term in the order of terms
semGPA.change.table<-retake103df%>%select(people_code_id,term_num,semGPA)%>%pivot_wider(names_from = term_num, values_from = semGPA)%>%
  select(which(colSums(is.na(.))<nrow(.)))%>%#remove NA values cols
  unite(`1`,`2`,`3`,`4`,`5`,`6`,`7`,`8`, col = "counts", na.rm=TRUE, sep = ",")%>%#View()
  #separate_rows(counts, sep = ",")#split into different rows
  separate(counts,c("semGPA_1sttime","semGPA_2ndtime","semGPA_3rdtime","semGPA_4thtime","semGPA_5thtime"),sep=",")


retake.change<-full_join(grades.change.table,semGPA.change.table)%>%
  mutate(grade_1to2=case_when(
  grade_1sttime=="Pass"&grade_2ndtime=="Pass"~"Same Pass",
  grade_1sttime=="Fail"&grade_2ndtime=="Fail"~"Same Fail",
  grade_1sttime=="Fail"&grade_2ndtime=="Pass"~"Increase",
  grade_1sttime=="Pass"&grade_2ndtime=="Fail"~"Decrease"),
  #compare 1st to 2nd time taking aac103
  semGPA_1to2=case_when(
  semGPA_1sttime=="higher than 2"&semGPA_2ndtime=="higher than 2"~"Same >2",
  semGPA_1sttime=="lower than 2"&semGPA_2ndtime=="lower than 2"~"Same <2",
  semGPA_1sttime=="lower than 2"&semGPA_2ndtime=="higher than 2"~"Increase",
  semGPA_1sttime=="higher than 2"&semGPA_2ndtime=="lower than 2"~"Decrease"),
  #reorder
  grade_1to2=factor(grade_1to2,levels = c("Same Pass","Increase","Decrease","Same Fail")),
  semGPA_1to2=factor(semGPA_1to2,levels = c("Same >2","Increase","Decrease","Same <2")),
  
  #compare 2nd to 3rd time taking aac103
  grade_2to3=case_when(
  grade_2ndtime=="Pass"&grade_3rdtime=="Pass"~"Same Pass",
  grade_2ndtime=="Fail"&grade_3rdtime=="Fail"~"Same Fail",
  grade_2ndtime=="Fail"&grade_3rdtime=="Pass"~"Increase",
  grade_2ndtime=="Pass"&grade_3rdtime=="Fail"~"Decrease"),
  
  semGPA_2to3=case_when(
  semGPA_2ndtime=="higher than 2"&semGPA_3rdtime=="higher than 2"~"Same >2",
  semGPA_2ndtime=="lower than 2"&semGPA_3rdtime=="lower than 2"~"Same <2",
  semGPA_2ndtime=="lower than 2"&semGPA_3rdtime=="higher than 2"~"Increase",
  semGPA_2ndtime=="higher than 2"&semGPA_3rdtime=="lower than 2"~"Decrease"),
  #reorder
  grade_2to3=factor(grade_2to3,levels = c("Same Pass","Increase","Decrease","Same Fail")),
  semGPA_2to3=factor(semGPA_2to3,levels = c("Same >2","Increase","Decrease","Same <2")),
  
  
  #compare 3rd to 4th time taking aac103
  grade_3to4=case_when(
  grade_3rdtime=="Pass"&grade_4thtime=="Pass"~"Same Pass",
  grade_3rdtime=="Fail"&grade_4thtime=="Fail"~"Same Fail",
  grade_3rdtime=="Fail"&grade_4thtime=="Pass"~"Increase",
  grade_3rdtime=="Pass"&grade_4thtime=="Fail"~"Decrease"),
  
  semGPA_3to4=case_when(
  semGPA_3rdtime=="higher than 2"&semGPA_4thtime=="higher than 2"~"Same >2",
  semGPA_3rdtime=="lower than 2"&semGPA_4thtime=="lower than 2"~"Same <2",
  semGPA_3rdtime=="lower than 2"&semGPA_4thtime=="higher than 2"~"Increase",
  semGPA_3rdtime=="higher than 2"&semGPA_4thtime=="lower than 2"~"Decrease"),
  #reorder
  grade_3to4=factor(grade_3to4,levels = c("Same Pass","Increase","Decrease","Same Fail")),
  semGPA_3to4=factor(semGPA_3to4,levels = c("Same >2","Increase","Decrease","Same <2")),
  
  
  #compare 4th to 5th time taking aac103
  grade_4to5=case_when(
  grade_4thtime=="Pass"&grade_5thtime=="Pass"~"Same Pass",
  grade_4thtime=="Fail"&grade_5thtime=="Fail"~"Same Fail",
  grade_4thtime=="Fail"&grade_5thtime=="Pass"~"Increase",
  grade_4thtime=="Pass"&grade_5thtime=="Fail"~"Decrease"),
  
  semGPA_4to5=case_when(
  semGPA_4thtime=="higher than 2"&semGPA_5thtime=="higher than 2"~"Same >2",
  semGPA_4thtime=="lower than 2"&semGPA_5thtime=="lower than 2"~"Same <2",
  semGPA_4thtime=="lower than 2"&semGPA_5thtime=="higher than 2"~"Increase",
  semGPA_4thtime=="higher than 2"&semGPA_5thtime=="lower than 2"~"Decrease"),
  #reorder
  grade_4to5=factor(grade_4to5,levels = c("Same Pass","Increase","Decrease","Same Fail")),
  semGPA_4to5=factor(semGPA_4to5,levels = c("Same >2","Increase","Decrease","Same <2"))
  )

```

# Overview of data frames created

1.  corelist: CourseCode, CourseGroup

2.  sectiontally_1822allcrs: merging 18-22 fall and spring from "section
    tally" files,

    \*coursecode=str_extract(event_id,"[A-Z]+[0-9]+")

3.  sectiontally_1822core: leftjoin core list, filter
    "Current_Enrollment"\>0, factorize "term" and "CourseGroup"

    ```{r}
    #save: 
    write_xlsx(sectiontally_1822allcrs,"/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Data and Analyses/Program Review/2022 Core Curriculum/data files/Section Tally_1822allcrs.xlsx")

    write_xlsx(sectiontally_1822core,"/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Data and Analyses/Program Review/2022 Core Curriculum/data files/Section Tally_1822core.xls")
    ```

4.  stucrs_1822allcrs: merging 18-22 fall and spring files from "student
    info by course" files, only keep valid grades in "Final_Grade", only keep active students (not
    dropped the class) in "Add_Drop", grade (C or better, D, F, W, P),
    convert letter grade to numeric "GPA"

5.  stucrs_1822core: leftjoin core list, factorize term and CourseGroup

6.  stucrs.id: distinct ppid by term, merge with dtm (TRANSFER_YN var)
    and deduplicate TRANSFER_YN

    ```{r}
    #save: 
    write_xlsx(stucrs_1822allcrs,"/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Data and Analyses/Program Review/2022 Core Curriculum/data files/StudentInfoCourse_1822allcrs.xlsx")

    write_xlsx(stucrs_1822core,"/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Data and Analyses/Program Review/2022 Core Curriculum/data files/StudentInfoCourse_1822core.xlsx")

    write_xlsx(stucrs.id,"/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Data and Analyses/Program Review/2022 Core Curriculum/data files/StudentInfoCourse_1822core_dedupid.xlsx")
    ```

7.  Corepath.ls: 2018 cohort ppid, term, CourseGroup , matric

8.  Corepath (viz of corepath.ls): ppid, coursegroup as cols; term as
    values; matric category

    ```{r}
    #save
    write_xlsx(corepath,"/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Data and Analyses/Program Review/2022 Core Curriculum/data files/path_18cohort.xlsx")

    write_xlsx(corepath.ls,"/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Data and Analyses/Program Review/2022 Core Curriculum/data files/path_df_18cohort.xlsx")
    ##AFTER EXPORT TO EXCEL: I did conditional formatting for term 1-8, each cell that contains a term ("1") has a different color (1-4 is ascending blue, 5-8 is ascending green)
    ```

9.  aac.crs: filter aac courses from stucrs_1822allcrs; term,coursecode,
    Semester_GPA, Cumulative_GPA

10. retake103df: based on aac.crs, filter out those who retake aac103
    (appear more than once when groupby ppid and course and then count
    ppid in that list)

11. retake.change: "passfail" and "semGPA" for each ppid (row) each term
    (col), more cols: compare previous term to later term

    ```{r}
    #save: 
    write_xlsx(aac.crs,"/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Data and Analyses/Program Review/2022 AAC/data files/StudentInfoCourse_1822aac.xlsx")

    write_xlsx(retake103df,"/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Data and Analyses/Program Review/2022 AAC/data files/aac103retake_stuinfo.xlsx")

    write_xlsx(retake.change,"/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Data and Analyses/Program Review/2022 AAC/data files/aac103retake_termchanges.xlsx")
    ```
