---
title: "Academic Achievement Center (AAC) Courses  \nEnrollments and Grades Review"
subtitle: "(2018 Fall - 2022 Spring)"
author: 'Lasell University Institutional Research'
date: "`r Sys.Date()`"
format: 
  pdf:
    keep-md: true
    include-in-header:
      - text: |
          \usepackage{fancyhdr}
          \addtolength{\headheight}{0.7cm}
    
          \pagestyle{fancy} 
          \fancyhead{}
          \fancyfoot{}
    
          \fancyhead[LO]{\includegraphics[height=1.3cm]{/Users/linlizhou/Documents/Rprojects/IR.png}}
          \fancyhead[RE]{\vspace{4mm}\textbf{AAC Courses Review}}
          \fancyfoot[C]{\thepage}
    
          \renewcommand{\headrulewidth}{0pt}
---

```{r load.df.funs, include=FALSE}
#load all necessary packages and themes, global optin chunk
source("/Users/linlizhou/Documents/Rprojects/IR-Projects/theme_source.R")

#change format: html (for render in Viewer) 
#format: html
#to the following for the word doc. version report
#format: 
#  docx:
#    reference-doc: /Users/linlizhou/Documents/Rprojects/IR-Projects/lasell.report.template.docx
#    prefer-html: true
#format: 
#  pdf:
#    classoption: [twoside]
#    include-in-header:
#      - text: |
#format:
#    pdf:
 #       toc: true
  #      toc-depth: 2
   #     toc-title: Table of contents
    #    number-sections: true
     #   highlight-style: github
#the following df are created from "/Users/linlizhou/Documents/Rprojects/IR-Projects/theme_source.R" 
#enrollment of core courses
#grades of aac courses
aac.crs<-read_xlsx("/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Data and Analyses/Program Review/2022 AAC/data files/StudentInfoCourse_1822aac.xlsx")
#for those who take aac103 more than once, their term comparison
retake.change<-read_xlsx("/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Data and Analyses/Program Review/2022 AAC/data files/aac103retake_termchanges.xlsx")

#reporting-goal/items

#DONE-For each term (fall/spring): # courses/ sections offered in each core segment – SECTION TALLY
#DONE-For each term (fall/spring): # registration in each core segment – SECTION TALLY
#DONE- % of pass, C or better, and Withdrawal; Average GPA (and SD) of each courses – STU INFO BY COURSE
#DONE-All core course enrollment and transfer proportion – deduplicated student count in STU INFO BY COURSE
#DONE/HIDE-All core course retention – STARFISH RETENTION REPORT
#DONE-Satisfaction – 2018-2022 4 years of satisfaction prt in that one question containing "core"
#DONE-course-taking sequence – 2018 COHORT BY GRADUATION IN 2022 OR NOT – POWERCAMPUS TRANSCRIPT

```

# Enrollment

```{r tab.aacenroll-unduplicated enrollment}
#for each term and each course, how many unique students are enrolled/exist in the dataset
tab.aacenroll<-aac.crs%>%group_by(coursecode,term)%>%summarise(n=n_distinct(people_code_id))%>%
  mutate(Average=round(mean(n),digits = 0))%>%
  pivot_wider(names_from = term,values_from = n)

#rename capital letter
names(tab.aacenroll)<-names(tab.aacenroll)%>%str_replace("FALL","Fall")%>%str_replace("SPRING","Spring")

#reorder cols
tab.aacenroll<-tab.aacenroll%>%select(coursecode,Average,`2018 Fall`,`2019 Spring`,`2019 Fall`,`2020 Spring`,`2020 Fall`,`2021 Spring`,`2021 Fall`,`2022 Spring`)#%>%View()
```

```{r static_tab.aacenroll}
#show the table
static_tab.aacenroll<-tab.aacenroll%>%
kbl(align = "c",booktabs = T,label="tab.aacenroll",#in-text reference
    caption = "AAC course enrollment by term", #table title
    col.names =c("",names(tab.aacenroll)[2:ncol(tab.aacenroll)]
                 #str_wrap(names(tab.aacenroll)[2:ncol(tab.aacenroll)],width = 5)
                 )) %>%#header names
#set overall style
  kable_styling(latex_options = c('hold_position'),#for non html output
                bootstrap_options = c("striped", "hover", "condensed", "responsive"),#for html output
                #have to remove left_flot position to render pdf successfully
#fill the page width-wise,#header stay when scroll
              full_width = F, fixed_thead = T, font_size = 12)%>%
#set header row: have to remove header row setting to successfully set width in column_spec
#row_spec(0,align = "c",color="black")%>%
#set first column: 
  column_spec(1, bold = T, border_right = F, background = "white", width = "4em",color="black")
  

#apply cf to multi columns
for (i in 3:ncol(tab.aacenroll)){
static_tab.aacenroll<-
  column_spec(kable_input=static_tab.aacenroll,
  column=i, width = "3em",background =cf_color(tab.aacenroll[i],a=70,b=60,c=45,d=40))
i=i+1
static_tab.aacenroll}
```

```{r showviz.aacenroll, include=TRUE}
static_tab.aacenroll
```

```{r reportvalues.enroll}
n_aacenroll<-aac.crs%>%group_by(coursecode,term)%>%summarise(n=n_distinct(people_code_id))%>%
  mutate(Average=round(mean(n),digits = 0))

n_aacenroll[n_aacenroll$coursecode=="AAC103","Average"][[1]][1]
```

Among the past 5 years (2018 Fall to 2022 Spring), AAC course enrollment
ranged from `r min(n_aacenroll$n)` to `r max(n_aacenroll$n)`. An average
enrollment for AAC103 over that time was
`r n_aacenroll[n_aacenroll$coursecode=="AAC103","Average"][[1]][1]`
students.

# Pass Rate

```{r tab.aacpass-pass vs fail}
# report prt students pass
tab.aacpass<-aac.crs%>%filter(!is.na(passfail))%>%#remove anything that was not defined by pass or fail
  group_by(coursecode,term,passfail)%>%summarise(cnt=n())%>%
  #mutate(prt=formattable::percent(cnt/sum(cnt),digits = 0))%>%
  mutate(prt=cnt/sum(cnt))%>%
  filter(passfail%in%c("Pass"))%>%select(-cnt)

tab.aacpass_avg<-tab.aacpass%>%select(-passfail)%>%
  group_by(coursecode)%>%summarize(Average=mean(prt))

tab.aacpass<-left_join(tab.aacpass,tab.aacpass_avg)%>%select(-passfail)%>%
  pivot_wider(names_from = term, values_from = prt)%>%
  select(coursecode,Average,`2018 Fall`,`2019 Spring`,`2019 Fall`,`2020 Spring`,`2020 Fall`,`2021 Spring`,`2021 Fall`,`2022 Spring`)%>%
mutate(across(Average:`2022 Spring`, ~percent(.x, digit=0)))
```

```{r static_tab.aacpass}
static_tab.aacpass<-tab.aacpass%>%
kbl(align = "c",booktabs = T,label="tab.aacpass",#in-text reference
    caption = "AAC course pass rates", #table title
    col.names =c("",names(tab.aacpass)[2:ncol(tab.aacpass)])) %>%#header names
#set overall style
  kable_styling(latex_options = c('hold_position'),bootstrap_options = c("striped", "hover", "condensed", "responsive"),
              full_width = F, fixed_thead = T, font_size = 12)%>%
#set header row
#row_spec(0,align = "c",color="black")%>%
#set first column: 
  column_spec(1, bold = T, border_right = F, background = "white", width = "4em",color="black")

#apply cf_color to multi columns
for (i in 2:ncol(tab.aacpass)){
static_tab.aacpass<-column_spec(
  kable_input=static_tab.aacpass,
  column=i, width = "3em",color = "black",
  background =cf_color(tab.aacpass[i],a=.9,b=.8))
i=i+1
static_tab.aacpass}
```

```{r showviz.aacpass, include=TRUE}
static_tab.aacpass
```

```{r reportvalues.passrate}
passrate.6<-aac.crs%>%filter(!is.na(passfail))%>%#remove anything that was not defined by pass or fail
  group_by(coursecode,term,passfail)%>%summarise(cnt=n())%>%
  #mutate(prt=formattable::percent(cnt/sum(cnt),digits = 0))%>%
  mutate(prt=cnt/sum(cnt))%>%
  filter(passfail%in%c("Pass"))%>%select(-cnt)%>%
  filter(prt<.6)
```

Average pass rate across all AAC courses is
`r mean(tab.aacpass_avg$Average)%>%percent(digit=0)` for the past 5
academic years. However, AAC103 pass rate in 2020 Fall was
`r passrate.6$prt%>%percent(digit=0)`.

```{r explore cumulative GPA by passfail}
#PASSED students' mean cumulative GPA
aac.crs%>%filter(!is.na(passfail))%>%#remove anything that was not defined by pass or fail
  group_by(term,coursecode,passfail)%>%
  summarise(mn=round(mean(Cumulative_GPA,na.rm=TRUE),digits=1))%>%
  filter(passfail%in%c("Pass"))%>%
  pivot_wider(names_from = passfail, values_from = mn)%>%
  pivot_wider(names_from = term,values_from = Pass)#%>%View()
#FAILED students' mean cumulative GPA
aac.crs%>%filter(!is.na(passfail))%>%#remove anything that was not defined by pass or fail
  group_by(term,coursecode,passfail)%>%
  summarise(mn=round(mean(Cumulative_GPA,na.rm=TRUE),digits=1))%>%
  filter(passfail%in%c("Fail"))%>%
  pivot_wider(names_from = passfail, values_from = mn)%>%
  pivot_wider(names_from = term,values_from = Fail)#%>%View()
```

```{r explore semester GPA mean by passfail}
#PASSED students' mean semester GPA
aac.crs%>%filter(!is.na(passfail))%>%#remove anything that was not defined by pass or fail
  group_by(term,coursecode,passfail)%>%
  summarise(mn=round(mean(Semester_GPA,na.rm=TRUE),digits=1))%>%
  filter(passfail%in%c("Pass"))%>%
  pivot_wider(names_from = passfail, values_from = mn)%>%
  pivot_wider(names_from = term,values_from = Pass)#%>%View()
#FAILED students' mean semester GPA
aac.crs%>%filter(!is.na(passfail))%>%#remove anything that was not defined by pass or fail
  group_by(term,coursecode,passfail)%>%
  summarise(mn=round(mean(Semester_GPA,na.rm=TRUE),digits=1))%>%
  filter(passfail%in%c("Fail"))%>%
  pivot_wider(names_from = passfail, values_from = mn)%>%
  pivot_wider(names_from = term,values_from = Fail)#%>%View()
```

## AAC103 Pass rate for students with different semester GPA

```{r tab.semgpa_pass}
#Rate of passing AAC103 for different semester GPA
tab.semgpa_pass<-aac.crs%>%filter(!is.na(passfail),coursecode=="AAC103")%>%#remove anything that was not defined by pass or fail
  group_by(term,semGPA,passfail)%>%summarise(cnt=n())%>%
  mutate(prt=formattable::percent(cnt/sum(cnt),digits = 0))%>%
  filter(passfail=="Pass")%>%select(-passfail,-cnt)%>%
  pivot_wider(names_from = semGPA,values_from = prt)%>%
  mutate(Diff=`> 2`-`< 2`)%>%select(term,`> 2`,`< 2`,Diff)%>%
  rename("Semester GPA >2"="> 2","Semester GPA <2"="< 2","Difference"="Diff")

```

```{r static_tab.semgpa_pass}
static_tab.semgpa_pass<-tab.semgpa_pass%>%
kbl(align = "c",booktabs = T,label="tab.semgpa_pass",#in-text reference
    caption = "AAC103 pass rates by semester GPA", #table title
    col.names =c("",names(tab.semgpa_pass[2:ncol(tab.semgpa_pass)]))) %>%#header names
#set overall style
  kable_styling(latex_options = c('hold_position'),bootstrap_options = c("striped", "hover", "condensed", "responsive"),
              full_width = F, fixed_thead = T, font_size = 12)%>%
#set header row row_spec(0,align = "c",color="black")%>%
#set first column: 
  column_spec(1, border_right = F, background = "white", width = "7em",color="black")%>%
#set difference column:
column_spec(4, width = "4em", background = if_else(tab.semgpa_pass[4]>.5,color_grey,if_else(tab.semgpa_pass[4]>.3,color_greylight,"white")))

#apply cf_color to multi columns
for (i in 2:3){
static_tab.semgpa_pass<-column_spec(
  kable_input=static_tab.semgpa_pass,
  column=i,color = "black",width = "4em",
  background =cf_color(tab.semgpa_pass[i],a=.9,b=.8))
i=i+1
static_tab.semgpa_pass}
```

```{r showviz.semgpa_pass, include=TRUE}
static_tab.semgpa_pass
```

Students with a semester GPA higher than 2.0 usually have a
`r min(tab.semgpa_pass$Difference)` to
`r max(tab.semgpa_pass$Difference)` higher AAC 103 pass rate than
students with a semester GPA below 2.0.

# Semester GPA

```{r tab.semGPA}
tab.semGPA<-aac.crs%>%filter(!is.na(passfail))%>%
  group_by(coursecode,term,semGPA)%>%summarise(cnt=n())%>%
  mutate(prt=formattable::percent(cnt/sum(cnt),digits = 0))%>%
  filter(semGPA=="> 2")%>%select(-semGPA,-cnt)

tab.semGPA_avg<-tab.semGPA%>%group_by(coursecode)%>%
  summarise(Average=mean(prt))

tab.semGPA<-left_join(tab.semGPA,tab.semGPA_avg)%>%
  #rename("Semester GPA >2"="prt")%>%
  pivot_wider(names_from = term,values_from = prt)%>%
   select(coursecode,Average,`2018 Fall`,`2019 Spring`,`2019 Fall`,`2020 Spring`,`2020 Fall`,`2021 Spring`,`2021 Fall`,`2022 Spring`)
```

```{r static_tab.semGPA}
static_tab.semGPA<-tab.semGPA%>%
kbl(align = "c",booktabs = T,label="tab.semGPA",#in-text reference
    caption = "Percentage of students with a higher than 2.0 semester GPA", #table title
    col.names =c("",names(tab.semGPA)[2:ncol(tab.semGPA)])) %>%#header names
#set overall style
  kable_styling(latex_options = c('hold_position'),bootstrap_options = c("striped", "hover", "condensed", "responsive"),
              full_width = F, fixed_thead = T, font_size = 12)%>%
#set header row row_spec(0,align = "c",color="black")%>%
#set first column: 
  column_spec(1, bold = T, border_right = F, background = "white", width = "4em",color="black")

#apply cf_color to multi columns
for (i in 2:ncol(tab.semGPA)){
static_tab.semGPA<-column_spec(
  kable_input=static_tab.semGPA,
  column=i,color = "black",width = "3em",
  background =cf_color(tab.semGPA[i],a=.9,b=.8))
i=i+1
static_tab.semGPA}
```

```{r showviz.semGPA, include=TRUE}
static_tab.semGPA
```

An average of
`r tab.semGPA_avg[tab.semGPA_avg$coursecode=="AAC102","Average"][[1]][1]`
of students in AAC102 course have a higher than 2.0 semester GPA over
the past 5 years. The average percentage of higher than 2.0 semester GPA
for AAC103 course is
`r tab.semGPA_avg[tab.semGPA_avg$coursecode=="AAC103","Average"][[1]][1]`.

## Semester GPA for students who pass or fail AAC103

```{r tab.semGPA_passfail}
#whether taking AAC would help semester GPA increase
tab.semGPA_passfail<-aac.crs%>%filter(!is.na(passfail),coursecode=="AAC103")%>%
  group_by(term,passfail,semGPA)%>%summarise(cnt=n())%>%
  mutate(prt=formattable::percent(cnt/sum(cnt),digits = 0))%>%
  filter(semGPA=="> 2")%>%select(-semGPA,-cnt)

tab.semGPA_passfail_avg<-tab.semGPA_passfail%>%group_by(passfail)%>%summarise(Average=mean(prt))

tab.semGPA_passfail<-left_join(tab.semGPA_passfail,tab.semGPA_passfail_avg)%>%
  pivot_wider(names_from = term,values_from = prt)%>%
   select(passfail,Average,`2018 Fall`,`2019 Spring`,`2019 Fall`,`2020 Spring`,`2020 Fall`,`2021 Spring`,`2021 Fall`,`2022 Spring`)
```

```{r static_tab.semGPA_passfail}
static_tab.semGPA_passfail<-tab.semGPA_passfail%>%
kbl(align = "c",booktabs = T,label="tab.semGPA_passfail",#in-text reference
    caption = "Percentage of students with a higher than 2.0 semester GPA among students by pass/ fail status", #table title
    col.names =c("",names(tab.semGPA_passfail)[2:ncol(tab.semGPA_passfail)])) %>%#header names
#set overall style
  kable_styling(latex_options = c('hold_position'),bootstrap_options = c("striped", "hover", "condensed", "responsive"),
              full_width = F, fixed_thead = T, font_size = 12)%>%
#set header row row_spec(0,align = "c",color="black")%>%
#set first column: 
  column_spec(1, bold=T, border_right = F, background = "white", width = "2em",color="black")

for (i in 2:ncol(tab.semGPA_passfail)){
static_tab.semGPA_passfail<-column_spec(
  kable_input=static_tab.semGPA_passfail,
  column=i,color = "black",width = "3em",
  background =cf_color(tab.semGPA_passfail[i],a=.9,b=.8))
i=i+1
static_tab.semGPA_passfail}
```

```{r showviz.semGPA_passfail, include=TRUE}
static_tab.semGPA_passfail
```

Among students who passed AAC103, an average of
`r tab.semGPA_passfail_avg[tab.semGPA_passfail_avg$passfail=="Pass","Average"][[1]][1]`
of students have a higher than 2.0 semester GPA. In contrast, only an
average of
`r tab.semGPA_passfail_avg[tab.semGPA_passfail_avg$passfail=="Fail","Average"][[1]][1]`
students have a higher than 2.0 semester GPA among students who failed
AAC103.

```{r hide tab.pass_semgpa}
#Rate of passing AAC103 for different semester GPA: hard to interpretate -- hide
tab.pass_semgpa<-aac.crs%>%filter(!is.na(passfail),coursecode=="AAC103")%>%#remove anything that was not defined by pass or fail
  group_by(term,passfail,semGPA)%>%summarise(cnt=n())%>%
  mutate(prt=formattable::percent(cnt/sum(cnt),digits = 0))%>%
  filter(semGPA=="> 2")%>%select(-semGPA,-cnt)%>%
  pivot_wider(names_from = passfail,values_from = prt)

tab.pass_semgpa$term<-tab.pass_semgpa$term%>%str_replace("FALL","Fall")%>%str_replace("SPRING","Spring")
```

```{r explore semester GPA categories}
#semGPA that lower than 2.0
aac.crs%>%filter(!is.na(passfail))%>%#remove anything that was not defined by pass or fail
  group_by(term,coursecode,passfail,semGPA)%>%summarise(cnt=n())%>%
  mutate(prt=formattable::percent(cnt/sum(cnt),digits = 0))%>%
  filter(passfail%in%c("Pass"))%>%
  select(-cnt)%>%pivot_wider(names_from = passfail, values_from = prt)%>%
  pivot_wider(names_from = term,values_from = Pass)%>%
  filter(semGPA=="lower than 2")%>%select(-semGPA)#%>%View()

#How many students FAIL AAC103 and finish the semester with a 2.0 or higher vs lower than a 2.0 semester GPA
#count for those who FAILED,  
#semGPA that higher than 2.0
aac.crs%>%filter(!is.na(passfail))%>%#remove anything that was not defined by pass or fail
  group_by(term,coursecode,passfail,semGPA)%>%summarise(cnt=n())%>%
  mutate(prt=formattable::percent(cnt/sum(cnt),digits = 0))%>%
  filter(passfail%in%c("Fail"))%>%
  select(-cnt)%>%pivot_wider(names_from = passfail, values_from = prt)%>%
  pivot_wider(names_from = term,values_from = Fail)%>%
  filter(semGPA=="higher than 2")%>%select(-semGPA)#%>%View()
#semGPA that lower than 2.0
aac.crs%>%filter(!is.na(passfail))%>%#remove anything that was not defined by pass or fail
  group_by(term,coursecode,passfail,semGPA)%>%summarise(cnt=n())%>%
  mutate(prt=formattable::percent(cnt/sum(cnt),digits = 0))%>%
  filter(passfail%in%c("Fail"))%>%
  select(-cnt)%>%pivot_wider(names_from = passfail, values_from = prt)%>%
  pivot_wider(names_from = term,values_from = Fail)%>%
  filter(semGPA=="lower than 2")%>%select(-semGPA)#%>%View()
```

# Retaking AAC103

## Pass rate when retaking

```{r tab.retakepass}
#pass rate across cols
pass.1st<-retake.change%>%filter(!is.na(grade_1sttime))%>%
  count(grade_1sttime)%>%mutate(prt=n/sum(n))%>%
  filter(grade_1sttime=="Pass")%>%select(-n,-grade_1sttime)%>%rename(`1st`=prt)

pass.2nd<-retake.change%>%filter(!is.na(grade_2ndtime))%>%
  count(grade_2ndtime)%>%mutate(prt=n/sum(n))%>%
  filter(grade_2ndtime=="Pass")%>%select(-n,-grade_2ndtime)%>%rename(`2nd`=prt)

pass.3rd<-retake.change%>%filter(!is.na(grade_3rdtime))%>%
  count(grade_3rdtime)%>%mutate(prt=n/sum(n))%>%
  filter(grade_3rdtime=="Pass")%>%select(-n,-grade_3rdtime)%>%rename(`3rd`=prt)

pass.4th<-retake.change%>%filter(!is.na(grade_4thtime))%>%
  count(grade_4thtime)%>%mutate(prt=n/sum(n))%>%
  filter(grade_4thtime=="Pass")%>%select(-n,-grade_4thtime)%>%rename(`4th`=prt)

pass.5th<-retake.change%>%filter(!is.na(grade_5thtime))%>%
  count(grade_5thtime)%>%mutate(prt=n/sum(n))%>%
  filter(grade_5thtime=="Pass")%>%select(-n,-grade_5thtime)%>%rename(`5th`=prt)

tab.retakepass<-cbind(pass.1st,pass.2nd,pass.3rd,pass.4th,pass.5th)%>%
  mutate(across(everything(),~percent(.x,digits = 0)))%>%
  pivot_longer(cols = `1st`:`5th`,names_to = "Times", values_to = "Pass rate")

N<-c(sum(is.na(retake.change$grade_1sttime)==FALSE),
          sum(is.na(retake.change$grade_2ndtime)==FALSE),
          sum(is.na(retake.change$grade_3rdtime)==FALSE),
          sum(is.na(retake.change$grade_4thtime)==FALSE),
          sum(is.na(retake.change$grade_5thtime)==FALSE))

tab.retakepass<-tab.retakepass%>%mutate(N)%>%filter(N>10)
```

```{r static_tab.retakepass}
static_tab.retakepass<-tab.retakepass%>%
kbl(align = "c",booktabs = T,label="tab.retakepass",#in-text reference
    caption = "AAC103 pass rates for iteration of the course", #table title
    col.names =c(names(tab.retakepass))) %>%#header names
#set overall style
  kable_styling(latex_options = c('hold_position'),bootstrap_options = c("striped", "hover", "condensed", "responsive"),
              full_width = F, fixed_thead = T, font_size = 12)%>%
#set header row row_spec(0,align = "c",color="black")%>%
#set first column: 
  column_spec(1, bold=T, border_right = F, background = "white", color="black")%>%
  column_spec(2,background = cf_color(tab.retakepass[2],a=.9,b=.8))%>%
  column_spec(3,width = "3em")
```

```{r showviz.retakepass, include=TRUE}
static_tab.retakepass
```

::: callout-note
From the analysis, we found `r N[4]` students took AAC103 4 times and
`r N[5]` took the course 5 times. Due to the small sample size, we
excluded those students from this analysis. The following tables
reported students who took AAC103 for the 1st, 2nd, and 3rd time.
:::

First time takers has the highest pass rate of
`r tab.retakepass[1,"Pass rate"]%>%percent(digit=0)`, while the pass
rate decreased to `r tab.retakepass[2,"Pass rate"]%>%percent(digit=0)`
and `r tab.retakepass[3,"Pass rate"]%>%percent(digit=0)` when students
completed the course for the second and third time. In other words,
AAC103's pass rate decreasedfor students that completed the course
multiple times.

## Semester GPA when retaking

```{r tab.retake_semGPA}
#pass rate across cols
semGPA.1st<-retake.change%>%filter(!is.na(semGPA_1sttime))%>%
  count(semGPA_1sttime)%>%mutate(prt=n/sum(n))%>%
  filter(semGPA_1sttime=="> 2")%>%select(-n,-semGPA_1sttime)%>%rename(`1st`=prt)

semGPA.2nd<-retake.change%>%filter(!is.na(semGPA_2ndtime))%>%
  count(semGPA_2ndtime)%>%mutate(prt=n/sum(n))%>%
  filter(semGPA_2ndtime=="> 2")%>%select(-n,-semGPA_2ndtime)%>%rename(`2nd`=prt)

semGPA.3rd<-retake.change%>%filter(!is.na(semGPA_3rdtime))%>%
  count(semGPA_3rdtime)%>%mutate(prt=n/sum(n))%>%
  filter(semGPA_3rdtime=="> 2")%>%select(-n,-semGPA_3rdtime)%>%rename(`3rd`=prt)

semGPA.4th<-retake.change%>%filter(!is.na(semGPA_4thtime))%>%
  count(semGPA_4thtime)%>%mutate(prt=n/sum(n))%>%
  filter(semGPA_4thtime=="> 2")%>%select(-n,-semGPA_4thtime)%>%rename(`4th`=prt)

semGPA.5th<-retake.change%>%filter(!is.na(semGPA_5thtime))%>%
  count(semGPA_5thtime)%>%mutate(prt=n/sum(n))%>%
  filter(semGPA_5thtime=="> 2")%>%select(-n,-semGPA_5thtime)%>%rename(`5th`=prt)

tab.retake_semGPA<-cbind(semGPA.1st,semGPA.2nd,semGPA.3rd,semGPA.4th,semGPA.5th)%>%
  mutate(across(everything(),~percent(.x,digits = 0)))%>%
  pivot_longer(cols = `1st`:`5th`,names_to = "Times", values_to = "Semester GPA >2")

tab.retake_semGPA<-tab.retake_semGPA%>%mutate(N)%>%filter(N>10)
```

```{r static_tab.retake_semGPA}
static_tab.retake_semGPA<-tab.retake_semGPA%>%
kbl(align = "c",booktabs = T,label="tab.retake_semGPA",#in-text reference
    caption = "Higher than 2.0 Semester GPA for iteration of the course", #table title
    col.names =c(names(tab.retake_semGPA))) %>%#header names
#set overall style
  kable_styling(latex_options = c('hold_position'),bootstrap_options = c("striped", "hover", "condensed", "responsive"),
              full_width = F, fixed_thead = T, font_size = 12)%>%
#set header row row_spec(0,align = "c",color="black")%>%
#set first column: 
  column_spec(1, bold=T, border_right = F, background = "white", color="black")%>%
  column_spec(2,width = "4em",background = cf_color(tab.retake_semGPA[2],a=.9,b=.8))%>%
  column_spec(3,width = "3em")
```

```{r showviz.retake_semGP, include=TRUE}
static_tab.retake_semGPA
```

The percentage of higher than 2.0 semester GPA students among AAC103
retakers range from
`r min(tab.retake_semGPA[,"Semester GPA >2"])%>%percent(digit=0)` to
`r max(tab.retake_semGPA[,"Semester GPA >2"])%>%percent(digit=0)`, with
the second time being the highest percentage of higher than 2.0 GPA.

```{r explore retake.aac103}
#how many passed/semgpa for the first time?
retake.change%>%group_by(semGPA_1sttime,grade_1sttime)%>%summarise(cnt=n())%>%mutate(prt=formattable::percent(cnt/sum(cnt),digits = 0))%>%select(-cnt)%>%
  pivot_wider(names_from = grade_1sttime, values_from = prt)#%>%View()#around 14-21% students failed and a majority passed aac103; difference between different semGPA groups is only 7%
#report N
retake.change%>%count(semGPA_1sttime)


#compared grade in 2nd to 1st, Increase/Decrease/Same?
retake.change%>%group_by(grade_1to2)%>%summarise(cnt=n())%>%mutate(prt=formattable::percent(cnt/sum(cnt),digits = 0))%>%select(-cnt)#%>%View()#

#compared semgpa in 2nd to 1st, Increase/Decrease/Same?
retake.change%>%group_by(semGPA_1to2)%>%summarise(cnt=n())%>%mutate(prt=formattable::percent(cnt/sum(cnt),digits = 0))%>%select(-cnt)#%>%View()#



#how many have a 3rd term
retake.change%>%filter(!is.na(grade_2to3))%>%nrow()

#compared grade in 3rd to 2nd, Increase/Decrease/Same?
retake.change%>%filter(!is.na(grade_2to3))%>%
  group_by(grade_2to3)%>%summarise(cnt=n())%>%mutate(prt=formattable::percent(cnt/sum(cnt),digits = 0))%>%select(-cnt)#%>%View()#

#compared semgpa in 3rd to 2nd, Increase/Decrease/Same?
retake.change%>%filter(!is.na(semGPA_2to3))%>%
  group_by(semGPA_2to3)%>%summarise(cnt=n())%>%mutate(prt=formattable::percent(cnt/sum(cnt),digits = 0))%>%select(-cnt)#%>%View()#




#how many have a 4th term
retake.change%>%filter(!is.na(grade_3to4))%>%nrow()

#compared grade in 3rd to 2nd, Increase/Decrease/Same?
retake.change%>%filter(!is.na(grade_3to4))%>%
  group_by(grade_3to4)%>%summarise(cnt=n())%>%mutate(prt=formattable::percent(cnt/sum(cnt),digits = 0))%>%select(-cnt)#%>%View()#

#compared semgpa in 3rd to 2nd, Increase/Decrease/Same?
retake.change%>%filter(!is.na(semGPA_3to4))%>%
  group_by(semGPA_3to4)%>%summarise(cnt=n())%>%mutate(prt=formattable::percent(cnt/sum(cnt),digits = 0))%>%select(-cnt)#%>%View()#




#how many have a 5th term
retake.change%>%filter(!is.na(grade_4to5))%>%nrow()

#compared grade in 3rd to 2nd, Increase/Decrease/Same?
retake.change%>%filter(!is.na(grade_4to5))%>%
  group_by(grade_4to5)%>%summarise(cnt=n())%>%mutate(prt=formattable::percent(cnt/sum(cnt),digits = 0))%>%select(-cnt)#%>%View()#

#compared semgpa in 3rd to 2nd, Increase/Decrease/Same?
retake.change%>%filter(!is.na(semGPA_4to5))%>%
  group_by(semGPA_4to5)%>%summarise(cnt=n())%>%mutate(prt=formattable::percent(cnt/sum(cnt),digits = 0))%>%select(-cnt)#%>%View()#

```

# Summary

+ Among the past 5 years (2018 Fall to 2022 Spring), the AAC103 course
has an average enrollment of
`r n_aacenroll[n_aacenroll$coursecode=="AAC103","Average"][[1]][1]`
students.

+ The average pass rate for AAC103 course is
`r mean(tab.aacpass_avg$Average)%>%percent(digit=0)`.

+ Students with a higher than 2.0 semester GPA usually have a
`r min(tab.semgpa_pass$Difference)` to
`r max(tab.semgpa_pass$Difference)` higher AAC103 pass rate than
students with a lower than 2.0 semester GPA.

+ An average of
`r tab.semGPA_avg[tab.semGPA_avg$coursecode=="AAC103","Average"][[1]][1]`
of students in the AAC103 course have a higher than 2.0 semester GPA.

+ Among those who pass AAC103,
`r tab.semGPA_passfail_avg[tab.semGPA_passfail_avg$passfail=="Pass","Average"][[1]][1]`
have a higher than 2.0 GPA, which means
`r 1-tab.semGPA_passfail_avg[tab.semGPA_passfail_avg$passfail=="Pass","Average"][[1]][1]`
do not have a high enough semester GPA. Among those who failed AAC103,
`r tab.semGPA_passfail_avg[tab.semGPA_passfail_avg$passfail=="Fail","Average"][[1]][1]`
still have a higher than 2.0 semester GPA (without succeeding in the
AAC103 course).

+ Taking AAC103 the second and third time does not improve the pass rate
for that particular course. First time takers have the highest pass rate
of `r tab.retakepass[1,"Pass rate"]%>%percent(digit=0)`, while the pass
rate decreased to `r tab.retakepass[2,"Pass rate"]%>%percent(digit=0)`
and `r tab.retakepass[3,"Pass rate"]%>%percent(digit=0)` when students
completed the course for the second and third time.

+ The percentage of obtaining a higher than 2.0 semester GPA are similar
for students who take AAC103 for the first and second time, which are
`r tab.retake_semGPA[1,"Semester GPA >2"]%>%percent(digit=0)` and
`r tab.retake_semGPA[2,"Semester GPA >2"]%>%percent(digit=0)`.

Please contact lzhou\@lasell.edu for questions
