---
title: "AlumTracking"
author: "Linli Zhou"
date: "2022-08-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load package}
library(readxl)
library(dplyr)
```

# Research question: 
1. Postgrad Life Basic: 1) How many alumni are employed/unemployed/continue-ed across years? 2) What are the most popular title/degree and employers/institutions?

- variables needed: 1) EMPLOYED, TITLE, EMPLOYER; 2) not/continue-ed+institution/degree
- data source: 1) historical.data append with survey and linkedin; 2)clearinghouse

2. What are alum's top interests in Lasell alum activities?

- variables needed: INTEREST
- data source: historical.data append with survey

3. Employ-ability/Continue-edu characteristics: 1) Which major/degree are most employable across different years for grad and undergrad? 2) How demographic (gender, race) correlate with employment?

- variables needed: level/gradyear,school/major/degree, gender/race
- data source: ipeds.complete.16-current

# Data Prep 


## GD Alumni 6 month

```{r read gd6m data}
#gd6m target data
#find sheet
excel_sheets("/Users/linlizhou/Documents/LASELL/data/alumni/gd6m/2021Grad6m_historic.xlsx")#only one sheet
#read historical data
gd6m<-read_excel("/Users/linlizhou/Documents/LASELL/data/alumni/gd6m/2021Grad6m_historic.xlsx")

#read survey data
survey<-read_excel("/Users/linlizhou/Documents/LASELL/data/alumni/gd6m/2021Gd6mSurvey_renamed.xlsx")

#read linkedin data
linkedin<-read_excel("/Users/linlizhou/Documents/LASELL/data/alumni/gd6m/2021Gd6mLinkedin_rename.xlsx")
```

```{r gd6m-select vars}
#######historical data 
gd6m_s<-gd6m%>%select(
  PC_ID, 
  `Employment Recode`, #EMPLOYED VAR -- changed to original var containing schooling info
  Employment, #placeholder for full/part time
  Employment_Organization, #EMPLOYER VAR
  Employment_JobTitle, #TITLE VAR
  Employed_income...30, #INCOME CAT VAR
  Education_attendance, #add EDUCATION VAR
  Education_institution, #add INSTITUTION VAR
  Education_Degree,#add DEGREE VAR
  starts_with("Interest_")#INTEREST VAR
)
#rename for consistency across all df
names(gd6m_s)<-c("PCID","Employment","Full/Part Time","Employer","Title","Income","Further Education","Institution","Degree", names(gd6m)[73:82])

######survey
survey_s<-survey%>%select(
  PC_ID,
  `Employment Recode`,# changed to original var containing schooling info
  Employment,# full/part time
  Employment_Organization,
  Employment_JobTitle,
  Employed_income,
  Education_attendance, #add EDUCATION VAR
  Education_institution, #add INSTITUTION VAR
  Education_Degree,#add DEGREE VAR
  starts_with("Interest_")
  )
#rename for consistency across all df
names(survey_s)<-names(gd6m_s)

#######select linkedin to be linkedin_s
linkedin_s<-linkedin%>%select(
  PC_ID,
  Employment,
  Employment_Organization,
  Employment_JobTitle,
  Education_attendance, #add EDUCATION VAR
  Education_institution, #add INSTITUTION VAR
  Education_Degree,#add DEGREE VAR
)
#rename for consistency across all df
names(linkedin_s)<-c("PCID","Employment","Employer","Title","Further Education","Institution","Degree")

#check employment
linkedin_s%>%group_by(Employment)%>%count()
#mutate full/part time
linkedin_s<-linkedin_s%>%mutate(`Full/Part Time`=case_when(
  Employment=="FT"~"Full Time",
  Employment=="PT"~"Part Time"
))
```

```{r merge gd6m}
#check rows
nrow(gd6m_s)+nrow(survey_s)+nrow(linkedin_s)#1404 rows
#join_all by all common cols
gd6m_m<-plyr::join_all(list(gd6m_s,survey_s,linkedin_s),type="full",match="all")#1404 rows; must use list(dfs)

#save
writexl::write_xlsx(gd6m_m,"/Users/linlizhou/Documents/LASELL/data/alumni/gd6m_merged.xlsx")
#rm unused cols
rm(gd6m,gd6m_s,survey,survey_s,linkedin,linkedin_s)
```



## GD 5 year
```{r read gd5yr full data and select/rename var}
#read data
gd5yr<-read_excel("/Users/linlizhou/Documents/LASELL/data/alumni/grad5y_full.xlsx")
#names
names(gd5yr)
gd5yr_s<-gd5yr%>%select(
  PCID, 
  names(gd5yr)[8], #EMPLOYED VAR
  names(gd5yr)[9],#full/part time
  `Employer Name`, #EMPLOYER VAR
  Title, #TITLE VAR
  names(gd5yr)[17], #INCOME CAT VAR
  `Further Education`,#add EDUCATION var
  names(gd5yr)[30], #add INSTITUTION var
  Degree...31, # add DEGREE var
  names(gd5yr)[46:49],#INTEREST VAR
  names(gd5yr)[51:56]#INTEREST VAR
)
#rename for consistency across all df
names(gd5yr_s)<-names(gd6m_m)
```



## UG 6 month

```{r read data}
#####ug6m data
#which is data sheet
excel_sheets("/Users/linlizhou/Documents/LASELL/data/alumni/ug6m/bd.xlsx")
#read data
ug6m<-read_excel("/Users/linlizhou/Documents/LASELL/data/alumni/ug6m/bd.xlsx",sheet = "AllData")

######survey data
#read data
excel_sheets("/Users/linlizhou/Documents/LASELL/data/alumni/ug6m/survey.xlsx")
survey<-read_excel("/Users/linlizhou/Documents/LASELL/data/alumni/ug6m/survey.xlsx",sheet = "Sheet1")

######linkedin data
#read data
linkedin<-read_excel("/Users/linlizhou/Documents/LASELL/data/alumni/ug6m/linkedin.xlsx")
#rm
rm(gd5yr)
```

```{r select var and rename}
#####ug6m data
#check names
names(ug6m)
#select
ug6m_s<-ug6m%>%select(PCID,
                      names(ug6m)[9:10],#employment and ft/pt
                      names(ug6m)[12:13],#employer and title
                      names(ug6m)[18],#income
                      names(ug6m)[25],#further edu
                      names(ug6m)[27:28],#institution and degree
                      names(ug6m)[42:45],
                      names(ug6m)[47:52])#omit 46th which is peer network
#rename to match other datasets (for later alrge merge)
names(ug6m_s)<-names(gd6m_m)


######survey data
#select data
survey<-survey%>%select(PCID,
                      names(ug6m)[9:10],#employment and ft/pt
                      names(ug6m)[12:13],#employer and title
                      names(ug6m)[18],#income
                      names(ug6m)[25],#further edu
                      names(ug6m)[27:28],#institution and degree
                      names(ug6m)[42:45],
                      names(ug6m)[47:52])#omit 46th which is peer network
#rename to match other datasets (for later alrge merge)
names(survey)<-names(gd6m_m)


######linkedin data
#select var
linkedin<-linkedin%>%select(`Power Campus ID`,
                            `Employed (FT/PT)`,
                            Employer,
                            Title,
                            `Pursuing Additional Ed (FT/PT)`,
                            Institution,
                            Degree
                            )%>%
  rename("PCID"=`Power Campus ID`,"Employment"=`Employed (FT/PT)`,"Further Education"=`Pursuing Additional Ed (FT/PT)`)
#check employment
linkedin%>%group_by(Employment)%>%count()
#mutate full/part time
linkedin<-linkedin%>%mutate(`Full/Part Time`=case_when(
  Employment=="FT"~"Full Time",
  Employment=="PT"~"Part Time"
))
```


```{r merge ug6m}
######merge
ug6m_m<-plyr::join_all(list(ug6m_s,survey,linkedin),type="full",match="first")#602 observation

#save
writexl::write_xlsx(ug6m_m,"/Users/linlizhou/Documents/LASELL/data/alumni/ug6m_merged.xlsx")
#rm
rm(ug6m,ug6m_s,linkedin,survey)
```



## UG 5year

```{r read data}
#read historical data
excel_sheets("/Users/linlizhou/Documents/LASELL/data/alumni/ug5y/db.xlsx")
ug5y<-read_excel("/Users/linlizhou/Documents/LASELL/data/alumni/ug5y/db.xlsx",sheet = "Data")

#####survey
#read data 
survey<-read_excel("/Users/linlizhou/Documents/LASELL/data/alumni/ug5y/survey.xlsx")

####linkedin
#which sheet to read
excel_sheets("/Users/linlizhou/Documents/LASELL/data/alumni/ug5y/linkedin.xlsx")
#read data
linkedin<-read_excel("/Users/linlizhou/Documents/LASELL/data/alumni/ug5y/linkedin.xlsx",sheet = "Sheet1")
```


```{r select var and rename}
##### historical data
#select vars
ug5y<-ug5y%>%select(PC_ID,
                    WorkStatus,#Employment
                    Employmenthours,#FT/PT
                    Organization,#employer
                    AnnualSalary,#income
                    `Attending_Post-GradEd`,#Further ed
                    Education_Degree,#degree
                    starts_with("Interest_"),-names(ug5y)[27])
#rename
names(ug5y)<-c("PCID","Employment","Full/Part Time","Employer","Income","Further Education","Degree",names(gd6m_m)[10:19])#names align with other 

#####survey
#names
names(survey)
survey<-survey%>%select(
  `Invite Custom Field 1`,#PCID
  names(survey)[54],#employment work status
  `Please describe your employment status:`,#ft/pt
  names(survey)[71],#employer
  names(survey)[70],#title
  names(survey)[74],#income
  names(survey)[128:129],#further education, institution
  names(survey)[133],#degree
  names(survey)[136:139],
  names(survey)[141:146]
)
#rename
names(survey)<-names(gd6m_m)

####linkedin
#select var and rename
linkedin<-linkedin%>%select(`Power Campus ID`,
                            `Employed (FT/PT)`,
                            Employer,
                            Title,
                            `Pursuing Additional Ed (FT/PT)`,
                            Institution,
                            Degree
                            )%>%
  rename("PCID"=`Power Campus ID`,"Employment"=`Employed (FT/PT)`,"Further Education"=`Pursuing Additional Ed (FT/PT)`)
#check employment
linkedin%>%group_by(Employment)%>%count()
#mutate full/part time
linkedin<-linkedin%>%mutate(`Full/Part Time`=case_when(
  Employment=="FT"~"Full Time",
  Employment=="PT"~"Part Time"
))
```


```{r merge ug5y}
######merge
ug5y_m<-plyr::join_all(list(ug5y,survey,linkedin),type="full",match="first")#602 observation

#save
writexl::write_xlsx(ug5y_m,"/Users/linlizhou/Documents/LASELL/data/alumni/ug5y_merged.xlsx")
#rm
rm(ug5y,linkedin,survey)
```


# Merge

```{r mutate 5y/6m col}
#read data

#add col to indicate the focus of outcome in each dataset
gd5yr_s<-gd5yr_s%>%mutate("Outcome Type"="5-Year Outcome")
ug5y_m<-ug5y_m%>%mutate("Outcome Type"="5-Year Outcome")
gd6m_m<-gd6m_m%>%mutate("Outcome Type"="6-Month Outcome")
ug6m_m<-ug6m_m%>%mutate("Outcome Type"="6-Month Outcome")
```

```{r merge large dataset}
#merge
alum<-plyr::join_all(list(gd5yr_s,gd6m_m,ug5y_m,ug6m_m),type="full")
#remove
rm(gd5yr_s,gd6m_m,ug6m_m,ug5y_m)
#save
writexl::write_xlsx(alum,"/Users/linlizhou/Documents/LASELL/data/alumni/alum_raw.xlsx")
```

# Clean Large Dataset
```{r interest var -mutate based on other col}
#combine multi-col into one INTEREST var
alum<-alum%>%mutate(Interest=case_when(
  Interest_AlumnCareerNetwork=="Alumni Career Network"~"Career Network",
  
  Interest_JobPosts=="Posting jobs or internships listings for Lasell students"~"Post Jobs",
  
  Interest_CareerFair=="Career Fair" | 
    Interest_CollegeFair=="College Fair"~"Career/College Fair",
  
  Interest_Volunteering=="Volunteering at Lasell events" | 
    Interest_CampusPresentation=="Campus presentation to students" | 
    Interest_Mentor=="Being a mentor to current students" ~"Volunteer",
  
Interest_SocialActivities == "Social activities (sporting events, reunion, etc.)" | 
Interest_Recreational=="Recreational programs (kayaking, hiking, etc.)" ~ "Social",
  
   Interest_AcademicCultural=="Academic/Cultural (lectures, theater, etc.)" ~ "Academic/Cultural"
   ))

#remove all "Interest_" subcols and only keep Interest (mutated conclusive col)
alum<-alum%>%select(-starts_with("Interest_"))
```


```{r recode employment}
#inspect employment
alum%>%group_by(Employment)%>%count() #%>%tail(14) to look at the tails

#recode using case_when (mutate same variable name to replace the origional Employment)
alum<-alum%>%mutate(Employment=case_when(
  stringr::str_detect(alum$Employment, "^[Ee][Mm][Pp]")~ "Employed",#start with emp no matter upper/lower case
  stringr::str_detect(alum$Employment, "^[Ii]ntern")~ "Employed",#start with emp no matter upper/lower case
  Employment %in% c("Contract","Freelance","Internship","FT","PT","Self","Temp","Yes") ~ "Employed",
  
  Employment %in% c("Additional Eduation","Additional Education","Edu","Further Ed","n/a","Other","UNK","Unknown") ~ "Unknown",
  
  Employment %in% c("No Emp No Edu","Unemployed","Neither employed nor pursing further study","No","Pursuing further study only, not employed")~"Unemployed"))
#rename NA with subset 
alum$Employment[is.na(alum$Employment)]="Unknown"#recheck looks right
```

```{r recode FT/PT}
#inspect FT/PT
alum%>%group_by(`Full/Part Time`)%>%count() %>%tail(18) #to look at the tails

#recode using case_when (mutate same variable name to replace the origional Employment)
alum<-
  alum%>%mutate(`Full/Part Time`=case_when(
    grepl(paste(c("full time|full-time|Full time|Full Time|FT"), collapse="|"), alum$`Full/Part Time` ) == TRUE ~ "Full time",
    stringr::str_detect(alum$`Full/Part Time`, "^[Ff]ull")~ "Full time",
  grepl("part time|part-time|Part Time|PT", alum$`Full/Part Time`) == TRUE ~ "Part time",
  stringr::str_detect(alum$`Full/Part Time`, "^[Pp]art")~ "Part time"))#%>%group_by(`Full/Part Time`,ft)%>%count()%>%tail(18) to check directly

#rename NA with subset 
alum$`Full/Part Time`[is.na(alum$`Full/Part Time`)]="Unknown"#recheck looks right
```


```{r recode income}
######inspect income
alum%>%group_by(Income)%>%count()#observe "to" and "-" interchangabily
#replace to with -
alum$Income<-gsub("to","-",alum$Income)

#recode other out of the "to" pattern 
alum$Income<-alum$Income%>%recode(
   "$100,000 or over" = ">$100,000","$100,000 or more" = ">$100,000",
  "$90,000 or over"="$90,000 - $99,999",
  "$80,000 or over"= "$80,000 - $89,999",
  "Less than $40,000"="$30,000 - $39,999",
  "$20,000 - $29,999"="Less than $30,000",
  "$24,999 or less"="Less than $30,000",
  "Less than $20,000"= "Less than $30,000",
  "Prefer not - state"="Unknown",
  "I prefer not - state"="Unknown"
)

#recode NA
alum$Income[is.na(alum$Income)]="Unknown"#recheck looks right

#check
alum%>%group_by(Income)%>%count()
```


## Add IPEDS.Complete

```{r ipeds for merge clean df}
#read ipeds data (prepared with PCID, level, degree, major, gradate, race, gender, school)
ipeds.16crt<-read_excel("/Users/linlizhou/Documents/LASELL/data/completion/16-current.xlsx")
#merge to alum.m large dataset
alum.m<-plyr::join_all(list(alum,ipeds.16crt),type="left")
```


```{r save large dataset}
writexl::write_xlsx(alum.m,"/Users/linlizhou/Documents/LASELL/data/alumni/alum.xlsx")
```



# Cleaning Alum Data

```{r}
alum<-read_excel("/Users/linlizhou/Documents/LASELL/data/alumni/alum.xlsx")

```















# Static Graphs

```{r}

```

# Shiny

```{r set up}
library(shiny)

#####DO NOT set your working directory in this app. This is will cause a problem when you try to upload the app online.

####data import: best practice is to have your .csv or other data file in the same directory as your .r file for the shiny app
```

```{r UI}
ui <- fluidPage(#start fluidPage
    titlePanel("Old Faithful Geyser Data"),# title
    sidebarLayout(#layout
      
#side appearance (input place)
sidebarPanel(
  
#####option 1-one value input  
  sliderInput(
    inputId="bins", # Slider: waiting for input of number of bins to define bins
    label="Number of bins:",#Slider title
    min = 1, max = 50, value = 30, sep="")    ),#Slider appearance, end of sliderInput

#####option 2-multiple value input
  checkboxGroupInput(#checkbox input
    inputId="checked_groups",#Input: waiting for input of checked boxes
    label="Which groups do you want to display?",#Slider title
    choices=c("a","b","c"),selected=c("a","b","c")  ),#Slider appearance; end of checkboxGroupInput

#main appearance (output place)
mainPanel(plotOutput("distPlot"))# the plot will be defined in server
    
  ) #end of sidebar layout
    )#end of fluidPage
```

```{r}
    inputPanel(
      )
```


```{r Server}
server <- function(input, output) {
  output$distPlot <- #define the output$name, call in UI
    renderPlot({#start defining plot
      
#####option 1- bin histogram
# select the target variable as list      
x    <- dat[, 2]
# inputed number of bins (e.g. number break into n+1 parts for n bins).
bins <- seq(min(x), max(x), length.out = input$bins + 1)
# draw histogram with the specified number of bins
hist(x, breaks = bins, col = 'darkgray', border = 'white')

######option 2-ggplot
#start plot
ggplot(
  #select the target variable given the UI input
  filter(dat,TargetVariable==input$my_cong),#single-option
  #filter(dat, Group %in% input$checked_groups)#check box
  
  #define the plot aesethics, #end plot + #a way to display  
  aes(x=Ideology,color=Party,fill=Party)  )+ geom_density(alpha=.5) 

      })#end of defining plot
    }#end of function
```


```{r Run Shiny}
# Run the application 
shinyApp(ui = ui, server = server)

```

