---
title: "**Science and Inquiry Knowledge and Perspectives (SIKP) Courses Review** \\vspace{-3cm}" 
format: 
  pdf:
    documentclass: article
    classoption: []
    fig-width: 8
    geometry:
      - top=25mm
      - bottom=20mm
      - left=15mm
      - right=15mm
      - textwidth=4.5in
    keep-md: true
    include-in-header:
      - text: |
          \usepackage{titling}
          \setlength{\droptitle}{-1.5in}
          \pretitle{\begin{center}
          \includegraphics[height=1in]{/Users/linlizhou/Documents/Rprojects/IR.png}\LARGE\\}
      - text: |
          \usepackage{fancyhdr}
          \addtolength{\headheight}{0.7cm}
    
          \pagestyle{fancy} 
          \fancyhead{}
          \fancyfoot{}
    
          \fancyhead[LO]{\includegraphics[height=1.3cm]{/Users/linlizhou/Documents/Rprojects/IR.png}}
          \fancyhead[RE]{\vspace{4mm}\textbf{AAC Courses Review}}
          \fancyfoot[C]{\thepage}
    
          \renewcommand{\headrulewidth}{0pt}
editor: visual
---

```{r yaml notes, include=FALSE}
#change format: html (for render in Viewer) 
#to the following for the word doc. version report
#format: 
#  docx:
#    reference-doc: /Users/linlizhou/Documents/Rprojects/IR-Projects/lasell.report.template.docx
#    prefer-html: true

```

```{r load.stucrs_1822allcrs, include=FALSE}
#load all necessary packages and themes, global optin chunk
source("/Users/linlizhou/Documents/Rprojects/IR-Projects/theme_source.R")

#the following df are created from "/Users/linlizhou/Documents/Rprojects/IR-Projects/theme_source.R" 

#grades of core courses: contains "Major", "GPA"/C("grade") for each "coursegroup" and "coursecode" by "term"(18fall-22spring)
stucrs_1822allcrs<-read_xlsx("/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Data and Analyses/Program Review/2022 Core Curriculum/data files/StudentInfoCourse_1822allcrs.xlsx")

#mutate term
stucrs_1822allcrs<-stucrs_1822allcrs%>%
  mutate(term=paste(academic_year,academic_term,sep=" "),
         term=factor(term,levels = c("2018 FALL","2019 SPRING","2019 FALL","2020 SPRING","2020 FALL","2021 SPRING","2021 FALL","2022 SPRING")))

#recode term
stucrs_1822allcrs$term<-
  recode(stucrs_1822allcrs$term,
         "2018 FALL"="2018 Fall","2019 SPRING"="2019 Spring",
         "2019 FALL"="2019 Fall","2020 SPRING"="2020 Spring",
         "2020 FALL"="2020 Fall","2021 SPRING"="2021 Spring",
         "2021 FALL"="2021 Fall","2022 SPRING"="2022 Spring")

#check: stucrs_1822allcrs%>%count(term); stucrs_1822allcrs%>%count(coursecode); stucrs_1822allcrs%>%count(Major)%>%View()
```

```{r filter.stucrs.si}
#focus on course group "Scientific Inquiry & Problem Solving/Science and Inquiry Knowledge and Perspectives (SIKP)" 
stucrs.si<-stucrs_1822allcrs%>%
  filter(stucrs_1822allcrs$coursecode %in% 
        c("BIO101", "BIO102", "BIO107", "BIO113", 
          "CHEM105", "CHEM203", 
          "ENV206", "ENV211", "ENV220", 
          "MATH109", 
          "CJ205",
          "PHYS107","PHYS108","PHYS111", "PHYS112", 
          "SCI103", "SCI104", "SCI105", "SCI106", "SCI107", "SCI114", "SCI115", "SCI117", "SCI118", "SCI119"))%>%unique()
```

```{r mutate.coursegrp}
stucrs.si<-stucrs.si%>%mutate(coursegrp=case_when(
  grepl("^BIO",coursecode)~"BIO",
  grepl("^CHEM",coursecode)~"CHEM",
  grepl("^ENV",coursecode)~"ENV",
  grepl("^MATH",coursecode)~"MATH",
  grepl("^CJ",coursecode)~"CJ",
  grepl("^PHYS",coursecode)~"PHYS",
  grepl("^SCI",coursecode)~"SCI"))#check:%>%count(coursegrp,coursecode)%>%View()
```

# Students Enrolled in SIKP Courses by Term

```{r crscnt}
#how many observation appeared for each course in each term:  
tab.crscnt<-stucrs.si%>%count(term,coursecode)%>%
pivot_wider(names_from="term",values_from="n",values_fill =0)%>%
  select(coursecode,`2018 Fall`,`2019 Spring`,`2019 Fall`,`2020 Spring`,`2020 Fall`,`2021 Spring`,`2021 Fall`,`2022 Spring`)%>%arrange(coursecode)
#check: are these appeared observations valid (unique and not drop and have a valid grade) students
#stucrs.si%>%count(Add_Drop); stucrs.si%>%count(Final_Grade)# all add and valid grades
#stucrs.si%>%count(term,coursecode,people_code_id)%>%count()#unique

#format table as viz (format beautifully with kbl functions)
viz.crscnt<-tab.crscnt%>%
kbl(align = "c",booktabs = T,label="tab.label", caption = "SIKP Course Enrollment by Semester", col.names =c("",str_wrap(names(tab.crscnt)[2:ncol(tab.crscnt)],width = 3))) %>%
#set in-text reference label, table title , header names
kable_styling(latex_options = c('HOLD_position'), full_width = F, fixed_thead = T, font_size = 12,bootstrap_options = c("striped", "hover", "condensed", "responsive"))%>%
#set overall style
column_spec(1, bold = F, border_right = F, background = "white", width = "5em",color="black")

#conditional formatting
cutraw<-stucrs.si%>%count(term,coursecode)%>%select(n)
cut1<-(max(cutraw)-min(cutraw))*.6+min(cutraw)
cut2<-(max(cutraw)-min(cutraw))*.4+min(cutraw)
cut3<-(max(cutraw)-min(cutraw))*.2+min(cutraw)
cut4<-1

for (i in 2:ncol(tab.crscnt)){
viz.crscnt<-
column_spec(kable_input=viz.crscnt,column=i, width = "3em",color="white",
            background =cf_color_blue(tab.crscnt[i],a=cut1,b=cut2,c=cut3,d=cut4))
i=i+1; viz.crscnt}
```

```{r show.crscnt, fig.width=8,include=TRUE}
viz.crscnt
```

# Distributions of Majors by Course Group

Table @tbl-mjcnt summarizes distributions of students' major for each
SIKP course groups. The table uses aggregated data across academic year
2018-2022, and excludes majors with less than 2% percentage observations
or missing a major value.

```{r request notes}
#optional: GPA/grades changes by term; GAP/grades by major
```

```{r mjcnt}
#count major (with toal row&col) for each coursecode across 18-22
tab.mjcnt<-stucrs.si%>%group_by(coursegrp,Major)%>%summarise(n=n())%>%mutate(prt=n/sum(n))%>%
  select(-n)%>%filter(prt>.02 & !is.na(Major))%>%#only show a portion
  pivot_wider(names_from=coursegrp,values_from=prt,values_fill=0)%>%arrange(Major)#reorder

tab.mjcnt<-tab.mjcnt%>%  
  #other majors: 
  rbind(c(Major="Other Majors",1-colSums(tab.mjcnt[-1])))%>%#check:tail(2)
  mutate(across(names(tab.mjcnt)[-1], function(x) percent(x, digit=0)))#change prt to %

#format table as viz (format beautifully with kbl functions)
viz.mjcnt<-tab.mjcnt%>%
kbl(align = "c",booktabs = T, col.names =c("",str_wrap(names(tab.mjcnt)[2:ncol(tab.mjcnt)],width = 3))) %>%
#set in-text reference label, table title , header names
kable_styling(latex_options = c('HOLD_position'), full_width = F, fixed_thead = T, font_size = 12,bootstrap_options = c("striped", "hover", "condensed", "responsive"))%>%
#set overall style
column_spec(1, bold = F, border_right = F, background = "white", width = "20em",color="black")

#conditional formatting
cutraw<-tab.mjcnt%>%pivot_longer(cols=c(BIO:SCI),names_to="coursegrp",values_to="prt")%>%select(prt)
cut1<-(max(cutraw)-min(cutraw))*.6+min(cutraw)
cut2<-(max(cutraw)-min(cutraw))*.2+min(cutraw)
cut3<-0.075
cut4<-0

for (i in 2:ncol(tab.mjcnt)){
viz.mjcnt<-
column_spec(kable_input=viz.mjcnt,column=i, width = "3em",color="white",
            background =cf_color_blue(tab.mjcnt[i],a=cut1,b=cut2,c=cut3,d=cut4))
i=i+1; viz.mjcnt}

#correct the other major row
viz.mjcnt<-viz.mjcnt%>%row_spec(nrow(tab.mjcnt),color = color_grey,background = "white")
```

```{r show.mjcnt, fig.width=8,include=TRUE}
#| label: tbl-mjcnt
#| tbl-cap: "Distributions of Majors by Course Groups"
viz.mjcnt
```

```{r explainhiddenplots}
#Plots below summarize distributions of students' major for each SIKP course groups. Plots are created using aggregated data across academic year 2018-2022. All plots below excluded majors with less than 2% percentage and observations that has a missing major value.
```

```{r viz_bio.major}
viz_bio.major<-stucrs.si%>%filter(grepl("^BIO",coursecode))%>%#check: %>%count(coursecode)
  group_by(Major)%>%summarise(n=n())%>%mutate(prt=n/sum(n))%>%arrange(-prt)%>%#check:View()
  select(-n)%>%filter(prt>.02)%>%filter(!is.na(Major))%>%

ggplot(aes(y=reorder(Major,prt), x = prt)) +  #y=factor(itemvar/yvar, levels = setyorder$yorder, ordered = TRUE), 
  geom_bar(stat="identity",position = position_dodge(),width=0.9,fill=color_bluelight)+#position = position_stack(),width=0.9
    scale_x_continuous(labels = scales::percent)+
  geom_text(aes(label=if_else(prt>0.02,as.character(percent(prt,digits = 0)),"")),#do not show anything less than error terms, to avoid overlapping labels as well
                     size=3,vjust=0.5,hjust=0.7,fontface="bold",position = position_dodge(0.9))+
   labs(title="BIO Courses",x="",y="")+ theme_lz()+theme(axis.text.y = element_text())
```

```{r viz_chem.major}
viz_chem.major<-stucrs.si%>%filter(grepl("^CHEM",coursecode))%>%#check: %>%count(coursecode)
  group_by(Major)%>%summarise(n=n())%>%mutate(prt=n/sum(n))%>%arrange(-prt)%>%#check:View()
  select(-n)%>%filter(prt>.02)%>%filter(!is.na(Major))%>%

ggplot(aes(y=reorder(Major,prt), x = prt)) +  #y=factor(itemvar/yvar, levels = setyorder$yorder, ordered = TRUE), 
  geom_bar(stat="identity",position = position_dodge(),width=0.9,fill=color_bluelight)+#position = position_stack(),width=0.9
    scale_x_continuous(labels = scales::percent)+
  geom_text(aes(label=if_else(prt>0.02,as.character(percent(prt,digits = 0)),"")),#do not show anything less than error terms, to avoid overlapping labels as well
                     size=3,vjust=0.5,hjust=0.7,fontface="bold",position = position_dodge(0.9))+
   labs(title="CHEM Courses",x="",y="")+ theme_lz()+theme(axis.text.y = element_text())
```

```{r viz_env.major}
viz_env.major<-stucrs.si%>%filter(grepl("^ENV",coursecode))%>%#check: %>%count(coursecode)
  group_by(Major)%>%summarise(n=n())%>%mutate(prt=n/sum(n))%>%arrange(-prt)%>%#check:View()
  select(-n)%>%filter(prt>.02)%>%filter(!is.na(Major))%>%

ggplot(aes(y=reorder(Major,prt), x = prt)) +  #y=factor(itemvar/yvar, levels = setyorder$yorder, ordered = TRUE), 
  geom_bar(stat="identity",position = position_dodge(),width=0.9,fill=color_bluelight)+#position = position_stack(),width=0.9
    scale_x_continuous(labels = scales::percent)+
  geom_text(aes(label=if_else(prt>0.02,as.character(percent(prt,digits = 0)),"")),#do not show anything less than error terms, to avoid overlapping labels as well
                     size=3,vjust=0.5,hjust=0.7,fontface="bold",position = position_dodge(0.9))+
   labs(title="ENV Courses",x="",y="")+ theme_lz()+theme(axis.text.y = element_text())
```

```{r viz_phys.major}
viz_phys.major<-stucrs.si%>%filter(grepl("^PHYS",coursecode))%>%#check: %>%count(coursecode)
  group_by(Major)%>%summarise(n=n())%>%mutate(prt=n/sum(n))%>%arrange(-prt)%>%#check:View()
  select(-n)%>%filter(prt>.02)%>%filter(!is.na(Major))%>%

ggplot(aes(y=reorder(Major,prt), x = prt)) +  #y=factor(itemvar/yvar, levels = setyorder$yorder, ordered = TRUE), 
  geom_bar(stat="identity",position = position_dodge(),width=0.9,fill=color_bluelight)+#position = position_stack(),width=0.9
    scale_x_continuous(labels = scales::percent)+
  geom_text(aes(label=if_else(prt>0.02,as.character(percent(prt,digits = 0)),"")),#do not show anything less than error terms, to avoid overlapping labels as well
                     size=3,vjust=0.5,hjust=0.7,fontface="bold",position = position_dodge(0.9))+
   labs(title="PHYS Courses",x="",y="")+ theme_lz()+theme(axis.text.y = element_text())
```

```{r viz_sci.major}
viz_sci.major<-stucrs.si%>%filter(grepl("^SCI",coursecode))%>%#check: %>%count(coursecode)
  group_by(Major)%>%summarise(n=n())%>%mutate(prt=n/sum(n))%>%arrange(-prt)%>%#check:View()
  select(-n)%>%filter(prt>.02)%>%filter(!is.na(Major))%>%

ggplot(aes(y=reorder(Major,prt), x = prt)) +  #y=factor(itemvar/yvar, levels = setyorder$yorder, ordered = TRUE), 
  geom_bar(stat="identity",position = position_dodge(),width=0.9,fill=color_bluelight)+#position = position_stack(),width=0.9
    scale_x_continuous(labels = scales::percent)+
  geom_text(aes(label=if_else(prt>0.02,as.character(percent(prt,digits = 0)),"")),#do not show anything less than error terms, to avoid overlapping labels as well
                     size=3,vjust=0.5,hjust=0.7,fontface="bold",position = position_dodge(0.9))+
   labs(title="SCI Courses",x="",y="")+ theme_lz()+theme(axis.text.y = element_text())
```

```{r viz_cj.major}
viz_cj.major<-stucrs.si%>%filter(grepl("^CJ",coursecode))%>%#check: %>%count(coursecode)
  group_by(Major)%>%summarise(n=n())%>%mutate(prt=n/sum(n))%>%arrange(-prt)%>%#check:View()
  select(-n)%>%filter(prt>.02)%>%filter(!is.na(Major))%>%

ggplot(aes(y=reorder(Major,prt), x = prt)) +  #y=factor(itemvar/yvar, levels = setyorder$yorder, ordered = TRUE), 
  geom_bar(stat="identity",position = position_dodge(),width=0.9,fill=color_bluelight)+#position = position_stack(),width=0.9
    scale_x_continuous(labels = scales::percent)+
  geom_text(aes(label=if_else(prt>0.02,as.character(percent(prt,digits = 0)),"")),#do not show anything less than error terms, to avoid overlapping labels as well
                     size=3,vjust=0.5,hjust=0.7,fontface="bold",position = position_dodge(0.9))+
   labs(title="CJ Courses",x="",y="")+ theme_lz()+theme(axis.text.y = element_text())
```

```{r longdisplay.viz_major,fig.height=6}
gridExtra::grid.arrange(viz_env.major,#19
                        viz_sci.major,#18
                        nrow=1, widths=c(1,1))
```

```{r middisplay.viz_major,fig.height=4}
gridExtra::grid.arrange(viz_bio.major,#12
                        viz_chem.major,#12
                        nrow=1, widths=c(1,1))
```

```{r shortdisplay.viz_major,fig.height=2.8}
gridExtra::grid.arrange(viz_cj.major,#3
                        viz_phys.major, #9
                        nrow=1, widths=c(1,1))
```

# Distributions of Majors by Individual Courses

## BIO

```{r biocnt}
#count major (with toal row&col) for each coursecode across 18-22
tab.biocnt<-stucrs.si%>%filter(grepl("^BIO",coursecode))%>%
  group_by(coursecode,Major)%>%
  summarise(n=n())%>%mutate(prt=n/sum(n))%>%select(-n)%>%
  filter(prt>.02 & !is.na(Major))%>%
  pivot_wider(names_from=coursecode,values_from=prt,values_fill=0)%>%arrange(Major)

tab.biocnt<-tab.biocnt%>%rbind(c(Major="Other Majors",1-colSums(tab.biocnt[-1])))%>%
  #check:tail(2) add "others" row
  mutate(across(names(tab.biocnt)[-1], function(x) percent(x, digit=0)))  #make numbers percentage

#format table as viz (format beautifully with kbl functions)
viz.biocnt<-tab.biocnt%>%
kbl(align = "c",booktabs = T, col.names =c("",str_wrap(names(tab.biocnt)[2:ncol(tab.biocnt)],width = 3))) %>%
#set in-text reference label, table title , header names
kable_styling(latex_options = c('HOLD_position'), full_width = F, fixed_thead = T, font_size = 12,bootstrap_options = c("striped", "hover", "condensed", "responsive"))%>%
#set overall style
column_spec(1, bold = F, border_right = F, background = "white", width = "20em",color="black")

#conditional formatting

for (i in 2:ncol(tab.biocnt)){
viz.biocnt<-
column_spec(kable_input=viz.biocnt,column=i, width = "4em",color="white",
            background =cf_color_blue(tab.biocnt[i],a=.2,b=.1,c=.075,d=0))
i=i+1; viz.biocnt}

#correct the other major row
viz.biocnt<-viz.biocnt%>%row_spec(nrow(tab.biocnt),color = color_grey,background = "white")
```

```{r show.biocnt, fig.width=8,include=TRUE}
#| label: tbl-biocnt
#| tbl-cap: "Distributions of Majors for BIO Courses"
viz.biocnt
```

## CHEM

```{r chemcnt}
#count major (with toal row&col) for each coursecode across 18-22
tab.chemcnt<-stucrs.si%>%filter(grepl("^CHEM",coursecode))%>%
  group_by(coursecode,Major)%>%
  summarise(n=n())%>%mutate(prt=n/sum(n))%>%select(-n)%>%
  filter(prt>.02 & !is.na(Major))%>%
  pivot_wider(names_from=coursecode,values_from=prt,values_fill=0)%>%arrange(Major)

tab.chemcnt<-tab.chemcnt%>%rbind(c(Major="Other Majors",1-colSums(tab.chemcnt[-1])))%>%
  #check:tail(2) add "others" row
  mutate(across(names(tab.chemcnt)[-1], function(x) percent(x, digit=0)))  #make numbers percentage

#format table as viz (format beautifully with kbl functions)
viz.chemcnt<-tab.chemcnt%>%
kbl(align = "c",booktabs = T, col.names =c("",str_wrap(names(tab.chemcnt)[2:ncol(tab.chemcnt)],width = 3))) %>%
#set in-text reference label, table title , header names
kable_styling(latex_options = c('HOLD_position'), full_width = F, fixed_thead = T, font_size = 12,bootstrap_options = c("striped", "hover", "condensed", "responsive"))%>%
#set overall style
column_spec(1, bold = F, border_right = F, background = "white", width = "20em",color="black")

#conditional formatting

for (i in 2:ncol(tab.chemcnt)){
viz.chemcnt<-
column_spec(kable_input=viz.chemcnt,column=i, width = "4em",color="white",
            background =cf_color_blue(tab.chemcnt[i],a=.2,b=.1,c=.075,d=0))
i=i+1; viz.chemcnt}

#correct the other major row
viz.chemcnt<-viz.chemcnt%>%row_spec(nrow(tab.chemcnt),color = color_grey,background = "white")
```

```{r show.chemcnt, fig.width=8,include=TRUE}
#| label: tbl-chemcnt
#| tbl-cap: "Distributions of Majors for CHEM Courses"
viz.chemcnt
```

## ENV

```{r envcnt}
#count major (with toal row&col) for each coursecode across 18-22
tab.envcnt<-stucrs.si%>%filter(grepl("^ENV",coursecode))%>%
  group_by(coursecode,Major)%>%
  summarise(n=n())%>%mutate(prt=n/sum(n))%>%select(-n)%>%
  filter(prt>.02 & !is.na(Major))%>%
  pivot_wider(names_from=coursecode,values_from=prt,values_fill=0)%>%arrange(Major)

tab.envcnt<-tab.envcnt%>%rbind(c(Major="Other Majors",1-colSums(tab.envcnt[-1])))%>%
  #check:tail(2) add "others" row
  mutate(across(names(tab.envcnt)[-1], function(x) percent(x, digit=0)))  #make numbers percentage

#format table as viz (format beautifully with kbl functions)
viz.envcnt<-tab.envcnt%>%
kbl(align = "c",booktabs = T, col.names =c("",str_wrap(names(tab.envcnt)[2:ncol(tab.envcnt)],width = 3))) %>%
#set in-text reference label, table title , header names
kable_styling(latex_options = c('HOLD_position'), full_width = F, fixed_thead = T, font_size = 12,bootstrap_options = c("striped", "hover", "condensed", "responsive"))%>%
#set overall style
column_spec(1, bold = F, border_right = F, background = "white", width = "20em",color="black")

#conditional formatting

for (i in 2:ncol(tab.envcnt)){
viz.envcnt<-
column_spec(kable_input=viz.envcnt,column=i, width = "4em",color="white",
            background =cf_color_blue(tab.envcnt[i],a=.2,b=.1,c=.075,d=0))
i=i+1; viz.envcnt}

#correct the other major row
viz.envcnt<-viz.envcnt%>%row_spec(nrow(tab.envcnt),color = color_grey,background = "white")
```

```{r show.envcnt, fig.width=8,include=TRUE}
#| label: tbl-envcnt
#| tbl-cap: "Distributions of Majors for ENV Courses"
viz.envcnt
```

## PHYS

```{r physcnt}
#count major (with toal row&col) for each coursecode across 18-22
tab.physcnt<-stucrs.si%>%filter(grepl("^PHYS",coursecode))%>%
  group_by(coursecode,Major)%>%
  summarise(n=n())%>%mutate(prt=n/sum(n))%>%select(-n)%>%
  filter(prt>.02 & !is.na(Major))%>%
  pivot_wider(names_from=coursecode,values_from=prt,values_fill=0)%>%arrange(Major)

tab.physcnt<-tab.physcnt%>%rbind(c(Major="Other Majors",1-colSums(tab.physcnt[-1])))%>%
  #check:tail(2) add "others" row
  mutate(across(names(tab.physcnt)[-1], function(x) percent(x, digit=0)))  #make numbers percentage

#format table as viz (format beautifully with kbl functions)
viz.physcnt<-tab.physcnt%>%
kbl(align = "c",booktabs = T, col.names =c("",str_wrap(names(tab.physcnt)[2:ncol(tab.physcnt)],width = 3))) %>%
#set in-text reference label, table title , header names
kable_styling(latex_options = c('HOLD_position'), full_width = F, fixed_thead = T, font_size = 12,bootstrap_options = c("striped", "hover", "condensed", "responsive"))%>%
#set overall style
column_spec(1, bold = F, border_right = F, background = "white", width = "20em",color="black")

#conditional formatting

for (i in 2:ncol(tab.physcnt)){
viz.physcnt<-
column_spec(kable_input=viz.physcnt,column=i, width = "4.5em",color="white",
            background =cf_color_blue(tab.physcnt[i],a=.2,b=.1,c=.075,d=0))
i=i+1; viz.physcnt}

#correct the other major row
viz.physcnt<-viz.physcnt%>%row_spec(nrow(tab.physcnt),color = color_grey,background = "white")
```

```{r show.physcnt, fig.width=8,include=TRUE}
#| label: tbl-physcnt
#| tbl-cap: "Distributions of Majors for PHYS Courses"
viz.physcnt
```

## SCI

```{r scicnt10}
#count major (with toal row&col) for each coursecode across 18-22
tab.scicnt10<-stucrs.si%>%filter(grepl("^SCI10",coursecode))%>%
  group_by(coursecode,Major)%>%
  summarise(n=n())%>%mutate(prt=n/sum(n))%>%select(-n)%>%
  filter(prt>.02 & !is.na(Major))%>%
  pivot_wider(names_from=coursecode,values_from=prt,values_fill=0)%>%arrange(Major)

tab.scicnt10<-tab.scicnt10%>%rbind(c(Major="Other Majors",1-colSums(tab.scicnt10[-1])))%>%
  #check:tail(2) add "others" row
  mutate(across(names(tab.scicnt10)[-1], function(x) percent(x, digit=0)))  #make numbers percentage

#format table as viz (format beautifully with kbl functions)
viz.scicnt10<-tab.scicnt10%>%
kbl(align = "c",booktabs = T, col.names =c("",str_wrap(names(tab.scicnt10)[2:ncol(tab.scicnt10)],width = 3))) %>%
#set in-text reference label, table title , header names
kable_styling(latex_options = c('HOLD_position'), full_width = F, fixed_thead = T, font_size = 12,bootstrap_options = c("striped", "hover", "condensed", "responsive"))%>%
#set overall style
column_spec(1, bold = F, border_right = F, background = "white", width = "20em",color="black")

#conditional formatting

for (i in 2:ncol(tab.scicnt10)){
viz.scicnt10<-
column_spec(kable_input=viz.scicnt10,column=i, width = "3em",color="white",
            background =cf_color_blue(tab.scicnt10[i],a=.2,b=.1,c=.075,d=0))
i=i+1; viz.scicnt10}

#correct the other major row
viz.scicnt10<-viz.scicnt10%>%row_spec(nrow(tab.scicnt10),color = color_grey,background = "white")
```

```{r show.scicnt10, fig.width=8,include=TRUE}
#| label: tbl-scicnt10
#| tbl-cap: "Distributions of Majors for SCI103-106 Courses"
viz.scicnt10
```

```{r scicnt11}
#count major (with toal row&col) for each coursecode across 18-22
tab.scicnt11<-stucrs.si%>%filter(grepl("^SCI11",coursecode))%>%
  group_by(coursecode,Major)%>%
  summarise(n=n())%>%mutate(prt=n/sum(n))%>%select(-n)%>%
  filter(prt>.02 & !is.na(Major))%>%
  pivot_wider(names_from=coursecode,values_from=prt,values_fill=0)%>%arrange(Major)

tab.scicnt11<-tab.scicnt11%>%rbind(c(Major="Other Majors",1-colSums(tab.scicnt11[-1])))%>%
  #check:tail(2) add "others" row
  mutate(across(names(tab.scicnt11)[-1], function(x) percent(x, digit=0)))  #make numbers percentage

#format table as viz (format beautifully with kbl functions)
viz.scicnt11<-tab.scicnt11%>%
kbl(align = "c",booktabs = T, col.names =c("",str_wrap(names(tab.scicnt11)[2:ncol(tab.scicnt11)],width = 3))) %>%
#set in-text reference label, table title , header names
kable_styling(latex_options = c('HOLD_position'), full_width = F, fixed_thead = T, font_size = 12,bootstrap_options = c("striped", "hover", "condensed", "responsive"))%>%
#set overall style
column_spec(1, bold = F, border_right = F, background = "white", width = "20em",color="black")

#conditional formatting

for (i in 2:ncol(tab.scicnt11)){
viz.scicnt11<-
column_spec(kable_input=viz.scicnt11,column=i, width = "4em",color="white",
            background =cf_color_blue(tab.scicnt11[i],a=.2,b=.1,c=.075,d=0))
i=i+1; viz.scicnt11}

#correct the other major row
viz.scicnt11<-viz.scicnt11%>%row_spec(nrow(tab.scicnt11),color = color_grey,background = "white")
```

```{r show.scicnt11, fig.width=8,include=TRUE}
#| label: tbl-scicnt11
#| tbl-cap: "Distributions of Majors for SCI114, 115, 118 Courses"
viz.scicnt11
```

## CJ

```{r cjcnt}
#count major (with toal row&col) for each coursecode across 18-22
tab.cjcnt<-stucrs.si%>%filter(grepl("^CJ",coursecode))%>%
  group_by(coursecode,Major)%>%
  summarise(n=n())%>%mutate(prt=n/sum(n))%>%select(-n)%>%
  filter(prt>.02 & !is.na(Major))%>%
  pivot_wider(names_from=coursecode,values_from=prt,values_fill=0)%>%arrange(Major)

tab.cjcnt<-tab.cjcnt%>%rbind(c(Major="Other Majors",1-colSums(tab.cjcnt[-1])))%>%
  #check:tail(2) add "others" row
  mutate(across(names(tab.cjcnt)[-1], function(x) percent(x, digit=0)))  #make numbers percentage

#format table as viz (format beautifully with kbl functions)
viz.cjcnt<-tab.cjcnt%>%
kbl(align = "c",booktabs = T, col.names =c("",str_wrap(names(tab.cjcnt)[2:ncol(tab.cjcnt)],width = 3))) %>%
#set in-text reference label, table title , header names
kable_styling(latex_options = c('HOLD_position'), full_width = F, fixed_thead = T, font_size = 12,bootstrap_options = c("striped", "hover", "condensed", "responsive"))%>%
#set overall style
column_spec(1, bold = F, border_right = F, background = "white", width = "20em",color="black")

#conditional formatting

for (i in 2:ncol(tab.cjcnt)){
viz.cjcnt<-
column_spec(kable_input=viz.cjcnt,column=i, width = "4em",color="white",
            background =cf_color_blue(tab.cjcnt[i],a=.2,b=.1,c=.075,d=0))
i=i+1; viz.cjcnt}

#correct the other major row
viz.cjcnt<-viz.cjcnt%>%row_spec(nrow(tab.cjcnt),color = color_grey,background = "white")
```

```{r show.cjcnt, fig.width=8,include=TRUE}
#| label: tbl-cjcnt
#| tbl-cap: "Distributions of Majors for CJ Courses"
viz.cjcnt
```
