---
title: "The Baseline Action and Momentum (BAM) Program  \nSurvey Results \\vspace{-3cm}"
format: 
  pdf:
    documentclass: article
    classoption: []
    fig-width: 8
    geometry:
      - top=25mm
      - bottom=20mm
      - left=15mm
      - right=15mm
      - textwidth=4.5in
    keep-md: true
    include-in-header:
      - text: |
          \usepackage{titling}
          \setlength{\droptitle}{-1.5in}
          \pretitle{\begin{center}
          \includegraphics[height=1in]{/Users/linlizhou/Documents/Rprojects/IR.png}\LARGE\\}
      - text: |
          \usepackage{fancyhdr}
          \addtolength{\headheight}{0.7cm}
    
          \pagestyle{fancy} 
          \fancyhead{}
          \fancyfoot{}
    
          \fancyhead[LO]{\includegraphics[height=1.3cm]{/Users/linlizhou/Documents/Rprojects/IR.png}}
          \fancyhead[RE]{\vspace{4mm}\textbf{AAC Courses Review}}
          \fancyfoot[C]{\thepage}
    
          \renewcommand{\headrulewidth}{0pt}
editor: visual
---

```{r libraries, include = FALSE}
source("/Users/linlizhou/Documents/Rprojects/IR-Projects/theme_source.R")
#change 
#format: 
#  pdf:
#to
#format:
#  docx:
#    reference-doc: /Users/linlizhou/Documents/Rprojects/IR-Projects/lasell.report.template.docx
#    prefer-html: true
```

```{r load_raw.surveyexport}
raw<-read_csv("/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Surveys/Lasell Internal/BAM Impact Survey/rawSurveyExport20221212.csv")
glimpse(raw)
```

```{r bam.remove_cols}
#remove unnecessary starter cols
bam<-raw%>%select(-(`Response ID`:`Date Submitted`),-(`Contact ID`:Source),-(`Invite Custom Field 1`:`Invite Custom Field 10`))%>%#remove unnecessary starter cols
  janitor::remove_empty(c("rows", "cols"))#remove empty rows/cols (including header has to be NA)

#remove NA cols
bam<-bam[ , colSums(is.na(bam)) < nrow(bam)] #sum each col's # of NA rows, not all rows are NA

#61 rows/observations
```

```{r bam.clean_names}
#look at the survey instruction: lapply(bam, unique)
# convinient col names:
bam<-janitor::clean_names(bam)
```

```{r bam_rename}
#rename cols: refer back to survey questions pdf

#same question rename to same start_texts
bam<-bam%>%rename(
#question 1
 acknowledge=i_have_read_the_information_on_the_previous_page_and_freely_consent_to_participate_in_this_research_i_understand_that_i_will_be_participating_in_a_study_on_the_impact_of_the_baseline_action_and_momentum_bam_programs_i_understand_that_my_participation_in_this_study_is_voluntary_and_i_may_withdraw_at_any_time_if_i_withdraw_from_the_study_then_all_measurements_and_questionnaire_data_from_me_will_be_destroyed_i_understand_that_every_effort_will_be_made_to_maintain_the_confidentiality_of_the_data_now_and_in_the_future,
 
#question 2
  act21_podseewhite=podcast_discussion_seeing_white_which_of_the_following_activities_did_you_engage_in_during_the_fall_2021_semester_select_all_that_apply,
  
  act21_bkhappen=book_discussion_what_happened_to_you_which_of_the_following_activities_did_you_engage_in_during_the_fall_2021_semester_select_all_that_apply,
  
  act21_docstuexp=video_documentary_the_student_experience_shown_at_fall_symposium_which_of_the_following_activities_did_you_engage_in_during_the_fall_2021_semester_select_all_that_apply,
  
  act21_ambassador=the_dei_ambassador_program_which_of_the_following_activities_did_you_engage_in_during_the_fall_2021_semester_select_all_that_apply,

act21_otheroption=other_write_in_which_of_the_following_activities_did_you_engage_in_during_the_fall_2021_semester_select_all_that_apply_58,

act21_otherwrite=other_write_in_which_of_the_following_activities_did_you_engage_in_during_the_fall_2021_semester_select_all_that_apply_59,
  
#question 3
act22_podracist=podcast_discussion_be_antiracist_which_of_the_following_activities_did_you_engage_in_during_the_spring_2022_semester_select_all_that_apply,
  
act22_bkinequity=book_discussion_despite_the_best_intentions_how_racial_inequity_thrives_in_good_schools_which_of_the_following_activities_did_you_engage_in_during_the_spring_2022_semester_select_all_that_apply,

act22_convadopt=bam_community_conversations_speaker_series_transracial_adoption_which_of_the_following_activities_did_you_engage_in_during_the_spring_2022_semester_select_all_that_apply,

act22_convlgbtq=bam_community_conversations_speaker_series_lgbtq_colleagues_which_of_the_following_activities_did_you_engage_in_during_the_spring_2022_semester_select_all_that_apply,

act22_convfirstgen=bam_community_conversations_speaker_series_first_gen_colleagues_which_of_the_following_activities_did_you_engage_in_during_the_spring_2022_semester_select_all_that_apply,

act22_disable=the_student_experience_students_with_disabilities_which_of_the_following_activities_did_you_engage_in_during_the_spring_2022_semester_select_all_that_apply,

act22_incluteach=accessible_connected_equitable_ace_learning_community_on_inclusive_teaching_which_of_the_following_activities_did_you_engage_in_during_the_spring_2022_semester_select_all_that_apply,

act22_ambassador=the_dei_ambassador_program_which_of_the_following_activities_did_you_engage_in_during_the_spring_2022_semester_select_all_that_apply,

act22_otheroption=other_write_in_which_of_the_following_activities_did_you_engage_in_during_the_spring_2022_semester_select_all_that_apply_68,

act22_otherwrite=other_write_in_which_of_the_following_activities_did_you_engage_in_during_the_spring_2022_semester_select_all_that_apply_69,

#question 4
act_time=how_much_time_approximately_did_you_spend_in_your_participation_in_all_bam_activities_over_the_course_of_the_academic_year,

#question 5
impv_yes=the_time_ive_spent_has_been_beneficial_please_agree_disagree_with_the_following_statements_after_participating_in_bam_learning_activities,

impv_recinequity=i_feel_more_able_to_recognize_issues_of_inequity_affecting_members_of_the_lasell_community_please_agree_disagree_with_the_following_statements_after_participating_in_bam_learning_activities,

impv_job=i_feel_better_equipped_to_do_my_job_teaching_advising_publicity_institutional_storytelling_systems_building_service_to_clients_customers_students_staff_etc_please_agree_disagree_with_the_following_statements_after_participating_in_bam_learning_activities,

impv_engagecolleague=i_feel_better_equipped_to_engage_with_colleagues_from_minoritized_backgrounds_please_agree_disagree_with_the_following_statements_after_participating_in_bam_learning_activities,

impv_engagestu=i_feel_better_equipped_to_engage_with_students_from_minoritized_backgrounds_please_agree_disagree_with_the_following_statements_after_participating_in_bam_learning_activities,

impv_talkinequity=i_feel_more_comfortable_participating_in_conversations_about_inequity_please_agree_disagree_with_the_following_statements_after_participating_in_bam_learning_activities,

impv_change=i_believe_i_can_impact_change_on_campus_please_agree_disagree_with_the_following_statements_after_participating_in_bam_learning_activities,

#question 6
impv_minority=improve_the_lasell_experience_for_students_faculty_and_staff_with_minoritized_identities_i_e_black_indigenous_people_of_color_lgbtqi_disability_status_first_generation_college_student_please_agree_disagree_with_the_following_statements_i_believe_broad_participation_in_bam_learning_activities_will,

impv_allexp=improve_the_lasell_experience_for_everyone_please_agree_disagree_with_the_following_statements_i_believe_broad_participation_in_bam_learning_activities_will,

impv_deistory=generate_positive_institutional_storytelling_about_the_university_s_leadership_on_dei_please_agree_disagree_with_the_following_statements_i_believe_broad_participation_in_bam_learning_activities_will,

impv_lifelearn=generate_positive_institutional_storytelling_about_the_extension_of_life_long_learning_to_all_please_agree_disagree_with_the_following_statements_i_believe_broad_participation_in_bam_learning_activities_will,

impv_deiduty=generate_shared_personal_and_institutional_responsibility_for_continuous_dei_improvement_please_agree_disagree_with_the_following_statements_i_believe_broad_participation_in_bam_learning_activities_will,

impv_collab=initiate_new_collaborations_ideas_and_work_efficiencies_from_folks_talking_across_unit_please_agree_disagree_with_the_following_statements_i_believe_broad_participation_in_bam_learning_activities_will,

#question
act_future=how_likely_are_you_to_continue_participating_in_bam_programs_and_events_in_the_upcoming_academic_year,

#open ended
qual_impv=please_describe_any_benefits_or_new_approaches_you_have_adopted_as_a_direct_result_of_bam_programs_and_participation_this_academic_year,

qual_sug=please_share_any_additional_suggestions_for_or_concerns_regarding_bam_programming_we_want_to_improve_what_we_do,

#demographics
dem_gender=please_describe_your_gender_identity,
dem_race=please_describe_your_racial_identity,
dem_otherrace=please_describe_any_of_your_other_personal_identities,
dem_othergd=some_other_race_write_in_please_describe_your_racial_identity,

#sentiment vars
qual_impv.stm=sentiment_please_describe_any_benefits_or_new_approaches_you_have_adopted_as_a_direct_result_of_bam_programs_and_participation_this_academic_year,

qual_sug.stm=sentiment_please_share_any_additional_suggestions_for_or_concerns_regarding_bam_programming_we_want_to_improve_what_we_do,

dem_other.stm=sentiment_please_describe_any_of_your_other_personal_identities
)
```

```{r bam.long_group.cols}
bam.long<-bam%>%
  #group similar items together as one variable
  pivot_longer(cols=starts_with("act21"),names_to="act21",values_to="act21_value")%>%
  pivot_longer(cols=starts_with("act22"),names_to="act22",values_to="act22_value")%>%
  pivot_longer(cols=impv_yes:impv_change,names_to="impved",values_to="impved_value")%>%
  pivot_longer(cols=impv_minority:impv_collab,names_to="willimpv",values_to="willimpv_value")
```

```{r save_bam_commentout}
#wb<-createWorkbook()

#addWorksheet(wb,"bam")
#writeData(wb,sheet = "bam",x=bam)

#addWorksheet(wb,"bam.long")
#writeData(wb,"bam.long",x=bam.long)

#saveWorkbook(wb,"/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Surveys/Lasell Internal/BAM Impact Survey/bam_working.xlsx",overwrite = TRUE)

```

# Survey Respondents

```{r plot.status}
#check: lapply(bam, unique)
plot.status<-bam%>%group_by(status)%>%summarise(cnt=n())%>%mutate(prt=round(cnt/sum(cnt)*100,digits = 0))%>%
ggplot(aes(x=2, y = prt, fill=status)) + xlim(0.5, 2.5)+ 
  geom_bar(stat="identity") +coord_polar(theta="y",start=0)+ 
  #circled coord, pie centered on 2; show .5-2.5 of pie (0-.5 is the hole)
  scale_fill_manual(values = c("#69b3e7","grey"))+
  annotate("text",x = 0.5, y = 0.5, fontface="bold", label = str_wrap( "61 Responses", width=10))+
  annotate("text",x = 0.5, y = 0.75, hjust=2.5,fontface="bold", label = str_wrap( "52%", width=10))+
  annotate("text",x = 0.5, y = 0.75, hjust=-1.7,fontface="bold", label = str_wrap( "48%", width=10))+#0.5 is centered location+
  #annotate("text",x = 0, y = 0.5, fontface="bold", label = ifelse(status=="Complete",as.character(cnt),""))+#0.5 is centered location+
  #geom_text(aes(label=cnt), size=3,vjust=0,hjust=0,fontface="bold",position = position_nudge())+
    theme_lz()+labs(title="",x="",y="",fill="",subtitle = "")
```

```{r plot.gender}
plot.gender<-bam%>%#check:count(dem_gender)
  filter(!is.na(dem_gender),dem_gender!="Prefer not to say")%>%#check:count(dem_gender)
  group_by(dem_gender)%>%summarise(cnt=n())%>%mutate(prt=round(cnt/sum(cnt)*100,digits = 0))%>%
  
ggplot(aes(x=2, y = prt, fill=dem_gender)) + geom_bar(stat="identity") +
  xlim(0.5, 2.5)+ coord_polar(theta="y",start=0)+ #circled coord, pie centered on 2; show .5-2.5 of pie (0-.5 hole)
  scale_fill_manual(values = c(color_blue_lasell,"#69b3e7","grey"))+
  
  #geom_text(aes(label=paste0(prt,"%")), size=3,vjust=-2,hjust=3,fontface="bold",position = position_dodge(1))+
  annotate("text",x = 0.5, y = 0.5, fontface="bold", label = str_wrap( "Gender", width=10))+
  annotate("text",x = 2, y = 0.75,vjust=0,hjust=0, fontface="bold", label = str_wrap( "3%", width=10))+
  annotate("text",x = 0.5, y = 0.75,vjust=0,hjust=2.5, fontface="bold", label = str_wrap( "61%", width=10))+
  annotate("text",x = 0.5, y = 0.75,vjust=0,hjust=-1.7, fontface="bold", label = str_wrap( "35%", width=10))+
  #0.5 is centered location+
  #annotate("text",x = 0, y = 0.5, fontface="bold", label = ifelse(status=="Complete",as.character(cnt),""))+#0.5 is centered location+
  
  theme_lz()+
  labs(title="",x="",y="",fill="",subtitle = "")
```

```{r plot.race}
plot.race<-bam%>%#check:count(dem_race)
  filter(!is.na(dem_race),dem_race!="Some Other Race - Write In")%>%
  group_by(dem_race)%>%summarise(cnt=n())%>%mutate(prt=round(cnt/sum(cnt)*100,digits = 0))%>%
  
ggplot(aes(x=2, y = prt, fill=dem_race)) + geom_bar(stat="identity") +
  xlim(0.5, 2.5)+ coord_polar(theta="y",start=0)+ #circled coord, pie centered on 2; show .5-2.5 of pie (0-.5 hole)
  scale_fill_manual(values = c(color_blue_lasell,"grey","#69b3e7"),labels=c("Asian","Black","White"))+
  #geom_text(aes(label=paste0(prt,"%")), size=3,vjust=-2,hjust=3,fontface="bold",position = position_dodge(1))+
  annotate("text",x = 0.5, y = 0.5, fontface="bold", label = str_wrap( "Race", width=10))+
  annotate("text",x = 2, y = 0.75,vjust=0,hjust=0.4, fontface="bold", label = str_wrap( "3%", width=10))+
  annotate("text",x = 2, y = 0.75,vjust=0,hjust=1.5, fontface="bold", label = str_wrap( "3%", width=10))+
  annotate("text",x = 0.5, y = 0.75,vjust=0,hjust=-1.7, fontface="bold", label = str_wrap( "94%", width=10))+
  #0.5 is centered location+
  #annotate("text",x = 0, y = 0.5, fontface="bold", label = ifelse(status=="Complete",as.character(cnt),""))+#0.5 is centered location+
  theme_lz()+labs(title="",x="",y="",fill="",subtitle = "")
```

```{r report_responses, fig.height=3, include = TRUE}
gridExtra::grid.arrange(plot.status,plot.gender,plot.race, nrow=1, widths=c(1,1,1))
```

The BAM survey received **61 responses**. Sixty-one percent of
respondents are female, 35% of respondents are male, and 3% are
**non-binary**. The majority (94%) of respondents are white, and 3%
**Asian** and 3% **Black**.

# BAM Activities Engagement

```{r plot.act21}
plot.act21<-bam.long%>%count(act21,act21_value)%>%
  ungroup()%>%group_by(act21)%>%mutate(prt=n/sum(n))%>%
  filter(!is.na(act21_value),act21!="act21_otherwrite",act21!="act21_otheroption")%>%
  ungroup()%>%select(act21_value,prt)%>%#must ungroup before selecting successfully
  
  ggplot(aes(x = prt, y=reorder(act21_value,prt), fill=act21_value)) +  
  geom_bar(stat="identity",position = position_dodge(),width=0.9)+
  scale_fill_manual(values = c("grey","#69b3e7","grey","#69b3e7"))+

  scale_y_discrete(labels=c(str_wrap("Book: What Happened to You?",width = 17),
                            str_wrap("DEI Ambassador",width = 17),
                            str_wrap("Podcast: Seeing White",width = 17),
                            str_wrap("E-Documentary: The Student Experience",width = 17)))+  #scale_x_continuous(labels = scales::percent)+
  geom_text(aes(label=percent(prt,digits = 0)),size=3,vjust=0.5,hjust=0.7,fontface="bold",position = position_dodge(0.9))+
  #geom_text(aes(label=if_else(prt>.8, as.character(round(prt,2)),"")),hjust=1.5,size=3,fontface="bold",position = position_dodge(0.9))+geom_text(aes(label=if_else(prt<.8, as.character(round(prt,2)),"")),hjust=1.5,
    labs(title="Engagement in BAM Activities in Fall 2021",x="",y="",fill="")+theme_lz()+theme(axis.text.y = element_text(),legend.position = "bottom/top")
```

```{r confirm_bam_act21}
#random check if prt the same using origional bam data: hooray
bam%>%count(act21_podseewhite)%>%mutate(prt=n/sum(n))%>%select(-n)%>%
  filter(!is.na(act21_podseewhite))#same with pivot_longer
bam%>%count(act21_bkhappen)%>%mutate(prt=n/sum(n))%>%select(-n)%>%
  filter(!is.na(act21_bkhappen))#same with pivot_longer
```

```{r plot.act22}
plot.act22<-bam.long%>%#count(act22_value)
  count(act22,act22_value)%>%
  ungroup()%>%group_by(act22)%>%mutate(prt=n/sum(n))%>%
  filter(!is.na(act22_value),act22!="act22_otherwrite",act22!="act22_otheroption")%>%
  ungroup()%>%select(act22_value,prt)%>%#must ungroup before selecting successfully
  
  ggplot(aes(x = prt, y=reorder(act22_value,prt))) +  
  geom_bar(stat="identity",position = position_dodge(),width=0.9,fill="grey")+
  #scale_fill_manual(values = c("grey","#69b3e7","grey","#69b3e7"))+

  scale_y_discrete(labels=c("Book: Racial Inequity","Inclusive Teaching","Transracial Adoption","LGBTQ Colleagues","First Gen Colleagues","DEI Ambassador","Student with Disabilities","Podcast: Antiracist"))+  #scale_x_continuous(labels = scales::percent)+
  geom_text(aes(label=percent(prt,digits = 0)),size=3,vjust=0.5,hjust=0.7,fontface="bold",position = position_dodge(0.9))+
  #geom_text(aes(label=if_else(prt>.8, as.character(round(prt,2)),"")),hjust=1.5,size=3,fontface="bold",position = position_dodge(0.9))+geom_text(aes(label=if_else(prt<.8, as.character(round(prt,2)),"")),hjust=1.5,
    labs(title="Engagement in BAM Activities in Spring 2022",x="",y="")+theme_lz()+theme(axis.text.y = element_text(),legend.position = "bottom/top")
```

```{r report_act, include = TRUE}
gridExtra::grid.arrange(plot.act21,plot.act22, nrow=1, widths=c(1,1))
```

```{r qual_activity}
#ACTIVITY
#2session
#suggest discussion of diversity of socioeconomic class within white group
#teaching how to deal with people with different views
#models of inclusive class design and examples of teaching DEI topics in class

#1oppo
#variety of opportunities presented (books, podcast, speaker series, etc.)
```

Most of BAM activities received around **15%** of respondents'
participation. The E-documentary on student experiences and podcast on
seeing white in Fall 2021 received the most participation, with 20% of
respondents engaged in each. Engagement in BAM activities seemed to
decrease from Fall 2021 to Spring 2022. Several BAM sessions in Spring
2022 (Book on racial inequity, Inclusive teaching, and Transracial
adoption) received less than 10% of respondents' participation.

From respondents' comments, we found that participants liked the variety
of **topics and formats** of presentations. Meanwhile, respondents hoped
to see more topics covered in the BAM events. A respondent suggested to
expand the race-centered diversity discussion to also include
**socioeconomic classes**, such as how diversity also exist within the
White ethnic group. Another respondent proposed BAM events around how to
properly deal with people with **different views**. A respondent also
requested a BAM session focusing on **practical examples and models** of
teaching DEI topics in class.

# BAM Activities Benefits

```{r plot.impved}
plot.impved<-bam.long%>%#check: count(impved)
  mutate(impved_group=case_when(
    impved_value%in%c("Agree","Strongly Agree")~"Positive",
    impved_value%in%c("Disagree","Strongly disagree")~"Negative"))%>%
  filter(!is.na(impved_group))%>%#exclude NA b/c NA does not mean anything (e.g.no-utility) in this question

  count(impved,impved_group)%>%ungroup()%>%#ungroup so that it's not prt within subgroups
  group_by(impved)%>%mutate(prt=n/sum(n))%>%#cal prt based on group of impved
  filter(impved_group=="Positive")%>%#only report positive (b/c negative contains the same meaning)
  
  ggplot(aes(x = prt, y=reorder(impved,prt))) +  
  geom_bar(stat="identity",position = position_dodge(),width=0.9,fill="#69b3e7")+
  #scale_fill_manual(values = c("grey","#69b3e7","grey","#69b3e7"))+

  scale_y_discrete(labels=c("Impact change on campus",
                            "Engage with minoritized colleagues",
                            "Equipped to do my job",
                            "Talk about inequity",
                            "Engage with minoritized students",
                            "Recognize inequity",
                            "Time spent beneficial"))+  #scale_x_continuous(labels = scales::percent)+
  geom_text(aes(label=percent(prt,digits = 0)),size=3,vjust=0.5,hjust=0.7,fontface="bold",position = position_dodge(0.9))+
  #geom_text(aes(label=if_else(prt>.8, as.character(round(prt,2)),"")),hjust=1.5,size=3,fontface="bold",position = position_dodge(0.9))+geom_text(aes(label=if_else(prt<.8, as.character(round(prt,2)),"")),hjust=1.5,
    labs(title="After Participating BAM Activities",x="",y="",fill="")+theme_lz()+theme(axis.text.y = element_text(),legend.position = "bottom/top")
```

```{r plot.willimpv}
plot.willimpv<-bam.long%>%#check:count(willimpv_value)
  mutate(willimpv_group=case_when(
    willimpv_value%in%c("Agree","Strongly Agree")~"Positive",
    willimpv_value%in%c("Disagree","Strongly Disagree")~"Negative"))%>%#check: %>%count(willimpv_group)
  filter(!is.na(willimpv_group))%>%#exclude NA b/c NA does not mean anything (e.g.no-utility) in this question

  count(willimpv,willimpv_group)%>%ungroup()%>%#ungroup so that it's not prt within subgroups
  group_by(willimpv)%>%mutate(prt=n/sum(n))%>%#cal prt based on group of willimpv
  filter(willimpv_group=="Positive")%>%#only report positive (b/c negative contains the same meaning)
  
  ggplot(aes(x = prt, y=reorder(willimpv,prt))) +  
  geom_bar(stat="identity",position = position_dodge(),width=0.9,fill="#69b3e7")+
  #scale_fill_manual(values = c("grey","#69b3e7","grey","#69b3e7"))+

  scale_y_discrete(labels=c("Life-long Learning",
                            "Expereinces of everyone",
                            "Collaboration and conversation",
                            "DEI Storytelling",
                            "DEI Responsibility",
                            "Expereinces of minority"))+  #scale_x_continuous(labels = scales::percent)+
  geom_text(aes(label=percent(prt,digits = 0)),size=3,vjust=0.5,hjust=0.7,fontface="bold",position = position_dodge(0.9))+
  #geom_text(aes(label=if_else(prt>.8, as.character(round(prt,2)),"")),hjust=1.5,size=3,fontface="bold",position = position_dodge(0.9))+geom_text(aes(label=if_else(prt<.8, as.character(round(prt,2)),"")),hjust=1.5,
    labs(title="Perceptions of BAM Benefits",x="",y="",fill="")+theme_lz()+theme(axis.text.y = element_text(),legend.position = "bottom/top")
```

```{r report_impv, include = TRUE}
gridExtra::grid.arrange(plot.impved,plot.willimpv, nrow=1, widths=c(1,1))
```

Respondents overall believe attending BAM activities are **beneficial**.
97% of respondents believe BAM programming could improve experiences of
minority students and everyone, generate shared responsibility and
storytelling about DEI, as well as facilitate collaborations and
conversations across units. Over 90% of respondents felt they are better
able to recognize and talk about inequity, and engage with minority
students and collagues. 84% of respondents felt they can impact change
on campus. Only 86% of respondents believe BAM programming could extend
life-long learning.

```{r qualbenefits}
bam.qual<-bam%>%select(starts_with("qual_"))
lapply(bam.qual, unique)
#BENEFITS
#Listen and don't make assumptions; Read to avoid offensive; conscientious of my word choice when communicating with students; understand possibilities of different reactions to words (7)
#interact with students to learn from their experiences; understand how feeling can affect learning (3)

#reinforced the importance and understanding of DEI
#expanding ambassadors to support more marginalized students
```

In the qualitative comments, many participants further indicated their
growth in becoming more conscience of assumptions and **word choices**.
Respondents reflected that they are more capable of understanding
reactions to words and how **feeling** can influence one's cognitive
learning. A few participants also mentioned that they are more
comfortable discussing **DEI in the classroom** and are more willing to
learn from student experiences. A participant also appreciated that the
BAM program helped reinforce the importance and understanding of DEI in
their department and in general.

# Future Participation

```{r plot.acttime}
plot.acttime<-bam%>%#check: count(act_time)
  filter(!is.na(act_time),act_time!="uncertain",act_time!="100")%>%
  mutate(act_time=as.numeric(act_time))%>%#chekc:%>%count(act_time)
 # count(act_time)%>%mutate(prt=n/sum(n))%>%
ggplot(aes(y = act_time, x=factor(0))) + geom_boxplot(fill="#69b3e7") +
  #scale_y_continuous(limits = c(0,40), breaks=(seq(0, 40, 5)) )+
  geom_text(aes(label=ifelse(act_time%in%c(0,5,10,12,20,36),act_time,"")),size=3)+
  labs(title="",x="Participation Time  \n(Hours over academic year)",y="")+
  theme_lz()#+theme(axis.text.y = element_text())
```

```{r report_act_future}
plot.actfuture<-bam%>%filter(!is.na(act_future))%>%
  mutate(act_future=factor(act_future, levels=c("Very Unlikely","Likely","Very Likely")))%>%
  group_by(act_future)%>%summarise(cnt=n())%>%mutate(prt=round(cnt/sum(cnt)*100,digits = 0))%>%
ggplot(aes(x=2, y = prt, fill=act_future)) + geom_bar(stat="identity") +
  xlim(0.5, 2.5)+ coord_polar(theta="y",start=0)+ #circled coord, pie centered on 2; show .5-2.5 of pie (0-.5 hole)

  #geom_text(aes(label=paste0(prt,"%")), size=3,vjust=-2,hjust=3,fontface="bold",position = position_dodge(1))+
  annotate("text",x = 0.5, y = 0.5, fontface="bold", label = str_wrap( "Future Participation", width=10))+
  annotate("text",x = 0.5, y = 0.5,vjust=-8,hjust=1.5, fontface="bold", label = str_wrap( "10%", width=10))+
  annotate("text",x = 0.5, y = 0.75,vjust=0.4,hjust=3.5, fontface="bold", label = str_wrap( "37%", width=10))+
  annotate("text",x = 0.5, y = 0.75,vjust=0,hjust=-2.5, fontface="bold", label = str_wrap( "53%", width=10))+
  #0.5 is centered location+
  #annotate("text",x = 0, y = 0.5, fontface="bold", label = ifelse(status=="Complete",as.character(cnt),""))+#0.5 is centered location+
  scale_fill_manual(values = c("grey",color_blue_lasell,"#69b3e7"),
                    guide=guide_legend(reverse = TRUE))+
  theme_lz()+theme(legend.position = "bottom")+
  labs(title="",x="",y="",fill="",subtitle = "")
```

```{r report_participate, include = TRUE}
gridExtra::grid.arrange(plot.acttime,plot.actfuture, nrow=1, widths=c(1,1))
```

Most respondents spent **10 hours** or more (over the academic year) on
all the BAM events. The maximum time spent is 36 hours. There are
**90%** of respondents indicated they are likely or very likely to
participate in future BAM events.

```{r qual_participate}
#PARTICIPATION 
#1timing of events
#When events consistently happen at the same time, it's hard for those with recurring meetings to attend.
#We need flexibility and session that are complete on your own time along with those that are done in real time. I would be more likely to complete something in my \"free\" time in my office rather than going to a session in person.

#2communication
#communication from our BAM ambassador regarding available programming (2)
#having reminders about events and opportunities
#see the whole calendar in January so that I can think about it overall
#outreach and advertise in different gatherings (e.g. faculty meeting, welcome back gathering, etc.)
```

From comments, a respondent indicated inconvenience of scheduling each
BAM events at the same time. The respondent suggested that different BAM
events could happen at **different times** and days of the week, which
may increase the possibilities of more people to be able to attend. The
respondent also requested BAM events to have both in-person and **online
recorded** versions, so that people can complete BAM programs with more
flexibility. Additionally, a respondent recommended that a BAM **event
calendar** could be helpful for participants to plan overall.

To increase BAM events participation, a respondent suggested that BAM
events can be promoted more strategically, such as **advertising** BAM
events at different gatherings and meetings like the faculty meetings
and welcome back gathering. A few respondents also indicated that they
hope to receive **more reminders** of the BAM events, and **more
reach-out** from BAM ambassadors regarding DEI opportunities.

# Summary

-   Respondents appreciated the variety of **topics and formats** of BAM
    events. A few more BAM event **topics t**hat respondents requested
    include: multi-faceted diversity beyond race (i.e. socio-economic
    classes), dealing with different views, and teaching DEI topics.

-   Over 97% of respondents perceived BAM program as **beneficial.** The
    benefits are concentrated on improved inclusive communication
    skills, openness to learn from student experiences, and
    understanding of how students' feelings can affect learning.

-   Engagement of BAM activities in Fall 2021 and Spring 2022 range from
    5% to 20% from survey respondents. To **increase participation**,
    respondents suggested that BAM events could happen at varied time
    with online recordings available. The BAM program may have a event
    calendar, which can be promoted early in the semester at different
    meetings. Respondents also requested more reminders of BAM events
    and communications about other relevant opportunities.
