---
title: "CMarinExcercise"
author: "Linli Zhou"
date: "2022-08-29"
output: 
  html_document:
    keep_md: true
---

The dataset used for this project contains the number of students enrolling in their first English course at a university who enrolled in transfer-level or below transfer-level English by term and race/ethnicity. 

Context: Assembly Bill 705 (Title 5, ยง 55003 and 55522) requires all California Community Colleges to
design placement methods that maximize the probability that students will enter and complete
transfer-level coursework in English and math/quantitative reasoning within one year of their
first enrollment in the discipline. In the databset, the university's methods used to determine placement changed from a placement test in fall 2015 and 2016, to multiple measures in fall 2017 and 2018, to AB705 in fall 2019. 

Research Question: How did the change in placement methods impact placement into transfer-level English?


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, include = TRUE, warning=FALSE, message=FALSE, fig.align = "center") #display code along with its results
library(readxl)
library(tidyverse)
library(writexl)
library(openxlsx)
library(formattable)#for percent function
library(ggrepel)
```

```{r setup color, include=FALSE}
library(ggplot2)

mycolors<-c("#13294b","#5c88da","#69b3e7","#fcb53b","#6C6F70","#641F45")
scale_color_manual(values=mycolors)

theme_lz <- function(){ 
    font <- "Helvetica"   #assign font family up front
    theme_minimal() %+replace%    #replace elements already strips axis lines, 
    theme(
      panel.grid.major = element_blank(),    #strip major gridlines
      panel.grid.minor = element_blank(),    #strip minor gridlines
      plot.title = element_text(family = font, size = 9, face = 'bold',hjust = 0.5, vjust = 2),
      axis.title = element_text(family = font, size = 9), 
      axis.text = element_text(family = font, size = 9), 
      axis.text.x = element_text(family = font, size = 9, margin = margin(t=5,b=10)),
      axis.ticks = element_blank(),          #strip axis ticks
      
      legend.title = element_text(family = font, size=9),
      legend.text = element_text(family = font, size=7),
      legend.position="right",
      
      strip.text = element_text(family = font, size = 9, margin = margin(t=5,b=10)),#move up is + 1
      strip.background = element_blank()
    )}
```

```{r load data}
data<-read_excel("/Users/linlizhou/Documents/LASELL/CMarinExcercise.xlsx",sheet = "raw")
```

```{r long data}
#transform pivot table into one observation each row
data.l<-pivot_longer(data,cols = `Fall 2015 (placement test)`:`Fall 2019 (AB705)`,names_to = "Term.Method",values_to = "NumberPlacement")
```

```{r separate col}
#Year col
data.l<-data.l%>%mutate(Year=case_when(
  Term.Method=="Fall 2015 (placement test)"~"2015",
  Term.Method=="Fall 2016 (placement test)"~"2016",
  Term.Method=="Fall 2017 (Multiple measures)"~"2017",
  Term.Method=="Fall 2018 (Multiple measures)"~"2018",
  Term.Method=="Fall 2019 (AB705)"~"2019"
))

#method col
data.l<-data.l%>%mutate(Method=case_when(
  Term.Method=="Fall 2015 (placement test)"~"Placement test",
  Term.Method=="Fall 2016 (placement test)"~"Placement test",
  Term.Method=="Fall 2017 (Multiple measures)"~"Multiple measures",
  Term.Method=="Fall 2018 (Multiple measures)"~"Multiple measures",
  Term.Method=="Fall 2019 (AB705)"~"AB705"
))

#save raw and tidy sheets in the same excel workbook
write.xlsx(list("tidy"=data.l,"raw"=data), file="/Users/linlizhou/Documents/LASELL/CMarinExcercise.xlsx")
```

```{r order of methods}
data.l$Method=factor(data.l$Method, levels=c("Placement test","Multiple measures","AB705"),labels=c("Placement Test (2015/16)","Multiple Measures (2017/18)","AB705 (2019)")) #recode the levels  
```


```{r within method-group, include=TRUE}
aggregate(data.l$NumberPlacement,by=list(Method=data.l$Method,Level=data.l$Course),FUN="sum")%>%#aggragated table with all vars needed
  group_by(Method)%>%mutate(prt=x/sum(x)) %>% #group by whatever is going to be the larger groups (adds up to 100%)
ggplot(aes(x=Level,y=percent(prt,digit=0),fill=Method))+
   geom_bar(stat="identity",position=position_dodge(),width = 0.8)+
  geom_text_repel(aes(label=percent(prt,digits=0)),color="black",size=4,position = position_dodge(width = 1),vjust=.9)+# hjust = 1.5 positions them inside the end of the bars. An hjust of 0.5 and a vjust of 0.5 center the box on the reference point. hjust=0, the left edge;;; For vertical, less is up and more is down
  theme_lz()+
    scale_fill_manual(values = c(mycolors[3],mycolors[2],mycolors[1]), name="Placement Methods")+#change legend color, lable, and title
  scale_y_continuous(breaks = seq(0, 0.3, by = 0.1) ,labels = scales::percent)+#present y axis label as percentage
  #geom_text_repel(aes(label= ifelse(Grade2System==4,paste(round(100*prt, 0), "%", sep=""),"")),size=3)+
  labs(x = "English Course Level", y = "", title="Students in Different English Courses by Placement Methods")+
   theme(axis.text.y=element_blank())
```

Conclusion: Each time we change placement methods, there have been around 13% more students to
be placed into transfer level than below transfer English course. For example, the latest
placement methods (AB705) put 13% more students into transfer level English course
than its predecessors (Multiple Measures).



```{r within method-group by race, include=TRUE}
aggregate(data.l$NumberPlacement,by=list(Method=data.l$Method,Level=data.l$Course, Race=data.l$Race),FUN="sum")%>%#aggragated table with all vars needed
  group_by(Method)%>%mutate(prt=x/sum(x)) %>% #group by whatever is going to be the larger groups (adds up to 100%)
ggplot(aes(x=Level,y=percent(prt,digit=0),fill=Method))+
   geom_bar(stat="identity",position=position_dodge(),width = 0.8)+
  facet_wrap(~Race,ncol=2)+
  #geom_text_repel(aes(label=percent(prt,digits=0)),color="black",size=4,position = position_dodge(width = 1),vjust=.9)+# hjust = 1.5 positions them inside the end of the bars. An hjust of 0.5 and a vjust of 0.5 center the box on the reference point. hjust=0, the left edge;;; For vertical, less is up and more is down
  theme_lz()+
    scale_fill_manual(values = c(mycolors[3],mycolors[2],mycolors[1]), name="Placement Methods")+#change legend color, lable, and title
  scale_y_continuous(breaks = seq(0, 0.3, by = 0.1) ,labels = scales::percent)+#present y axis label as percentage
  #geom_text_repel(aes(label= ifelse(Grade2System==4,paste(round(100*prt, 0), "%", sep=""),"")),size=3)+
  labs(x = "English Course Level", y = "", title="Students in Different English Courses by Placement Methods for Different Racial Groups")+
  theme(panel.grid.major.y = element_line(colour = "grey95"))
```


Conclusion: One-year throughput increased among all race/ethnic groups, during MMAP and AB705,
particularly among Hispanic/Latinx students, though a large throughput gap between
White students and Hispanic/Latinx, Asian, and Black/African-American students
remained in fall 2019.

