---
title: "FacultyTenureTrends"
author: "Linli Zhou"
date: "`r Sys.Date()`"
output: 
  html_document:
    keep_md: true
runtime: shiny
---

```{r setup, include=FALSE}
library(readxl)
library(tidyverse)
library(ggrepel)
library(formattable)
library(kableExtra)
knitr::opts_chunk$set(echo = FALSE, include = TRUE, warning=FALSE, message=FALSE, fig.align = "center")
#theme
theme_lz.html <- function(){ 
theme_minimal() %+replace%    #replace elements already strips axis lines, 
  theme(
    panel.grid.major = element_blank(),    #no major gridlines
    panel.grid.minor = element_blank(),    #no minor gridlines
    plot.title = element_text(hjust = 0.5, vjust = 2),
    axis.ticks = element_blank(),          #strip axis ticks
    axis.text.y=element_blank(),
    legend.position="bottom",
    legend.direction = "horizontal",
    strip.background = element_blank()#facet background
  )}
#setwd
#setwd("/Users/linlizhou/Documents/Rprojects/IR-Projects/Data Reporting/")
#load data
data<-read_excel("Faculty Data for Analyst Candidates.xlsx")
```

# Research Questions

1. How has the proportion of tenure-line (TL) and non-tenure (NT) faculty **changed over time**?

2. How has the proportion of TL faculty in certain **rank, racial, or sex** groups changed over time?

3. How has the proportion of TL and NT faculty changed over time for different **departments**?

```{r clean, results='hide'}
#remove duplicated rows
data<-unique(data)#from 4003 to 3984 observations
#investigate duplicated ID/persons
unique(data$ID)%>%length()#1147 unique ID
data%>% group_by(ID) %>% summarise(cnt=n()) %>%arrange(-cnt) %>%filter(cnt>1) #815 duplicated IDs
#thus, need n_distinct ID in the following codes
```

# Trends


```{r unique TvsN across year}
data%>%group_by(Year, `Tenure Status`)%>%
summarise(cnt=n_distinct(ID))%>%mutate(prt=percent(cnt/sum(cnt),digits=0))%>%

ggplot(aes(color=factor(`Tenure Status`),x=factor(Year),y=prt,group=factor(`Tenure Status`)))+geom_line()+
geom_text(aes(label=prt))+

scale_y_continuous(breaks = seq(.4,.6,by=.05),labels = scales::percent)+
labs(title=str_wrap("Proportion of Faulcty in Different Tenure-line Status",50),x="",y="")+
scale_color_discrete(labels=c("Non-tenure","Tenure"),name="")+theme_lz.html()+
theme(axis.text.y=element_blank())
```

* Tenure-line (TL) proportion increased 4% from 2016 to 44% in 2021, with 2020 being the highest 45%. 


# Trends Breakdown: Faculty Rank

```{r tenured trend by rank}
#pivot table
data%>% filter(Rank=="Professor"|Rank=="Assistant Professor"| Rank=="Associate Professor")%>%
  group_by(Year, Rank,`Tenure Status`)%>%#2016 professor as a group -> proportions of (non) tenure for all professors in 2016
summarise(cnt=n_distinct(ID))%>%mutate(prt=percent(cnt/sum(cnt),digits=0))%>%filter(`Tenure Status`=="Tenure Line")%>%
  
#plot
ggplot(aes(color=factor(Rank),linetype=factor(Rank),x=factor(Year),y=prt,group=factor(Rank)))+geom_line()+
geom_text_repel(aes(label=prt))+theme_lz.html()+
  
#themes
scale_y_continuous(breaks = seq(.55,.75,by=.1),labels = scales::percent)+
scale_color_discrete(name="")+
scale_linetype_discrete(name="")+
 
theme(axis.text.y=element_blank())+
labs(title="Tenure-line Faculty of Different Ranks",x="",y="")
```

* Although Assistant Professor and Professor experienced a 6% and 3% drop in TL proportion in 2017 and 2018 respectively, their TL proportion has increased to 73% and 75% respectively in 2021.  
* Associate professor, though slightly increased 1-2% in 2016-2019, dropped from 66% in 2019 to 60% in 2021.




# Trends Breakdown: Race

```{r facet two race bulk group}
#race count
nrace<-data%>% filter( !(`Race/Ethnicity`%in% c("Unreported", "Two or More Races",NA)))%>%filter(`Tenure Status`=="Tenure Line")%>%
  group_by(`Race/Ethnicity`)%>%count()%>%arrange(-n)%>%mutate(race=factor(`Race/Ethnicity`))

#create two bulk group and pivot table
racepvt<-data%>%filter( !(`Race/Ethnicity`%in% c("Unreported", "Two or More Races",NA)))%>%mutate(RaceGroup=case_when(
  `Race/Ethnicity` %in% nrace$`Race/Ethnicity`[1:2] ~ "Larger Racial Group",
  `Race/Ethnicity` %in% nrace$`Race/Ethnicity`[3:5] ~ "Smaller Racial Group",))%>%
#pivot table  
  group_by(Year, `Race/Ethnicity`,RaceGroup,`Tenure Status`)%>%#2016 male as a group -> proportions of (non) tenure for all male professors in 2016
summarise(cnt=n_distinct(ID))%>%mutate(prt=percent(cnt/sum(cnt),digits=0))%>%filter(`Tenure Status`=="Tenure Line")

#max/min data label
#max.min<-racepvt%>%select(`Race/Ethnicity`,prt)%>%group_by(`Race/Ethnicity`)%>%summarise(max=max(prt),min=min(prt))%>%arrange(min)
  
#plot
racepvt%>%ggplot(aes(x=factor(Year),y=prt,color=factor(`Race/Ethnicity`),linetype=factor(`Race/Ethnicity`),group=factor(`Race/Ethnicity`)))+geom_line()+theme_lz.html()+
  scale_color_manual(name="",limits=nrace$race, values = c("black","blue","chartreuse3","darkgoldenrod","brown1"),labels=c("White","Asian","International","Hispanic","Black"))+  
  scale_linetype_manual(name="",limits=nrace$race, values = c("solid","longdash","twodash","solid","longdash"),labels=c("White","Asian","International","Hispanic","Black"))+
  facet_wrap(~RaceGroup,labeller=labeller(RaceGroup= c(`Larger Racial Group`="Larger Racial Groups (Tenure-line Faculty>100)", `Smaller Racial Group`="Smaller Racial Groups (10<Tenure-line Faculty<100)") ) )+
  
geom_text_repel(aes(label=prt))+
#themes
scale_y_continuous(breaks = seq(.2,1,by=.2),labels = scales::percent)+
theme(axis.text.y=element_text())+theme(panel.grid.major.y = element_line(color = "grey95"), panel.grid.minor.y = element_line(color = "grey95"))+#theme(legend.position = "right", legend.direction = "vertical")+
  guides(color = guide_legend(nrow = 1, byrow = TRUE))+
labs(title=str_wrap("Tenure-line Faculty in Different Racial Groups",80),x="",y="")
```

* White faculty has a stable 42-48% TL proportion. 
* Asian faculty dropped from 40-42% in 2016-2017 to 32% in 2018. Though increased to 40% in 2019, dropped to 31% again in 2020. In the most recent year, Asian faculty's TL proportion reached the highest 51% in 2021.

* International, Hispanic, and Black faculty have 22-35% TL proportions in 2016-2017, 12-17% less than White and Asian faculty. However, their TL proportion increased since 2018 and reached 46-48% in 2021. 
+ International faculties have the lowest tenure-line proportion of 20% in 2016, but the proportion jumped to 50% in 2018 and 2021.
+ Hispanic faculties have increased tenure-line proportion from 33% in 2016 to 59% in 2020, and 55% in 2021, both are the highest among all racial groups in those two years. 
+ Black faculties' tenure-line proportion dropped from 50% in 2017 to 20% in 2018, but has been increasing by 7% each year to 44% in 2020 and kept stable at 45% in 2021.




# Trends Breakdown: Legal Sex & Race

```{r tenured trend by sex in different race}
#pivot table
data%>% filter(`Race/Ethnicity`!="Unreported")%>% group_by(Year,`Race/Ethnicity`, `Tenure Status`,`Legal Sex`)%>%#2016 male as a group -> proportions of (non) tenure for all male professors in 2016
summarise(cnt=n_distinct(ID))%>%mutate(prt=percent(cnt/sum(cnt),digits=0))%>%filter(`Tenure Status`=="Tenure Line")%>%
#plot
ggplot(aes(color=factor(`Legal Sex`),x=factor(Year),y=prt,group=factor(`Legal Sex`)))+geom_line()+facet_wrap(~`Race/Ethnicity`)+theme_lz.html()+
geom_text_repel(aes(label=prt),size=3)+
#themes
scale_y_continuous(breaks = seq(.2,.8,by=.2),labels = scales::percent)+
#scale_x_discrete(labels=c())
scale_color_discrete(name="")+
theme(axis.text.y=element_text())+theme(panel.grid.major.y = element_line(color = "grey95"))+
labs(title="Gender Gaps for Tenure-line Faculty",x="",y="")
```

* Hispanic and White faculty have a consistent gender gap during 2016-2021.
* White faculty has 50% and 60% gender difference in 2016 and 2019. The TL proportion difference decreased since 2019 and reached 20% in 2021. 
* Hispanic faculty gender gap has been consistently between 20-28%. 


# Departments with Significant Changes (2016~2021)

```{r dep prop.year table}
#n dep; filter out small dep that has skewed prt
n10dep<-data%>%group_by(Department)%>%summarise(cnt=n())%>% filter(cnt>10)%>%arrange(cnt)

#tenure prop by department
dep.Tprop<-data%>%filter(Department %in% n10dep$Department)%>%
  group_by(Year,Department, `Tenure Status`)%>%
  summarise(cnt=n_distinct(ID))%>%mutate(prt=percent(cnt/sum(cnt),digits = 0))%>%
  arrange(Department)%>%filter(`Tenure Status`=="Tenure Line")%>%
  select(-`Tenure Status`,-cnt)#have to remove cnt because only have the same value can be seen as one group; while cnt for different years vary, making departments not considered as the same

#year as cols
dep.wide<-dep.Tprop%>%pivot_wider(names_from = Year,values_from = prt)%>%mutate(Change=`2021`-`2016`,Average=mean(c(`2016`,`2017`,`2018`,`2019`,`2020`,`2021`)))%>%arrange(-Average)
```

```{r change_avg.dep}
#average and rank and change
average.dep<-dep.wide%>%select(Department,Average,Change)%>%arrange(-Average)%>% ungroup%>%mutate(`Rank of Average`=rank(-Average))#needs to ungroup before row_number or rank

#sig change>10%; list of departments
change.dep<-dep.wide%>%select(Department,`2016`,`2021`,Change)%>%
  filter(Change>0.1 | Change<(-0.1))%>%arrange(-Change) #have to use () for -0.1

change.avgrank<-merge(change.dep,average.dep)%>%select(Department,Change,Average)%>%arrange(-Change)
#condformat(change.dep) %>% rule_fill_gradient(Change, low=rgb(1,0,0),high=rgb(0,1,0))#low=rgb(1,0,0),high=rgb(0,1,0) good red-yellow/white-green

change.avgrank%>%formattable(list(
  Change=color_tile("red","yellow"),#from red to sth in between to yellow ultimately
  Average=color_bar("lightblue"),
  Change=formatter("span", style = ~ style(color = ifelse(Change >0, "darkgreen", "red")),
                    ~ icontext(ifelse(Change <0,"arrow-down", ifelse(Change>0.2,"thumbs-up","arrow-up")), Change))#,#the last change is to show values of change after styles
  #`Rank of Average`= formatter("span",style=x~style(color=ifelse(x<10,"darkgreen",ifelse(x>20,"red","grey"))))
))#%>%kable("html",caption = "Changes and Averages of Tenure-line Proportion for Departments")
```

* TL proportion of nine departments increased at least 13-40% during 2016-2021, with American Studies increased the most. 
* However, three departments (Econ, Phil, Chem) decreased 11-13% from 2016 to 2021. 



# Trends for Individual Departments (Interactive Dashboard)


```{r dep groups}
#order based on tenure prt -- exclude those without any tenure
dep.order.t<-data%>%group_by(Department,`Tenure Status`)%>%
  summarise(cnt=n_distinct(ID))%>%mutate(prt=percent(cnt/sum(cnt),digits = 0))%>%
  filter(`Tenure Status`=="Tenure Line")%>%arrange(prt)%>%
  mutate(dep.f=factor(Department))
#excluded in order
order.exclude<-data[( data$Department %in% dep.order.t$dep.f ) == FALSE,] %>%group_by(Department)%>%
  summarise(cnt=n_distinct(ID)) %>% arrange(cnt) %>% mutate(dep.xf=factor(Department))
#full order based on prt of tenured
dep.order<-c(order.exclude$dep.xf,dep.order.t$dep.f)
all_dep<-data%>%group_by(Department)%>%count()%>%arrange(Department)%>%select(Department)
```

```{r}
ui <- fluidPage(
  sidebarLayout(
    
    sidebarPanel(checkboxGroupInput(
        inputId="mylist",
        label="Which department(s) do you want to display?",
        choices=c("African and African American Studies",
"American Studies",
"Anthropology",
#"Asian American and Pacific Islander Studies",
"Biochemistry",
"Biology",
"Chemistry",
"Classical Studies",
#"Comparative Literature",
"Computer Science",
#"Creativity, the Arts, and Social Transformation",
"Economics",
"Education",
"English",
#"Environmental Studies",
#"Film, Television and Interactive Media",
"Fine Arts",
#"Genetic Counseling",
"German, Russian & Asian Languages and Literatures",
#"Graduate Professional Studies",
"Health: Science, Society and Policy",
"Heller",
"History",
"Hornstein Jewish Professional Leadership Graduate Program",
#"International and Global Studies Program",
"International Business School",
#"International Center for Ethics, Justice, and Public Life",
#"Islamic & Middle Eastern Study",
#"Jack, Joseph, and Morton Mandel Center for Studies in Jewish Education",
#"Journalism",
#"Legal Studies",
"Linguistics",
"Mandel Center for St in J Ed",
"Mathematics",
"Music",
#"Myra Kraft Transitional Year Program",
"Near Eastern & Judaic Studies",
#"Peace Conflict Coexistence",
"Philosophy",
"Physics",
"Politics",
"Psychology",
#"Religious Studies",
"Romance Studies",
"Schusterman Center",
#"Social Justice and Social Policy",
"Sociology",
#"Student Support Services",
"Theater Arts",
#"University Writing Program",
"Women's, Gender, and Sexuality Studies"
#"Writing Program"
),
        selected=c("African and African American Studies"))),
  
      mainPanel(plotOutput("line"))))

server <- function(input, output,session) {
  output$line<-renderPlot({
    
plot_dat<-data%>%filter(Department %in% input$mylist ) %>%#has to be INPUT$inputid
  group_by(Year,Department,`Tenure Status`)%>%
  summarise(cnt=n_distinct(ID))%>%mutate(prt=percent(cnt/sum(cnt),digits = 0))%>%
    filter(`Tenure Status`=="Tenure Line")
  
ggplot(data=plot_dat, aes(x=Year,y=prt,color=Department,group=Department))+geom_line()+theme_lz.html()+
  #scale_color_discrete(limits = dep.order[dep.order %in% input$mylist])+
    scale_y_continuous(labels=scales::percent_format(accuracy = 1))+
    theme(axis.text.y=element_text(),legend.direction = "vertical")+
    theme(panel.grid.major.y = element_line(color = "grey95"))+
    labs(x="",y="",title=str_wrap("Selected Departments' Trends of Tenure-Line Faculty Proportion",40))
  })}

# Run the application 
shinyApp(ui = ui, server = server)
```


# Summary

* Tenure-line (TL) proportion increased 4% from 2016 to 2021, with 2020 being the highest 45%.
* TL proportion for assistant professor and professor both increased 12% and 5% respectively from 2016 to 2021. However, TL proportion for associate professor decreased 3% during 2016-2021.
* Although international, Hispanic, and black faculties used to have 12-17% less TL proportion than Asian and White faculties in 2016, after increases over the years, their TL proportion are similar in 2021 in a range of 45-51%.
* Consistent gender gaps of at least 20% difference in TL proportion still exist for White and Hispanic faculties in 2021. 
* TL proportion  of nine departments increased at least 13-40% during 2016-2021, with American Studies increased the most. However, three departments (Econ, Phil, Chem) decreased 11-13% from 2016 to 2021. 

