---
title: "2022 Fall Parent Survey Results \\vspace{-3cm}" 
date: "`r Sys.Date()`"
format: 
  pdf:
    documentclass: article
    classoption: []
    fig-width: 8
    geometry:
      - top=25mm
      - bottom=20mm
      - left=15mm
      - right=15mm
      - textwidth=4.5in
    keep-md: true
    include-in-header:
      - text: |
          \usepackage{titling}
          \setlength{\droptitle}{-1.5in}
          \pretitle{\begin{center}
          \includegraphics[height=1in]{/Users/linlizhou/Documents/Rprojects/IR.png}\LARGE\\}
      - text: |
          \usepackage{fancyhdr}
          \addtolength{\headheight}{0.7cm}
    
          \pagestyle{fancy} 
          \fancyhead{}
          \fancyfoot{}
    
          \fancyhead[LO]{\includegraphics[height=1.3cm]{/Users/linlizhou/Documents/Rprojects/IR.png}}
          \fancyhead[RE]{\vspace{4mm}\textbf{AAC Courses Review}}
          \fancyfoot[C]{\thepage}
    
          \renewcommand{\headrulewidth}{0pt}
editor: visual
---

```{r libraries, include = FALSE}
source("/Users/linlizhou/Documents/Rprojects/IR-Projects/theme_source.R")
#change 
#format: 
#  pdf:
#to
#format:
#  docx:
#    reference-doc: /Users/linlizhou/Documents/Rprojects/IR-Projects/lasell.report.template.docx
#    prefer-html: true
```

```{r load_rawdf.surveyexport}
raw<-read_csv("/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Surveys/Lasell Internal/Parent Survey/fall 2022/20221213114001-SurveyExport.csv")
lapply(raw[1:60], unique)
```

```{r parentdf.andcleancols}
#remove unnecessary starter cols
parent<-raw%>%
  #remove unnecessary starter cols
  select(-(`Response ID`:`Date Submitted`),#keep status
                     -(`Contact ID`: `Invite Status`),#keep email
                     -(`First Name`:Source),
                     -(`Invite Custom Field 1`:`Invite Custom Field 10`))%>%
  #remove empty rows/cols (including header has to be NA)
  janitor::remove_empty(c("rows", "cols"))

#remove NA cols
parent<-parent[ , colSums(is.na(parent)) < nrow(parent)] #sum each col's # of NA rows, not all rows are NA

# convinient col names:
parent<-janitor::clean_names(parent)

#284 rows/observations
#look at the survey instruction:
```

```{r parent_rename}
#rename cols: 
# refer back to survey questions pdf
# lapply(parent[4:ncol(parent)-1], unique)

#rule: same question same starter_texts
parent<-parent%>%rename(
## 1 satisfaction
satis.overall=overall_how_satisfied_are_you_with_your_childs_undergraduate_education_so_far,

#1.1 academic satisfaction
satis.aca_instruct=overall_quality_of_instruction_as_a_parent_guardian_how_satisfied_are_you_with_the_quality_of_each_of_the_following_aspects_of_your_students_academic_experience_at_lasell_if_any_aspect_does_not_apply_please_select_n_a,

satis.aca_advise=quality_of_academic_advising_as_a_parent_guardian_how_satisfied_are_you_with_the_quality_of_each_of_the_following_aspects_of_your_students_academic_experience_at_lasell_if_any_aspect_does_not_apply_please_select_n_a,

satis.aca_faculty=contact_with_faculty_as_a_parent_guardian_how_satisfied_are_you_with_the_quality_of_each_of_the_following_aspects_of_your_students_academic_experience_at_lasell_if_any_aspect_does_not_apply_please_select_n_a,

satis.aca_tutor=tutoring_and_other_academic_help_as_a_parent_guardian_how_satisfied_are_you_with_the_quality_of_each_of_the_following_aspects_of_your_students_academic_experience_at_lasell_if_any_aspect_does_not_apply_please_select_n_a,

#1.2 service satisfaction
satis.sv_house=student_housing_as_a_parent_guardian_how_satisfied_are_you_with_the_quality_of_each_of_the_following_aspects_of_campus_services_and_facilities_at_lasell_if_any_aspect_does_not_apply_please_select_n_a,

satis.sv_career=career_counseling_as_a_parent_guardian_how_satisfied_are_you_with_the_quality_of_each_of_the_following_aspects_of_campus_services_and_facilities_at_lasell_if_any_aspect_does_not_apply_please_select_n_a,

satis.sv_parent=the_office_of_parent_engagement_as_a_parent_guardian_how_satisfied_are_you_with_the_quality_of_each_of_the_following_aspects_of_campus_services_and_facilities_at_lasell_if_any_aspect_does_not_apply_please_select_n_a,

satis.sv_dine=dining_as_a_parent_guardian_how_satisfied_are_you_with_the_quality_of_each_of_the_following_aspects_of_campus_services_and_facilities_at_lasell_if_any_aspect_does_not_apply_please_select_n_a,

satis.sv_fin=financial_aid_office_as_a_parent_guardian_how_satisfied_are_you_with_the_quality_of_each_of_the_following_aspects_of_campus_services_and_facilities_at_lasell_if_any_aspect_does_not_apply_please_select_n_a,

satis.sv_health=health_services_as_a_parent_guardian_how_satisfied_are_you_with_the_quality_of_each_of_the_following_aspects_of_campus_services_and_facilities_at_lasell_if_any_aspect_does_not_apply_please_select_n_a,

satis.sv_mental=mental_health_counseling_as_a_parent_guardian_how_satisfied_are_you_with_the_quality_of_each_of_the_following_aspects_of_campus_services_and_facilities_at_lasell_if_any_aspect_does_not_apply_please_select_n_a,

satis.sv_account=financial_services_student_accounts_as_a_parent_guardian_how_satisfied_are_you_with_the_quality_of_each_of_the_following_aspects_of_campus_services_and_facilities_at_lasell_if_any_aspect_does_not_apply_please_select_n_a,

satis.sv_police=campus_police_as_a_parent_guardian_how_satisfied_are_you_with_the_quality_of_each_of_the_following_aspects_of_campus_services_and_facilities_at_lasell_if_any_aspect_does_not_apply_please_select_n_a,

#1.3 life satisfaction

satis.life_safe=your_students_safety_on_campus_as_a_parent_guardian_how_satisfied_are_you_with_the_quality_of_each_of_the_following_aspects_of_campus_life_at_lasell_if_any_aspect_does_not_apply_please_select_n_a,

satis.life_race=ethnic_and_racial_diversity_on_campus_as_a_parent_guardian_how_satisfied_are_you_with_the_quality_of_each_of_the_following_aspects_of_campus_life_at_lasell_if_any_aspect_does_not_apply_please_select_n_a,

satis.life_belong=sense_of_community_on_campus_as_a_parent_guardian_how_satisfied_are_you_with_the_quality_of_each_of_the_following_aspects_of_campus_life_at_lasell_if_any_aspect_does_not_apply_please_select_n_a,

satis.life_social=social_life_on_campus_as_a_parent_guardian_how_satisfied_are_you_with_the_quality_of_each_of_the_following_aspects_of_campus_life_at_lasell_if_any_aspect_does_not_apply_please_select_n_a,

## information
#2.1 info on food committee

infofood_knowcommittee=are_you_aware_that_there_is_a_student_run_food_committee_that_is_open_to_all_students_and_meets_twice_a_month_on_thursdays_with_the_director_of_dining_services_and_vice_president_of_administrative_services,

infofood_attendcommittee=has_your_student_attended_one_of_those_meetings_of_student_run_food_committee_to_share_comments_and_concerns,

infofood_committeequal=other_write_in_has_your_student_attended_one_of_those_meetings_of_student_run_food_committee_to_share_comments_and_concerns,

infofood_try=would_you_be_interested_in_coming_to_lasell_to_try_the_food,

#2.2 info received/need
inforecv_counsel=counseling_services_please_rate_each_of_the_following_areas_on_the_information_you_have_received_about_this_area_relative_to_your_needs,

inforecv_athletic=athletics_please_rate_each_of_the_following_areas_on_the_information_you_have_received_about_this_area_relative_to_your_needs,

inforecv_finaid=financial_aid_please_rate_each_of_the_following_areas_on_the_information_you_have_received_about_this_area_relative_to_your_needs,

inforecv_prtevent=events_for_parents_i_e_family_friends_alumni_weekend_webinars_please_rate_each_of_the_following_areas_on_the_information_you_have_received_about_this_area_relative_to_your_needs,

inforecv_acapolicy=academic_life_and_policies_please_rate_each_of_the_following_areas_on_the_information_you_have_received_about_this_area_relative_to_your_needs,

inforecv_activity=off_campus_programs_i_e_study_abroad_please_rate_each_of_the_following_areas_on_the_information_you_have_received_about_this_area_relative_to_your_needs,

inforecv_career=career_counseling_please_rate_each_of_the_following_areas_on_the_information_you_have_received_about_this_area_relative_to_your_needs,

inforecv_health=health_services_please_rate_each_of_the_following_areas_on_the_information_you_have_received_about_this_area_relative_to_your_needs,

inforecv_house=residential_life_and_policies_please_rate_each_of_the_following_areas_on_the_information_you_have_received_about_this_area_relative_to_your_needs,

inforecv_event=special_events_on_campus_please_rate_each_of_the_following_areas_on_the_information_you_have_received_about_this_area_relative_to_your_needs,

inforecv_resource=resources_for_parents_i_e_office_of_parent_engagement_parents_council_please_rate_each_of_the_following_areas_on_the_information_you_have_received_about_this_area_relative_to_your_needs,

inforecv_acasupport=academic_support_services_i_e_tutoring_please_rate_each_of_the_following_areas_on_the_information_you_have_received_about_this_area_relative_to_your_needs,

inforecv_religion=religious_life_please_rate_each_of_the_following_areas_on_the_information_you_have_received_about_this_area_relative_to_your_needs,

inforecv_stuorg=student_organizations_please_rate_each_of_the_following_areas_on_the_information_you_have_received_about_this_area_relative_to_your_needs,

inforecv_finoption=financing_options_i_e_installments_pre_pay_please_rate_each_of_the_following_areas_on_the_information_you_have_received_about_this_area_relative_to_your_needs,

inforecv_safe=campus_safety_please_rate_each_of_the_following_areas_on_the_information_you_have_received_about_this_area_relative_to_your_needs,

#2.3 info relied on
inforely_stu=talking_with_my_student_to_what_extent_do_you_rely_on_each_of_the_following_sources_for_information_about_college_life_and_policies,

inforely_mainweb=visiting_the_main_lasell_website_to_what_extent_do_you_rely_on_each_of_the_following_sources_for_information_about_college_life_and_policies,

inforely_call=calling_someone_at_lasell_to_what_extent_do_you_rely_on_each_of_the_following_sources_for_information_about_college_life_and_policies,

inforely_parent=talking_with_other_parents_to_what_extent_do_you_rely_on_each_of_the_following_sources_for_information_about_college_life_and_policies,

inforely_prtweb=visiting_the_parents_and_families_webpage_to_what_extent_do_you_rely_on_each_of_the_following_sources_for_information_about_college_life_and_policies,
  
inforely_facebook=using_the_parents_network_facebook_group_to_what_extent_do_you_rely_on_each_of_the_following_sources_for_information_about_college_life_and_policies,

inforely_email=emails_from_the_office_of_parent_engagement_or_another_office_to_what_extent_do_you_rely_on_each_of_the_following_sources_for_information_about_college_life_and_policies,

#2.4 info from students
infoconv_aca=current_academic_matters_how_often_do_you_discuss_each_of_the_following_with_your_student,

infoconv_gradplan=graduate_school_plans_how_often_do_you_discuss_each_of_the_following_with_your_student,

infoconv_career=career_plans_how_often_do_you_discuss_each_of_the_following_with_your_student,

infoconv_fin=finances_how_often_do_you_discuss_each_of_the_following_with_your_student,

infoconv_campus=campus_life_how_often_do_you_discuss_each_of_the_following_with_your_student,

infoconv_health=your_students_physical_or_emotional_health_how_often_do_you_discuss_each_of_the_following_with_your_student,

## 3. events
# 3.1 attended events
evted_townhall=did_you_attend_the_virtual_parents_town_hall_in_october,
evted_townhall_qual=please_share_your_thoughts_recommendation_for_the_virtual_parent_town_hall_you_attended_in_october,

evted_wkend=did_you_attend_family_friends_and_alumni_weekend,
evt_wkend_qual=please_share_your_thoughts_recommendation_for_the_family_friends_and_alumni_weekend_you_attended,

evted_recept=did_you_attend_the_2022_parents_reception,
evted_recept_qual=please_share_your_thoughts_recommendation_for_the_2022_parents_reception_you_attended,

# 3.2 will attend events
evted_recept23=will_you_be_attending_the_2023_parents_reception_a_parent_only_event_to_meet_other_parents_president_and_other_lasell_staff_members_this_is_a_free_event_which_will_likely_happen_on_a_weekend_in_april_and_will_be_held_on_campus_in_dunne_house,

evtwill_know=a_get_to_know_you_activity_with_other_parents_guardians_what_types_of_webinars_do_you_wish_the_office_of_parent_engagement_to_offer_in_the_spring,

evtwill_staff=opportunity_to_meet_the_deans_and_other_faculty_members_what_types_of_webinars_do_you_wish_the_office_of_parent_engagement_to_offer_in_the_spring,

evtwill_senior=parents_guardians_of_seniors_to_discuss_what_comes_next_after_lasell_and_what_seniors_should_be_doing_to_prepare_for_graduation_what_types_of_webinars_do_you_wish_the_office_of_parent_engagement_to_offer_in_the_spring,

evtwill_social=open_discussion_with_staff_members_for_parents_guardians_with_students_struggling_to_get_involved_or_make_friends_what_types_of_webinars_do_you_wish_the_office_of_parent_engagement_to_offer_in_the_spring,

evtwill_otheropt=other_write_in_required_what_types_of_webinars_do_you_wish_the_office_of_parent_engagement_to_offer_in_the_spring_168,

evtwill_otherqual=other_write_in_required_what_types_of_webinars_do_you_wish_the_office_of_parent_engagement_to_offer_in_the_spring_169,

## overall

satis.overall_qual=please_share_any_additional_questions_or_comments_about_your_experiences_as_a_parent_or_guardian_of_a_lasell_students
)
```

```{r parent_rmmorecols}
#check: lapply(parent[3:ncol(parent)-1], unique)
parent<-parent%>%select(-(academic_how_often_do_you_discuss_each_of_the_following_with_your_student:no_idea_what_he_wants_to_do_and_school_no_resources_how_often_do_you_discuss_each_of_the_following_with_your_student))
```

```{r qualvsquan}
parent.quan<-parent%>%select(!ends_with("qual"))#check: %>%names()#61
parent.qual<-parent%>%select(ends_with("qual"))#check: %>%names()#6
```

```{r parent.long_group.cols}
#check: lapply(parent.quan, unique)
#names(parent.quan)
parent.satis<-parent.quan%>%select(starts_with("satis"))%>%
  #group similar items together as one variable
  pivot_longer(cols=starts_with("satis.aca"),names_to="satis.aca",values_to="satis.aca_value")%>%
  pivot_longer(cols=starts_with("satis.sv"),names_to="satis.sv",values_to="satis.sv_value")%>%
  pivot_longer(cols=starts_with("satis.life"),names_to="satis.life",values_to="satis.life_value")

parent.info<-parent.quan%>%select(starts_with("info"))%>%
  pivot_longer(cols=starts_with("infofood"),names_to="infofood",values_to="infofood_value")%>%
  pivot_longer(cols=starts_with("inforecv"),names_to="inforecv",values_to="inforecv_value")%>%
  pivot_longer(cols=starts_with("inforely"),names_to="inforely",values_to="inforely_value")%>%
  pivot_longer(cols=starts_with("infoconv"),names_to="infoconv",values_to="infoconv_value")

parent.evt<-parent.quan%>%select(starts_with("evt"),status)%>%
  pivot_longer(cols=starts_with("evted"),names_to="evted",values_to="evted_value")%>%
  pivot_longer(cols=starts_with("evtwill"),names_to="evtwill",values_to="evtwill_value")
```

```{r save_parent_commentout}
#wb<-createWorkbook()

#addWorksheet(wb,"parent")
#writeData(wb,sheet = "parent",x=parent)

#addWorksheet(wb,"parent.quan")
#writeData(wb,sheet = "parent.quan",x=parent.quan)

#addWorksheet(wb,"parent.qual")
#writeData(wb,sheet = "parent.qual",x=parent.qual)

#addWorksheet(wb,"parent.satis")
#writeData(wb,"parent.satis",x=parent.satis)
#addWorksheet(wb,"parent.info")
#writeData(wb,"parent.info",x=parent.info)
#addWorksheet(wb,"parent.evt")
#writeData(wb,"parent.evt",x=parent.evt)

#saveWorkbook(wb,"/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Surveys/Lasell Internal/Parent Survey/fall 2022/parentsurveyworking2.xlsx",overwrite = TRUE)
```

# Survey Responses and Overall Satisfaction

```{r prep.response}
#contactlist<-read_excel("/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Surveys/Lasell Internal/Parent Survey/fall 2022/FY23 ALL Parents Email List.xls")/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Surveys/Lasell Internal/Parent Survey/fall 2022/FY23 ALL Parents Email List.xls
#harcode: 1492
#population N: nrow(contactlist)
#sample N: nrow(parent)

#sample by status
sample.status<-parent%>%count(status)
```

```{r plot.response}

#construct a tibble
plot.response<-tibble(items=c("Complete","Partial","Not respond"),
       values=c(sample.status[sample.status$status=="Complete",]$n,
                sample.status[sample.status$status=="Partial",]$n,
                1492-nrow(parent)))%>%
  mutate(items=factor(items,levels =c("Complete","Partial","Not respond") ))%>%
  mutate(prt=values/sum(values))%>%
#create a donut chart
ggplot(aes(x=2, y = values, fill=items)) + geom_bar(stat="identity") +
   xlim(0.5, 2.5)+ coord_polar(theta="y",start=0)+ #circled coord, pie centered on 2; show .5-2.5 of pie (0-.5 is the hole)
  scale_fill_manual(values = c(color_blue_lasell,"grey","#69b3e7"))+#,labels=c("..","..",..);number of colors and legend labels are based on how many groups

  annotate("text",x = 0.5, y = 0.5, fontface="bold", label = str_wrap( "19% Response Rate", width=10))+#0.5 is centered location
  annotate("text",x = 0.5, y = 0.75, hjust=-1.7,fontface="bold", label = str_wrap( "81%", width=10))+#left data label
  annotate("text",x = 2, y = 0.75, hjust=1.5,fontface="bold", label = str_wrap( "15%", width=10))+#right data label
  annotate("text",x = 0.5, y = 0.5,vjust=-2.5,hjust=3.5, fontface="bold", label = str_wrap( "4%", width=10))+#upperright data label
    theme_lz()+labs(x="",y="",fill="",title = "N=284")+theme(legend.position = "right",legend.direction = "vertical")
```

```{r plot.satisoverall}
#lapply(parent.quan,unique)
#names(parent.quan)
plot.satisoverall<-
parent%>%#check:count(satis.overall)
  mutate(satis.overall.gp=case_when(
    satis.overall%in%c("Dissatisfied","Very dissatisfied")~"negative",
    satis.overall%in%c("Satisfied","Very satisfied")~"positive",
    satis.overall=="Neither satisfied or dissatisfied"~"neutral"))%>%
  
  count(satis.overall.gp)%>%mutate(prt=n/sum(n))%>%
  
ggplot(aes(x=2, y = prt, fill=satis.overall.gp)) + geom_bar(stat="identity") +
   xlim(0.5, 2.5)+ coord_polar(theta="y",start=0)+ #circled coord, pie centered on 2; show .5-2.5 of pie (0-.5 is the hole)
  scale_fill_manual(values = c("grey",color_yellowlight,color_blue),labels=c("Dissatisfied","Neutral","Satisfied"),
                    guide = guide_legend(reverse = TRUE))+#number of colors and legend labels are based on how many groups

  annotate("text",x = 0.5, y = 0.5, fontface="bold", label = str_wrap( "Overall Satisfaction", width=10))+#0.5 is centered location
  annotate("text",x = 0.5, y = 0.75, hjust=-1.7,fontface="bold", label = str_wrap( "84%", width=10))+#right data label
  
  annotate("text",x = 2, y = 0.9, vjust=0,hjust=0.8,fontface="bold", label = str_wrap( "9%", width=10))+#left data label
  
  annotate("text",x = 2, y = 0.95,vjust=0,hjust=0.1, fontface="bold", label = str_wrap( "7%", width=10))+#upperright data label
    theme_lz()+labs(title="",x="",y="",fill="",subtitle = "")+theme(legend.position = "right",legend.direction = "vertical")
```

```{r report_responserate.overall, fig.height=2.8,include=TRUE}
gridExtra::grid.arrange(plot.response, plot.satisoverall, nrow=1, widths=c(1,1))
#add subtitle: n=284
```

The 2022 Fall Parent Survey received 284 responses, representing a 19%
response rate. Among those respondents, 84% of parents are **satisfied**
with their students' experiences at Lasell.

# Satisfaction

```{r plot.satis_aca}
#5
#"satis.overall"            "satis.aca_instruct"      "satis.aca_advise"         "satis.aca_tutor"         "satis.aca_faculty"

#since we show more than one group in bar chart, we need to set y label's order 
#the order of y lable is based on prt of the "positive" group
satis_aca.setyorder<-parent.satis%>%#check: count(satis.aca_value)
  filter(!is.na(satis.aca_value),satis.aca_value!="N/A")%>%
  mutate(satis.aca_gp=case_when(
    satis.aca_value%in%c("Satisfied","Very satisfied")~"positive",
    satis.aca_value%in%c("Dissatisfied","Very Dissatisfied")~"negative",
    satis.aca_value=="Neither satisfied or dissatisfied"~"neutral"))%>%
  
  count(satis.aca,satis.aca_gp)%>%#mutate(prt=n/sum(n))
  ungroup()%>%group_by(satis.aca)%>%mutate(prt=n/sum(n))%>%
  filter(satis.aca_gp=="positive")%>%arrange(prt)%>%mutate(yorder=factor(satis.aca))

#lapply(parent.satis,unique)#satis.aca
plot.satis_aca<-
parent.satis%>%#check: count(satis.aca_value)
  filter(!is.na(satis.aca_value),satis.aca_value!="N/A")%>%
  mutate(satis.aca_gp=case_when(
    satis.aca_value%in%c("Satisfied","Very satisfied")~"positive",
    satis.aca_value%in%c("Dissatisfied","Very Dissatisfied")~"negative",
    satis.aca_value=="Neither satisfied or dissatisfied"~"neutral"))%>%
  
  count(satis.aca,satis.aca_gp)%>%#mutate(prt=n/sum(n))
  ungroup()%>%group_by(satis.aca)%>%mutate(prt=n/sum(n))%>%

ggplot(aes(y=factor(satis.aca, levels = satis_aca.setyorder$yorder, ordered = TRUE),
           x = prt, fill=satis.aca_gp)) +  
  geom_bar(stat="identity",position = position_stack(),width = 0.9)+#,position = position_dodge(),width=0.9
   scale_fill_manual(values = c("grey",color_yellowlight,color_blue),labels=c("Dissatisfied","Neutral","Satisfied"))+#number of colors and legend labels are based on how many groups

  scale_y_discrete(labels=c(str_wrap("Tutor/other help",width = 10),
                            str_wrap("Advising quality",width = 10),
                            str_wrap("Faculty contact",width = 10),
                            str_wrap("Instruction quality",width = 10)
                            ))+#the first label is for the bottom bar, 2nd label for 2nd bottombar...
  #  scale_x_continuous(labels = scales::percent)+
  geom_text(aes(label=percent(prt,digits = 0)),size=3,vjust=0,hjust=0,fontface="bold",position = position_stack(0))+#,position = position_dodge(0.9)
  #geom_text(aes(label=if_else(prt>.8, as.character(round(prt,2)),"")),hjust=1.5,size=3,fontface="bold",position = position_dodge(0.9))+geom_text(aes(label=if_else(prt<.8, as.character(round(prt,2)),"")),hjust=1.5,
    labs(title="Satisfaction in Students' Academic Experiences",x="",y="",fill="")+ theme_lz()+theme(axis.text.y = element_text(),legend.position = "")
```

```{r plot.satis_sv}
#9
# "satis.sv_house"          "satis.sv_career"          "satis.sv_police"         "satis.sv_dine"            "satis.sv_health"          "satis.sv_mental"          "satis.sv_fin"            "satis.sv_account"         "satis.sv_parent" 

#since we show more than one group in bar chart, we need to set y label's order 
#the order of y lable is based on prt of the "positive" group
satis_sv.setyorder<-
parent.satis%>%#check:count(satis.sv_value)
  filter(!is.na(satis.sv_value),satis.sv_value!="N/A")%>%
  mutate(satis.sv_gp=case_when(
    satis.sv_value%in%c("Satisfied","Very Satisfied")~"positive",
    satis.sv_value%in%c("Dissatisfied","Very dissatisfied")~"negative",
    satis.sv_value=="Neither dissatisfied or satisfied"~"neutral"))%>%#check:count(satis.sv_gp)
  
  count(satis.sv,satis.sv_gp)%>%#mutate(prt=n/sum(n))
  ungroup()%>%group_by(satis.sv)%>%mutate(prt=n/sum(n))%>%
  filter(satis.sv_gp=="positive")%>%arrange(prt)%>%mutate(yorder=factor(satis.sv))
  

#lapply(parent.satis,unique)# satis.sv
plot.satis_sv<-
parent.satis%>%#check:count(satis.sv_value)
  filter(!is.na(satis.sv_value),satis.sv_value!="N/A")%>%
  mutate(satis.sv_gp=case_when(
    satis.sv_value%in%c("Satisfied","Very Satisfied")~"positive",
    satis.sv_value%in%c("Dissatisfied","Very dissatisfied")~"negative",
    satis.sv_value=="Neither dissatisfied or satisfied"~"neutral"))%>%#check:count(satis.sv_gp)
  
  count(satis.sv,satis.sv_gp)%>%#mutate(prt=n/sum(n))
  ungroup()%>%group_by(satis.sv)%>%mutate(prt=n/sum(n))%>%

ggplot(aes(y=factor(satis.sv, levels = satis_sv.setyorder$yorder, ordered = TRUE), 
           x = prt, fill=satis.sv_gp)) +   
  geom_bar(stat="identity",position = position_stack(),width=0.9)+
   scale_fill_manual(values = c("grey",color_yellowlight,color_blue),labels=c("Dissatisfied","Neutral","Satisfied"),
                     guide = guide_legend(reverse = TRUE))+#number of colors and legend labels are based on how many groups

  scale_y_discrete(labels=c(str_wrap("Dining",width = 10),
                            str_wrap("Career Counseling",width = 10),
                            str_wrap("Mental Counseling",width = 10),
                            str_wrap("Health Services",width = 10),
                            str_wrap("Student Accounts",width = 10),
                            str_wrap("Financial Aid",width = 10),
                            str_wrap("Housing",width = 10),
                            str_wrap("Parent Engagement",width = 10),
                            str_wrap("Campus Police",width = 10)))+#the first label is for the bottom bar, 2nd label for 2nd bottombar...
  #  scale_x_continuous(labels = scales::percent)+
  geom_text(aes(label=percent(prt,digits = 0)),size=3,vjust=0.5,hjust=0,fontface="bold",position = position_stack(0))+
  #geom_text(aes(label=if_else(prt>.8, as.character(round(prt,2)),"")),hjust=1.5,size=3,fontface="bold",position = position_dodge(0.9))+geom_text(aes(label=if_else(prt<.8, as.character(round(prt,2)),"")),hjust=1.5,
    labs(title="Satisfaction in Services and Facilities",x="",y="",fill="")+ theme_lz()+theme(axis.text.y = element_text(),legend.position = "bottom")
```

```{r plot.satis_life}
#4
#"satis.life_social"        "satis.life_belong"       "satis.life_safe"          "satis.life_race" 

#lapply(parent.satis,unique)# satis.life and satis.life_value

#since we show more than one group in bar chart, we need to set y label's order 
#the order of y lable is based on prt of the "positive" group
satis_life.setyorder<-
parent.satis%>%#check:count(satis.life_value)
  filter(!is.na(satis.life_value),satis.life_value!="N/A")%>%
  mutate(satis.life_gp=case_when(
    satis.life_value%in%c("Satisfied","Very Satisfied")~"positive",
    satis.life_value%in%c("Dissatisfied","Very dissatisfied")~"negative",
    satis.life_value=="Neither dissatisfied or satisfied"~"neutral"))%>%#check:count(satis.life_gp)
  
  count(satis.life,satis.life_gp)%>%#mutate(prt=n/sum(n))
  ungroup()%>%group_by(satis.life)%>%mutate(prt=n/sum(n))%>%
  filter(satis.life_gp=="positive")%>%arrange(prt)%>%mutate(yorder=factor(satis.life))
  

#plot
plot.satis_life<-
parent.satis%>%#check:count(satis.life_value)
  filter(!is.na(satis.life_value),satis.life_value!="N/A")%>%
  mutate(satis.life_gp=case_when(
    satis.life_value%in%c("Satisfied","Very Satisfied")~"positive",
    satis.life_value%in%c("Dissatisfied","Very dissatisfied")~"negative",
    satis.life_value=="Neither dissatisfied or satisfied"~"neutral"))%>%#check:count(satis.life_gp)
  
  count(satis.life,satis.life_gp)%>%#mutate(prt=n/sum(n))
  ungroup()%>%group_by(satis.life)%>%mutate(prt=n/sum(n))%>%

ggplot(aes(y=factor(satis.life, levels = satis_life.setyorder$yorder, ordered = TRUE), 
           x = prt, fill=satis.life_gp)) +   
  geom_bar(stat="identity",position = position_stack(),width=0.9)+
   scale_fill_manual(values = c("grey",color_yellowlight,color_blue),labels=c("Dissatisfied","Neutral","Satisfied"))+#number of colors and legend labels are based on how many groups

  scale_y_discrete(labels=c(str_wrap("Social life",width = 10),
                            str_wrap("Sense of Community",width = 10),
                            str_wrap("Racial diversity",width = 10),
                            str_wrap("Campus safety",width = 10)))+#the first label is for the bottom bar, 2nd label for 2nd bottombar...
  #  scale_x_continuous(labels = scales::percent)+
  geom_text(aes(label=percent(prt,digits = 0)),size=3,vjust=0.5,hjust=0,fontface="bold",position = position_stack(0))+
  #geom_text(aes(label=if_else(prt>.8, as.character(round(prt,2)),"")),hjust=1.5,size=3,fontface="bold",position = position_dodge(0.9))+geom_text(aes(label=if_else(prt<.8, as.character(round(prt,2)),"")),hjust=1.5,
    labs(title="Satisfaction in Campus Life",x="",y="",fill="")+ theme_lz()+theme(axis.text.y = element_text(),legend.position = "")

```

```{r plot.satis_left}
plot.satis_left<-gridExtra::grid.arrange(plot.satis_aca, plot.satis_life, ncol=1, heights=c(1,1))
```

```{r report_satis, fig.height=4, include=TRUE}
gridExtra::grid.arrange(plot.satis_left, plot.satis_sv, nrow=1, widths=c(1,1))
```

Most parents are satisfied with students' academic experiences, campus
life, and most of Lasell services and facilities. The highest
satisfaction is in **campus safety**, with 92% of parents satisfied with
it. Other aspects that have more than 80% satisfaction rate include:
instruction quality, faculty contact with students, campus police,
parent engagement, and housing.

However, there are a few services and facilities on campus that receive
lower than 65% satisfaction rate, including **dining**, **career
counseling**, **mental counseling**, and **social life on campus**.

```{r satis_qualcmt}
###CAREER
#open discussion for identify good fit jobs and how to find jobs (3)
#specific, major-specific, 1:1 advisor help (3)

#professor's teaching method, lack academic community, tuition reset help financially, friendly community

###ACTIVITY
#campus activities more promotion through RAs (2)
#more events in the boston city, promote more
```

For dining, many parents are concerned about **food availability and
quality** at Lasell. Parents feel the dining hall lacks sufficient
supply of food when their students cannot eat in **after-hours**.
Parents hope that Lasell can have **more food vendors** that are
available in late hours. Also, parents mention worries about food
quality and the lack of **healthy food** options. Several parents would
like to meet with the food provider or staff members to talk about food
options. Some parents suggested that Lasell to change to a more
student-caring food service provider. Additionally, a parent suggested
providing **discounted** meal plans for students who only east twice a
day.

# Food Committee (FC)

```{r plot.fdcomt.aware}
#3
#"infofood_knowcommittee"   "infofood_attendcommittee" "infofood_try"

#lapply(parent.info,unique)# infofood and infofood_value

plot.fdcomt.aware<-parent.quan%>%#check: count(infofood_knowcommittee)
  filter(!is.na(infofood_knowcommittee))%>%
   count(infofood_knowcommittee)%>%mutate(prt=round(n/sum(n)*100,digits = 1))%>%

ggplot(aes(x=2, y = prt, fill=infofood_knowcommittee)) + geom_bar(stat="identity") +
   xlim(0.5, 2.5)+ coord_polar(theta="y",start=0)+ #circled coord, pie centered on 2; show .5-2.5 of pie (0-.5 is the hole)
  scale_fill_manual(values = c("grey",color_yellowlight,color_blue_lasell))+#number of colors and legend labels are based on how many groups; colors order alphebatically

  annotate("text",x = 0.5, y = 0.5, fontface="bold", label = str_wrap( "FC Awareness", width=10))+#0.5 is centered location
 annotate("text",x = 0.5, y = 0.75, hjust=3,fontface="bold", label = str_wrap( "79%", width=10))+#left data label  or 3
    annotate("text",x = 2, y = 0.9,vjust=0.5,hjust=-0.7, fontface="bold", label = str_wrap( "14%", width=10))+#upperright data label  (or 0.4 or 1.5 for slight right and left)
  annotate("text",x = 1, y = 0.6, vjust=-0.2,hjust=-3.4,fontface="bold", label = str_wrap( "7%", width=10))+#right data label  or -2.5
    theme_lz()+labs(title="",x="",y="",fill="",subtitle = "")
```

```{r plot.fdtry}
plot.fdtry<-parent.quan%>%#check: count(infofood_try)
  filter(!is.na(infofood_try))%>%
  mutate(infofood_try=factor(infofood_try,levels = c("No","Maybe","Yes")))%>%
   count(infofood_try)%>%mutate(prt=round(n/sum(n)*100,digits = 0))%>%

ggplot(aes(x=2, y = prt, fill=infofood_try)) + geom_bar(stat="identity") +
   xlim(0.5, 2.5)+ coord_polar(theta="y",start=0)+ #circled coord, pie centered on 2; show .5-2.5 of pie (0-.5 is the hole)
  scale_fill_manual(values = c("grey",color_yellowlight,color_blue_lasell))+#number of colors and legend labels are based on how many groups; colors order alphebatically

annotate("text",x = 0.5, y = 0.5, fontface="bold", label = str_wrap( "Try Lasell Food", width=10))+#0.5 is centered location
annotate("text",x = 0.5, y = 0.5, vjust=0,hjust=3,fontface="bold", label = str_wrap( "47%", width=10))+#left data label  or 3
  
    annotate("text",x = 1.5, y = 0.15,hjust=-1.5, fontface="bold", label = str_wrap( "24%", width=10))+#upperright data label  (or 0.4 or 1.5 for slight right and left)
  annotate("text",x = 0.5, y = 0.5, vjust=5,hjust=-1,fontface="bold", label = str_wrap( "29%", width=10))+#right data label  or -2.5
    theme_lz()+labs(title="",x="",y="",fill="",subtitle = "")
```

```{r plot.fdattend}
plot.fdattend<- parent.quan%>%#check: count(infofood_attendcommittee)
  filter(!is.na(infofood_attendcommittee),infofood_attendcommittee!="Other - Write In",
         infofood_attendcommittee!="I don't know")%>%#check: count(infofood_attendcommittee)
   count(infofood_attendcommittee)%>%mutate(prt=round(n/sum(n)*100,digits = 0))%>%

ggplot(aes(x=2, y = prt, fill=infofood_attendcommittee)) + geom_bar(stat="identity") +
   xlim(0.5, 2.5)+ coord_polar(theta="y",start=0)+ #circled coord, pie centered on 2; show .5-2.5 of pie (0-.5 is the hole)
  scale_fill_manual(values = c(color_yellowlight,color_blue,color_blue_lasell,color_redlight),labels=c("No, don't know","No, enjoy food", "Yes, helpful", "Yes, unhelpful"))+#number of colors and legend labels are based on how many groups; colors order alphebatically

annotate("text",x = 0.5, y = 0.5, fontface="bold", label = str_wrap( "Student Attend FC", width=10))+
 
annotate("text",x = 0.5, y = 0.5, vjust=0,hjust=3,fontface="bold", label = str_wrap( "51%", width=10))+ #mid-right
annotate("text",x = 0.5, y = 0.5, vjust=0,hjust=-2,fontface="bold", label = str_wrap( "42%", width=10))+#mid-left
  
annotate("text",x = 0.5, y = 0.5, vjust=-9,hjust=0, fontface="bold", label = str_wrap( "2%", width=10))+#top
annotate("text",x = 0.5, y = 0.5, vjust=-7,hjust=-1,fontface="bold", label = str_wrap( "5%", width=10))+
    theme_lz()+labs(title="",x="",y="",fill="",subtitle = "")+theme(legend.position = "bottom")
```

```{r report_fd,include=TRUE}
gridExtra::grid.arrange(plot.fdcomt.aware, plot.fdattend, plot.fdtry, nrow=1, widths=c(1,1,1))
```

For the student-run food committee (FC), 79% of parents are **not
aware** of it, and only 7% of parents think their students attended the
FC. There are 42% of parents think their students did not attend the FC
because they enjoy the food. Other parents commented that their students
have a **schedule conflict** during FC meeting times. Parents
recommended a **web forum** as an more accessible and efficient way to
give feedback about food.

Another reason for students not attending the FC is the belief that
nothing will change no matter what students say in the committee.
Parents are upset about the long-existing complaints about the food, and
hope to see if any **actions** are resulted from the FC.

Fifty-one percent of parents may be interested in trying Lasell food.
Apart from trying the food, some parents requested a **meeting** with
the food provider or staff members to talk and offer suggestions about
food service at Lasell.

```{r food_qualcmt}
###FOOD
#meeting about food (3)
#late food option and more vendors more availablity on campus, sufficient supply, healthy options, high-quality food, a better/care-student food service provider (4)
#discounted meal plan for students who eat 2 meals a day
###FC
#web forms feedback more effeicient due to schedlue conflict (4)
#nothing will change not matter meeting (3)
```

# Information Received

```{r plot.info_recv}
#16
#"inforecv_prtevent"       "inforecv_resource"        "inforecv_acapolicy"       "inforecv_house"           "inforecv_religion"       "inforecv_event"           "inforecv_safe"           "inforecv_stuorg"          "inforecv_athletic"       "inforecv_activity"        "inforecv_finaid"         "inforecv_finoption"       "inforecv_acasupport"      "inforecv_career"          "inforecv_health"         "inforecv_counsel"

#lapply(parent.info,unique)# inforecv and inforecv_value

#factorize legend
parent.info<-parent.info%>%mutate(inforecv_value=factor(inforecv_value,
                                                        levels =c("I receive TOO MUCH information",
                                                                  "I am SATISFIED with the information I have",
                                                                  "I do NOT need information",
                                                                  "I want MORE information") ))

#since we show more than one group in bar chart, we need to set y label's order 
#the order of y lable is based on prt of the "positive" group
info_recv.setyorder<-
parent.info%>%#check:count(inforecv_value)
  filter(!is.na(inforecv_value))%>%
  count(inforecv,inforecv_value)%>%#mutate(prt=n/sum(n))
  ungroup()%>%group_by(inforecv)%>%mutate(prt=n/sum(n))%>%
  filter(inforecv_value=="I want MORE information")%>%arrange(prt)%>%mutate(yorder=factor(inforecv))
  
#plot
plot.info_recv<-
parent.info%>%#check:count(inforecv_value)
  filter(!is.na(inforecv_value))%>%
  count(inforecv,inforecv_value)%>%#mutate(prt=n/sum(n))
  ungroup()%>%group_by(inforecv)%>%mutate(prt=n/sum(n))%>%

ggplot(aes(y=factor(inforecv, levels = info_recv.setyorder$yorder, ordered = TRUE), 
           x = prt, fill=inforecv_value)) +   
  geom_bar(stat="identity",position = position_stack(),width=0.9)+
   scale_fill_manual(values = c(color_redlight,color_blue_lasell,color_yellowlight,color_blue),
                     labels=c("Too much","Satisfied","No demand","Want more"),
                     guide=guide_legend(reverse = TRUE))+#number of colors and legend labels are based on how many groups

  scale_y_discrete(labels=c(str_wrap("Religious life",width = 30),
                            str_wrap("Athletics",width = 30),
                            str_wrap("Events for parents",width = 30),
                            str_wrap("Campus safety",width = 30),
                            str_wrap("Resources for parents",width = 30),
                            str_wrap("Financial options",width = 30),
                            str_wrap("Academic life and policies",width = 30),
                            str_wrap("Health services",width = 30),
                            str_wrap("Residential life and policies",width = 30),
                            str_wrap("Financial aid",width = 30),
                            str_wrap("Student organizations",width = 30),
                            str_wrap("Counseling services",width = 30),
                            str_wrap("Academic support services",width = 30),
                            str_wrap("Campus events",width = 30),
                            str_wrap("Off-campus programs",width = 30),
                            str_wrap("Career counseling",width = 30)
                            ))+#the first label is for the bottom bar, 2nd label for 2nd bottombar...
  #  scale_x_continuous(labels = scales::percent)+
  geom_text(aes(label=if_else(prt>.03,paste0(round(prt,digits = 2)*100,"%"),"")),
            size=3,vjust=0.5,hjust=0,fontface="bold",position = position_stack(0))+
  #geom_text(aes(label=if_else(prt>.8, as.character(round(prt,2)),"")),hjust=1.5,size=3,fontface="bold",position = position_dodge(0.9))+geom_text(aes(label=if_else(prt<.8, as.character(round(prt,2)),"")),hjust=1.5,
    labs(title="Please rate the information you have received:",x="",y="",fill="")+ theme_lz()+theme(axis.text.y = element_text(),legend.position = "bottom")
```

```{r plot.info_rely}
#7
#"inforely_stu"            "inforely_mainweb"         "inforely_prtweb"          "inforely_facebook"        "inforely_call"           "inforely_email"           "inforely_parent"

#lapply(parent.info,unique)# inforecv==>inforely and inforely_value

#since we show more than one group in bar chart, we need to set y label's order 
#the order of y lable is based on prt of the "positive" group
info_rely.setyorder<-
parent.info%>%#check:count(inforely_value)
  filter(!is.na(inforely_value))%>%
  count(inforely,inforely_value)%>%#mutate(prt=n/sum(n))
  ungroup()%>%group_by(inforely)%>%mutate(prt=n/sum(n))%>%
  filter(inforely_value=="To a great extent")%>%arrange(prt)%>%mutate(yorder=factor(inforely))
  
#plot
plot.info_rely<-
parent.info%>%#check:count(inforely_value)
  filter(!is.na(inforely_value))%>%
  mutate(inforely_value=factor(inforely_value,levels = c("Not at all","Very little","Somewhat","To a great extent")))%>%#factorize legend (inforely_value)
  count(inforely,inforely_value)%>%#mutate(prt=n/sum(n))
  ungroup()%>%group_by(inforely)%>%mutate(prt=n/sum(n))%>%

ggplot(aes(y=factor(inforely, levels = info_rely.setyorder$yorder, ordered = TRUE), 
           x = prt, fill=inforely_value)) +   
  geom_bar(stat="identity",position = position_stack(),width=0.9)+
   scale_fill_manual(values = c(color_redlight,color_yellowlight,color_blue,color_blue_lasell),
                     guide=guide_legend(reverse = TRUE))+#number of colors and legend labels are based on how many groups

  scale_y_discrete(labels=c(str_wrap("Other parents",width = 30),
                            str_wrap("Call staff",width = 30),
                            str_wrap("Parent website",width = 30),
                            str_wrap("Main website",width = 30),
                            str_wrap("Parent Facebook",width = 30),
                            str_wrap("Emails from Lasell",width = 30),
                            str_wrap("My students",width = 30)
                            ))+#the first label is for the bottom bar, 2nd label for 2nd bottombar...
  #  scale_x_continuous(labels = scales::percent)+
  geom_text(aes(label=if_else(prt>0.03,as.character(percent(prt,digits = 0)),"")),
            size=3,vjust=0.5,hjust=0,fontface="bold",position = position_stack(0))+
  #geom_text(aes(label=if_else(prt>.8, as.character(round(prt,2)),"")),hjust=1.5,size=3,fontface="bold",position = position_dodge(0.9))+geom_text(aes(label=if_else(prt<.8, as.character(round(prt,2)),"")),hjust=1.5,
    labs(title="To what extent do you rely on sources of information below",x="",y="",fill="")+ theme_lz()+theme(axis.text.y = element_text(),legend.position = "bottom")  #"Discuss with students about the following aspects"
```

```{r plot.info_conv}
#6
#"infoconv_aca"             "infoconv_gradplan"       "infoconv_career"          "infoconv_fin"           "infoconv_campus"          "infoconv_health" 
#lapply(parent.info,unique)# inforely==>infoconv and infoconv_value


#since we show more than one group in bar chart, we need to set y label's order 
#the order of y lable is based on prt of the "positive" group
info_conv.setyorder<-
parent.info%>%#check:count(infoconv_value)
  filter(!is.na(infoconv_value))%>%
  count(infoconv,infoconv_value)%>%#mutate(prt=n/sum(n))
  ungroup()%>%group_by(infoconv)%>%mutate(prt=n/sum(n))%>%
  filter(infoconv_value=="Always")%>%arrange(prt)%>%mutate(yorder=factor(infoconv))
  
#plot
plot.info_conv<-
parent.info%>%#check:count(infoconv_value)
  filter(!is.na(infoconv_value))%>%
  mutate(infoconv_value=factor(infoconv_value,levels = c("Never","Rarely","Sometimes","Often","Always")))%>%#factorize legend (infoconv_value)
  count(infoconv,infoconv_value)%>%#mutate(prt=n/sum(n))
  ungroup()%>%group_by(infoconv)%>%mutate(prt=n/sum(n))%>%

ggplot(aes(y=factor(infoconv, levels = info_conv.setyorder$yorder, ordered = TRUE), 
           x = prt, fill=infoconv_value)) +   
  geom_bar(stat="identity",position = position_stack(),width=0.9)+
   scale_fill_manual(values = c(color_redlight,color_yellowlight,color_bluelight,color_blue,color_blue_lasell),
                     guide=guide_legend(reverse = TRUE))+#number of colors and legend labels are based on how many groups

  scale_y_discrete(labels=c(str_wrap("Graduate school plans",width = 30),
                            str_wrap("Finances",width = 30),
                            str_wrap("Career plans",width = 30),
                            str_wrap("Campus life",width = 30),
                            str_wrap("Academic matters",width = 30),
                            str_wrap("Health (mental/physical)",width = 30)
                            ))+#the first label is for the bottom bar, 2nd label for 2nd bottombar...
  #  scale_x_continuous(labels = scales::percent)+
  geom_text(aes(label=if_else(prt>0.03,as.character(percent(prt,digits = 0)),"")),
            size=3,vjust=0.5,hjust=0,fontface="bold",position = position_stack(0))+
  #geom_text(aes(label=if_else(prt>.8, as.character(round(prt,2)),"")),hjust=1.5,size=3,fontface="bold",position = position_dodge(0.9))+geom_text(aes(label=if_else(prt<.8, as.character(round(prt,2)),"")),hjust=1.5,
    labs(title="Frequency of discussing the following with your student:",x="",y="",fill="")+ theme_lz()+theme(axis.text.y = element_text(),legend.position = "bottom")
```

```{r report_plan1}
#plot.info_left<-gridExtra::grid.arrange(plot.info_rely, plot.info_conv, ncol=1, heights=c(1,1))
#gridExtra::grid.arrange(plot.info_recv, plot.info_left, nrow=1, widths=c(1,1))
```

```{r report_info.recv,  fig.height=6, include=TRUE}
plot.info_recv
```

Above 70% of parents are satisfied with information received around
events for parents, campus safety, and resources for parents. However,
**career counseling** and **off-campus programs** have only a 40%
satisfaction rate from parents. The **career counseling** also has the
most unfulfilled demand, with 46% of parents wanting more information
around career counseling from Lasell.

From parents' comments, we find parents' suggestions that the current
career services are too general. Parents hope students have
**major-specific** guidance and learn the **process** of finding a job.
Many parents request the career center adviser to offer open discussions
with students about **how to identify** good-fit jobs.

```{r info_qualcmt}
###INFORMATION
#talk to RAs about dorm/student life, and their responsibilities and seek help (2). 
#talk to kids in sports and their trainers.
#how parents can help
#prep for grad school, what options and guidance in program options and costs and fundings
#Parents would like more guidance on master program options and financial costs and funding. 
```

In terms of off-campus programs, a few parents suggest to have **RAs**
involved in promoting campus activities. Also, a parent recommended to
have more or promote any existing events that happen in **Boston**,
which could be a good resource to learn.

# Information Source

```{r report_inforely.conv,  include=TRUE}
gridExtra::grid.arrange(plot.info_rely, plot.info_conv, nrow=1, widths=c(1,1))
```

**Students** are the primary source of information for 76% of parents.
Meanwhile, 58% of parents rely on **emails from Lasell** as an
information source. Parents discuss most frequently with students about
**mental/physical health, academic matters, campus life, and career
plans**. Other topics like finances and graduate school plans do not
happen as often between parents and students. A parent mention that they
hope Lasell can provide information about **graduate school** options
and the costs and funding for graduate school.

# Events

```{r plot.evted}
#4
#"evted_townhall"           "evted_wkend"             "evted_recept"     "evted_recept23" 
#check: lapply(parent.evt, unique)#evted and evted_value

#since we show more than one group in bar chart, we need to set y label's order 
#the order of y lable is based on prt of the "positive" group
evted.setyorder<-
parent.evt%>%filter(!is.na(evted_value))%>%
  mutate(evted_value.gp=if_else(evted_value%in%c("No, I had a scheduling conflict","No, I have a scheduling conflict"),"Schedule conflict",
                            if_else(evted_value%in%c("No, I was not interested.","No, I am not interested"),"Not interested",
                            if_else(evted_value=="Yes","Yes","Don't know"))))%>%#check: count(evted_value.gp,evted_value)
  count(evted,evted_value.gp)%>%ungroup()%>%group_by(evted)%>%mutate(prt=n/sum(n))%>%
  filter(evted_value.gp=="Yes")%>%arrange(prt)%>%mutate(yorder=factor(evted))
  
#plot
plot.evted<-
parent.evt%>%filter(!is.na(evted_value))%>%
  mutate(evted_value.gp=if_else(evted_value%in%c("No, I had a scheduling conflict","No, I have a scheduling conflict"),"Schedule conflict",
                            if_else(evted_value%in%c("No, I was not interested.","No, I am not interested"),"Not interested",
                            if_else(evted_value=="Yes","Yes","Don't know"))))%>%#check: count(evted_value.gp,evted_value)
  mutate(evted_value.gp=factor(evted_value.gp,levels = c("Not interested","Schedule conflict","Don't know","Yes")))%>%
  count(evted,evted_value.gp)%>%ungroup()%>%group_by(evted)%>%mutate(prt=n/sum(n))%>%

ggplot(aes(y=factor(evted, levels = evted.setyorder$yorder, ordered = TRUE), 
           x = prt, fill=evted_value.gp)) +   
  geom_bar(stat="identity",position = position_stack(),width=0.9)+
   scale_fill_manual(values = c(color_redlight,color_greylight,color_yellowlight,color_blue_lasell),
                     guide = guide_legend(reverse = TRUE))+#number of colors and legend labels are based on how many groups

  scale_y_discrete(labels=c(str_wrap("2023 Parents Reception",width = 17),
                            str_wrap("2022 Virtual Parents Town Hall ",width = 17),
                            str_wrap("2022 Parents Reception",width = 17),
                            str_wrap("2022 Family, Friends, and Alumni Weekend",width = 17)
                            ))+#the first label is for the bottom bar, 2nd label for 2nd bottombar...
  #  scale_x_continuous(labels = scales::percent)+
  geom_text(aes(label=if_else(prt>0.03,as.character(percent(prt,digits = 0)),"")),size=3,vjust=0.5,hjust=0,fontface="bold",position = position_stack(0))+
  #geom_text(aes(label=if_else(prt>.8, as.character(round(prt,2)),"")),hjust=1.5,size=3,fontface="bold",position = position_dodge(0.9))+geom_text(aes(label=if_else(prt<.8, as.character(round(prt,2)),"")),hjust=1.5,
    labs(title="Did you/ will you attend:",x="",y="",fill="")+ theme_lz()+theme(axis.text.y = element_text(),legend.position = "bottom")
```

```{r plot.evtwill}
#4
#"evtwill_know"             "evtwill_staff"            "evtwill_senior"           "evtwill_social"
#check: lapply(parent.evt, unique)#evtwill and evtwill_value

 
#plot
plot.evtwill<-
parent.evt%>%#filter(!is.na(evtwill_value))%>%
  filter(evtwill!="evtwill_otheropt",
         status=="Complete")%>%#since this is the last question, we can filter out those who complete the survey
  count(evtwill,evtwill_value)%>%ungroup()%>%group_by(evtwill)%>%mutate(prt=n/sum(n))%>%
  filter(!is.na(evtwill_value))%>%

ggplot(aes(y=reorder(evtwill, prt), x = prt)) +   
  geom_bar(stat="identity",position = position_dodge(),width=0.9,fill=color_blue)+
  
  scale_y_discrete(labels=c(str_wrap("Know other parents",width = 17),
                            str_wrap("Students' social life",width = 17),
                            str_wrap("Meet deans/ faculty",width = 17),
                            str_wrap("Senior graduation & plans",width = 17)
                            ))+#the first label is for the bottom bar, 2nd label for 2nd bottombar...
  #  scale_x_continuous(labels = scales::percent)+
  geom_text(aes(label=percent(prt,digits = 0)),size=3,vjust=0.5,hjust=1,fontface="bold",position = position_dodge(0))+
  #geom_text(aes(label=if_else(prt>.8, as.character(round(prt,2)),"")),hjust=1.5,size=3,fontface="bold",position = position_dodge(0.9))+geom_text(aes(label=if_else(prt<.8, as.character(round(prt,2)),"")),hjust=1.5,
    labs(title="Interests in webinars:",x="",y="",fill="")+ theme_lz()+theme(axis.text.y = element_text(),legend.position = "")
```

```{r report_event,fig.height=3, include=TRUE}
gridExtra::grid.arrange(plot.evted, plot.evtwill, nrow=1, widths=c(2,1))
```

```{r event_qualcmt.eventspecific}
###PARENT.EVENT-IMPV
#directory of events
#more events on sunday
#more food
###PARENT.EVENT-ENJOY
#diverse options (3), well organized,  community connectted (4)
#good to see campus (2)
```

The FFA Weekend is the most popular event among parents, as 44% of
parents participated in it. Around 10% to 15% of parents attended or
will attend the parent receptions and town hall events. For parents who
did not participate, **scheduling conflict** is the main reason for
missing those events.

Parents who attended the above events enjoyed the events having
**diverse options** and being **well-organized**. Parents find these
events to be a good way to **build community** with other parents and
connect to Lasell. A few parents also appreciate the opportunity to
**visit the campus** during in-person events. In terms of suggestions,
parents hope future events could provide an **event directory**, have
some more events on **Sunday** (specific to the FFA weekend), and supply
more **food**.

In the spring semester, 42% of parents are interested in a webinar on
**senior graduation and plans**. 34% of parents are interested in
**meeting with academic deans and faculty**. Besides, a few parents
would like to talk to **RAs** about student life, and learn RA
responsibilities and how to seek help from them. A parent with a student
athlete hopes to talk to the athletic trainers.

# Summary

-   84% of parents are satisfied with Lasell overall. **Campus safety**
    has the highest satisfaction rate, with 92% of parents satisfied
    with it.

-   Dining Services and Food

    -   Dining services has the lowest (39%) satisfaction rate. Parents
        are mainly dissatisfied about the **food availability
        (late-hour) and quality (healthy food)**.

    -   Only 7% of parents think their students attended the food
        committee (FC), and 79% of parents are not aware of the
        existence of FC. As reflected in parents' comments, many
        students have schedule conflicts during the FC. Some other
        **accessible** ways of participation (e.g. web forums) may help
        increase participation. Some parents indicated that their
        students do not believe anything would change from the FC.
        Promotions of any **action** resulted from the FC would help
        change that belief and increase students' participation.

    -   51% of parents may be interested in trying Lasell's food.

-   Career Services

    -   Career counseling has the most unfulfilled demand, with 46% of
        parents wanting more information around career from Lasell.
        Parents hope students have **major-specific** guidance and learn
        the **process** of identifying a good-fit job.

-   Information

    -   **Students** are the primary source of information for 76%
        parents. 58% of parents also rely on **emails from Lasell** for
        information.

    -   Parents discuss **health** issues most frequently with students.
        Beyond the different information parents received, some parents
        requested to receive more information around **graduate school**
        options and costs.

    -   Only 40% are satisfied with information received around
        **off-campus activities**. Parents would like more promotion,
        probably with the help of **RAs**, for off-campus activities
        (e.g. activities in Boston).

-   Events

    -   Although over 40% of parents missed events due to **schedule
        conflicts**, parents who attended the FFA, Town Hall, and Parent
        Reception enjoyed the past events and consider them as
        well-organized, and a good opportunity to build **community**.

    -   In the spring semester, 42% of parents are interested in a
        webinar on **senior graduation and plans**. 34% of parents are
        interested in **meeting with academic deans and faculty**.
        Besides those offerings, parents would also like to talk to
        **RAs, athletic trainers, and food services** to learn their
        responsibilities and provide suggestions.
