---
title: "CommonDataset_report"
format: pdf
editor: visual
---

```{r set up}
source("/Users/linlizhou/Documents/Rprojects/IR-Projects/theme_source.R")
```

# CDS-I3 Class Size UG

```{r load_secsize}
secsize<-read_excel("/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Surveys/Common Data Set/2022-2023/datafiles/Course Count FA'22_cleanCDS-I.xlsx")
#for convience of reporting
secsize<-secsize%>%mutate(size=factor(size,levels =c("2-9","10-19","20-29","30-39") ))


```

```{r report_sec.size}
#section
secsize%>%filter(type=="section")%>%
  filter(!is.na(size))%>%#remove 1 individual enrolled classes
  count(size)%>%
  pivot_wider(names_from = size, values_from = n)#convnience to report

#check type: secsize%>%count(type)
#subsection: including lab and recitation
secsize%>%filter(type%in%c("lab","recitation"))%>%
  filter(!is.na(size))%>%#remove 1 individual enrolled classes
  count(size)%>%
  pivot_wider(names_from = size, values_from = n)#convnience to report

#compared to 2021-22 data: looks similar
# compared to raw(cleaned data): results are the same
```

# CDS-F Fall Enrollment: UG state, res/com, age

```{r load_fallenroll}
#degsk<-read_excel("/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Surveys/Common Data Set/2022-2023/datafiles/Fall 2022 UG Backup Data Report_cleanCDS-F.xlsx")
fallenroll<-read_excel("/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Surveys/Common Data Set/2022-2023/datafiles/Fall 2022 UG Backup Data Report_cleanCDS-FandB.xlsx")
```

## Degree seeking students

```{r report_degsk.state}
#important vars are admit_region, fyft and others
#admit region
fallenroll%>%filter(degreeseek=="Y")%>%#degree seeking students
  count(ADMIT_REGION)%>%
  filter(ADMIT_REGION!="intl",#exclude international from numerator and denominator
         !is.na(ADMIT_REGION))%>%#remove NA from discussion
  mutate(prt=n/sum(n)*100)%>%
  filter(ADMIT_REGION=="other states")#only report out of state prt
```

```{r report_degsk.res.com}
#recoding live on vs off campus
fallenroll$`Res/Comm`<-recode(fallenroll$`Res/Comm`,C="off campus",R="on campus")
#for convinience of reporting
fallenroll<-fallenroll%>%mutate(`Res/Comm`=factor(`Res/Comm`,
                          levels = c("on campus","off campus")))

#report
fallenroll%>%filter(degreeseek=="Y")%>%#degree seeking students
  count(`Res/Comm`)%>%
  mutate(prt=n/sum(n)*100)
```

```{r report_degsk.age}
#age 25 or older
fallenroll%>%filter(degreeseek=="Y")%>%#degree seeking students
  mutate(age.gp=if_else(Age>=25,">=25","<25"))%>%
  count(age.gp)%>%
  filter(!is.na(age.gp))%>%#remove the one NA
  mutate(prt=n/sum(n)*100)%>%
  filter(age.gp==">=25")#only report 25 or older
#check with raw data: 1186 <25; 1235 has age value; 96% is < 25


#avg age of full time students
fallenroll%>%filter(degreeseek=="Y")%>%#degree seeking students
  filter(`FT/PT`=="FT")%>%#full time students
  summarise(mn=mean(Age,na.rm=TRUE))

#avg age of all students
fallenroll%>%filter(degreeseek=="Y")%>%#degree seeking students
  summarise(mn=mean(Age,na.rm=TRUE))
```

## First time first year students

```{r report_ftfy}
#admit region
fallenroll%>%filter(degreeseek=="Y")%>%#degree seeking students
  filter(fyft=="Y")%>%#only first time/non-transfer/complt first year/new students
  count(ADMIT_REGION)%>%
  filter(ADMIT_REGION!="intl",#exclude international from numerator and denominator
         !is.na(ADMIT_REGION))%>%#remove NA from discussion
  mutate(prt=n/sum(n)*100)%>%
  filter(ADMIT_REGION=="other states")#only report out of state prt

#live on vs off campus
fallenroll%>%filter(degreeseek=="Y")%>%#degree seeking students
  filter(fyft=="Y")%>%#only fyft students
  count(`Res/Comm`)%>%
  mutate(prt=n/sum(n)*100)

#age
fallenroll%>%filter(degreeseek=="Y")%>%#degree seeking students
  filter(fyft=="Y")%>%#only fyft students
  mutate(age.gp=if_else(Age>=25,">=25","<25"))%>%
  count(age.gp)%>%
  filter(!is.na(age.gp))%>%#remove the one NA
  mutate(prt=n/sum(n)*100)%>%
  filter(age.gp==">=25")#only report 25 or older
#check with raw data: 315 <25; 324 has age value; 97% is < 25

#avg age of full time students
fallenroll%>%filter(degreeseek=="Y")%>%#degree seeking students
  filter(fyft=="Y")%>%#only fyft students
  filter(`FT/PT`=="FT")%>%#full time students
  summarise(mn=mean(Age,na.rm=TRUE))

#avg age of all students
fallenroll%>%filter(degreeseek=="Y")%>%#degree seeking students
  filter(fyft=="Y")%>%#only fyft students
  summarise(mn=mean(Age,na.rm=TRUE))
```

# CDS-B2 Fall Enrollment: UG race

```{r factorize_eth}
#for convnience of reporting
#check: fallenroll%>%count(Ethnicity)
fallenroll<-fallenroll%>%mutate(Ethnicity=factor(Ethnicity,
            levels = c("Non Resident Alien","Hispanic","Black or African American",
                       "White","Asian","Native Hawaiian or Other Pacific Islander",
                       "Two or more Races","Race and Ethnicity Unknown")))
```

## All enrolled students

```{r report_allenroll.race}
fallenroll%>%
  count(Ethnicity)
```

## Degree seeking students

```{r report_degsk.race}
#report degsk race
fallenroll%>%filter(degreeseek=="Y")%>%
  count(Ethnicity)
```

## First time first year students

```{r report_ftfy.degsk.race}
fallenroll%>%filter(degreeseek=="Y",#degree seeking students
                    fyft=="Y")%>%#first time first year students
  count(Ethnicity)
```

# CDS-B1 Fall Enrollment: UG FT/PT, gender

```{r recode_gender}
#for convnience of reporting
fallenroll$Gender<-recode(fallenroll$Gender,M="Men",F="Women")
#factorize order
fallenroll<-fallenroll%>%mutate(Gender=factor(Gender,
                levels = c("Men","Women")))
```

```{r report_UG.dgsk.fyft}
#UG, degsk, fy(new).ft(non-transfer/non-complete)
fallenroll%>%#UG
filter(degreeseek=="Y",#degree seeking
  #fyft=="Y"#alternative first year and first time filter
  `College Attend`=="NEW",#first year
  `Transfer YN`=="N",#first time: not a transfer student
  !str_detect(Curriculum, "[Cc]ompletion"), #first time: not trans-completion program
  )%>%
  count(`FT/PT`,Gender)%>%
  pivot_wider(names_from = `FT/PT`,values_from = n)
```

```{r UG.dgsk.fy.nft}
#UG, degsk, fy(new).nf-t (transfer/complete)
fallenroll%>%#UG
filter(degreeseek=="Y",#degree seeking
  `College Attend`=="NEW",#first year
  `Transfer YN`=="Y"| str_detect(Curriculum, "[Cc]ompletion")
  #not first time: transfer student OR not first time: in trans-completion program
  )%>%
  count(`FT/PT`,Gender)%>%
  pivot_wider(names_from = `FT/PT`,values_from = n)
#results: there are no transfer new dgsk UG students
```

```{r UG.dgsk.nfy}
#UG, degsk, nf-y(ret)
fallenroll%>%#UG
filter(degreeseek=="Y",#degree seeking
  `College Attend`!="NEW",#not first year
  #no matter transfer or not
  )%>%
  count(`FT/PT`,Gender)%>%
  pivot_wider(names_from = `FT/PT`,values_from = n)
```

```{r UG.ndgsk}
#UG, n-degsk
fallenroll%>%#UG
filter(degreeseek=="N",# notdegree seeking
  # no matter first year or not
  # no matter transfer or not
  )%>%
  count(`FT/PT`,Gender)%>%
  pivot_wider(names_from = `FT/PT`,values_from = n)
```

```{r confirm_dgsk}
#explore consistence of dgsk students: fallenroll%>%filter(degreeseek=="Y",`FT/PT`=="FT")%>%count(`College Attend`,`Transfer YN`)
#confirm gender by FT/PT
fallenroll%>%#UG
filter(degreeseek=="Y")%>%#degree seeking
  count(`FT/PT`,Gender)%>%
  pivot_wider(names_from = `FT/PT`,values_from = n)
```

```{r confirm_allUG}
fallenroll%>%#UG
  count(`FT/PT`,Gender)%>%
  pivot_wider(names_from = `FT/PT`,values_from = n)
```

# CDS-B1 Fall Enrollment: GD FT/PT, gender

```{r load_gdenroll}
gdenroll<-read_excel("/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Registrar Reports/2022 Fall/Graduate/2022 Fall Graduate Backup Data Report.xlsx")
#check duplication: gdenroll%>%count(People_Code_Id)%>%count(n)#no duplication 392

#check: glimpse(gdenroll)
```

```{r fulfill_genderNA}
#all non-transfer: gdenroll%>%count(Transfer_YN)#none transfer students
#dgsk: gdenroll%>%count(Degree,Curriculum)%>%View()#Degree!="NON" for dgsk students
#Gender: gdenroll%>%count(Gender)#3 unknown gender
#explore gender unknown: gdenroll%>%filter(Gender=="U")%>%select(People_Code_Id,Name,Age,New_Ret_Term_YN,Degree,Curriculum,Admit_Year)
#assign gender to unknown gender based on names
gdenroll[gdenroll$People_Code_Id=="P000057114","Gender"]<-"F"
gdenroll[gdenroll$People_Code_Id=="P000056435","Gender"]<-"M"
gdenroll[gdenroll$People_Code_Id=="P000038867","Gender"]<-"M"
#check Gender: gdenroll%>%count(Gender)#no unknown now

#reorder and recode Gender
gdenroll$Gender<-factor(gdenroll$Gender,levels = c("M","F"))
gdenroll$Gender<-recode(gdenroll$Gender,M="Men",F="Women")
```

```{r report_firsttime/year and others}
#first time and first year mean the same thing here

#dgsk new (first time/year in the program)
gdenroll%>%filter(Degree!="NON",#dgsk students 
                  New_Ret_Term_YN=="Y"#first year
                  )%>%count(FT_PT,Gender)%>%
  pivot_wider(names_from = FT_PT,values_from = n)


#other dgsk: dgsk and non new (not first time/year in the program)
gdenroll%>%filter(Degree!="NON",#dgsk students 
                  New_Ret_Term_YN=="N"#first year
                  )%>%count(FT_PT,Gender)%>%
  pivot_wider(names_from = FT_PT,values_from = n)

#other enrolled: non-dgsk
gdenroll%>%filter(Degree=="NON",#non-dgsk students 
                  )%>%count(FT_PT,Gender)

##confirm if all gd are reported
gdenroll%>%count(FT_PT,Gender)%>%
  pivot_wider(names_from = FT_PT,values_from = n)

#total gd: since no duplication: nrow(gdenroll)
```

# CDS I2 Faculty-student ratio: based on B1 student number

```{r ALLstudent_FTE}
#full time equivalent=full time student headcount + 1/3* part time student headcount
#UG students by FT/PT
ug_n<-fallenroll%>%count(`FT/PT`)
#GD students by FT/PT
gd_n<-gdenroll%>%count(FT_PT)

#FTE
ug_n[ug_n$`FT/PT`=="FT",]$n+ gd_n[gd_n$FT_PT=="FT",]$n + #full time
  1/3 * (ug_n[ug_n$`FT/PT`=="PT",]$n+ gd_n[gd_n$FT_PT=="PT",]$n )#part time
```

# CDS-B4: 2016 cohort finaid and completion

```{r load_cohort16_fin}
cohort16_fin<-read_excel("/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Surveys/Common Data Set/2022-2023/datafiles/Fall 2016 freeze file.cleanCDS-B4.xlsx",sheet ="cohort16fin" )

#glimpse(cohort16_fin)
#check: cohort16_fin%>%count(Cohort)
```

```{r report_2016cohort_fin}
#all students are dgsk, full time, fall enrolled (first year/new), first time (non-transfer) students
#CDS is just reporting finaid status in fall (no matter later semesters finaid status)

#1."Recipients of a Federal Pell Grant"
cohort16_fin%>%filter(pell=="receive")%>%
  nrow()#137

#2."Recipients of a Subsidized Stafford Loan who did not receive a pell"
cohort16_fin%>%filter(stafford=="receive",#Recipients of a Subsidized Stafford Loan"
                    pell=="not receive")%>%#who did not receive a pell"
  nrow()#186


#3.part1-in the finaid file, "Students who did not receive either a Pell Grant or a subsidized Stafford Loan"
cohort16_fin%>%filter(pell=="not receive",#not receiving pell-(but received other finaid)
                    stafford=="not receive")%>%#not receiving stafford-(but received other finaid)
  nrow()#89

#3.part2-not even in the finaid file, "Students who did not receive either a Pell Grant or a subsidized Stafford Loan"
#(students who did not receive any grant are not in the fin16 file) NA in pell and stafford (the two cols are mutated based on fin16 cols)
cohort16_fin%>%filter(is.na(pell), 
                    is.na(stafford))%>%
  #not receiving any finaid at all
  nrow()#25


#confirm all dgskFTft students: cohort16_fin%>%nrow()#437

```

```{r explore_completion.cols}
#glimpse(cohort16_fin)
#explore: #graduated (Y/N), grad date (Y-M-D), grad year (`complete year` actually)
```

```{r report_cohort2016_comp.4}
#1."Recipients of a Federal Pell Grant"
cohort16_fin%>%filter(`Grad Year`<=4)%>%
  filter(pell=="receive")%>%nrow()#72

#2."Recipients of a Subsidized Stafford Loan who did not receive a pell"
cohort16_fin%>%filter(`Grad Year`<=4)%>%
  filter(stafford=="receive",#Recipients of a Subsidized Stafford Loan"
         pell=="not receive")%>%#who did not receive a pell"
  nrow()#114


#3.part1-in the finaid file, "Students who did not receive either a Pell Grant or a subsidized Stafford Loan"
cohort16_fin%>%filter(`Grad Year`<=4)%>%
  filter(pell=="not receive",#not receiving pell-(but received other finaid)
        stafford=="not receive")%>%#not receiving stafford-(but received other finaid)
  nrow()#51

#3.part2-not even in the finaid file, "Students who did not receive either a Pell Grant or a subsidized Stafford Loan"
#(students who did not receive any grant are not in the fin16 file) NA in pell and stafford (the two cols are mutated based on fin16 cols)
cohort16_fin%>%filter(`Grad Year`<=4)%>%
  filter(is.na(pell), is.na(stafford))%>%
  #not receiving any finaid at all
  nrow()#12

#confirm all complete in 4 yr or less: cohort16_fin%>%filter(`Grad Year`<=4)%>%nrow() # 249
```

```{r report_cohort2016_comp.4-5}
#1."Recipients of a Federal Pell Grant"
cohort16_fin%>%filter(`Grad Year`>4,`Grad Year`<=5)%>%
  filter(pell=="receive")%>%nrow()#5

#2."Recipients of a Subsidized Stafford Loan who did not receive a pell"
cohort16_fin%>%filter(`Grad Year`>4,`Grad Year`<=5)%>%
  filter(stafford=="receive",#Recipients of a Subsidized Stafford Loan"
         pell=="not receive")%>%#who did not receive a pell"
  nrow()#4


#3.part1-in the finaid file, "Students who did not receive either a Pell Grant or a subsidized Stafford Loan"
cohort16_fin%>%filter(`Grad Year`>4,`Grad Year`<=5)%>%
  filter(pell=="not receive",#not receiving pell-(but received other finaid)
        stafford=="not receive")%>%#not receiving stafford-(but received other finaid)
  nrow()#1

#3.part2-not even in the finaid file, "Students who did not receive either a Pell Grant or a subsidized Stafford Loan"
#(students who did not receive any grant are not in the fin16 file) NA in pell and stafford (the two cols are mutated based on fin16 cols)
cohort16_fin%>%filter(`Grad Year`>4,`Grad Year`<=5)%>%
  filter(is.na(pell), is.na(stafford))%>%
  #not receiving any finaid at all
  nrow()#1

#confirm all complete in more than 4 but within 5 yr: cohort16_fin%>%filter(`Grad Year`>4,`Grad Year`<=5)%>%nrow()#11

```

```{r report_cohort2016_comp.5-6}
#1."Recipients of a Federal Pell Grant"
cohort16_fin%>%filter(`Grad Year`>5,`Grad Year`<=6)%>%
  filter(pell=="receive")%>%nrow()#2

#2."Recipients of a Subsidized Stafford Loan who did not receive a pell"
cohort16_fin%>%filter(`Grad Year`>5,`Grad Year`<=6)%>%
  filter(stafford=="receive",#Recipients of a Subsidized Stafford Loan"
         pell=="not receive")%>%#who did not receive a pell"
  nrow()#4


#3.part1-in the finaid file, "Students who did not receive either a Pell Grant or a subsidized Stafford Loan"
cohort16_fin%>%filter(`Grad Year`>5,`Grad Year`<=6)%>%
  filter(pell=="not receive",#not receiving pell-(but received other finaid)
        stafford=="not receive")%>%#not receiving stafford-(but received other finaid)
  nrow()#0

#3.part2-not even in the finaid file, "Students who did not receive either a Pell Grant or a subsidized Stafford Loan"
#(students who did not receive any grant are not in the fin16 file) NA in pell and stafford (the two cols are mutated based on fin16 cols)
cohort16_fin%>%filter(`Grad Year`>5,`Grad Year`<=6)%>%
  filter(is.na(pell), is.na(stafford))%>%
  #not receiving any finaid at all
  nrow()#0

#confirm all complete in more than 5 but within 6 yr: cohort16_fin%>%filter(`Grad Year`>5,`Grad Year`<=6)%>%nrow()
```

```{r confirm_com.6.tot}
cohort16_fin%>%filter(`Grad Year`<=6)%>%nrow()#266
```

# CDS-J Complete by UG CIP

```{r load_ipedscomplete}
complete<-read_excel("/Volumes/lasellshare/Faculty_Staff_Shares$/IR/Surveys/Common Data Set/2022-2023/datafiles/Complete.with.Ethnicity_age.eric.editted_cleanCDS-J.xlsx")

#complete%>%glimpse()
```

```{r convinient_reporting}
#for convinience of reporting: 
#complete<-complete%>%mutate(degree_awarded=factor(degree_awarded, levels = c("bachelor","associate","certificates"))) #, turns out can't change order in pivot_wider

#for convinence 
complete<-complete%>%mutate(cip.2g=factor(cip.2g,levels = c("01",  "03",  "04",  "05",  "09",  "10",  "11",  "12",  "13",  "14",  "15",  "16",  "19",  "22",  "23",  "24",  "25",  "26",  "27",  "28", "29",  "30",  "31",  "38",  "39",  "40",  "41",  "42",  "43",  "44",  "45",  "46",  "47",  "48",  "49",  "50",  "51",  "52",  "54")))

#related variables
#complete%>%count(Degree,degree_awarded)
  #only report UG (bachelor's certificate, associate, and bachelor's); 
  #no master/certificate: current certificates are all postbachelor
```

```{r hide-report_cip.prt}
#report bachelor and associate togher (adding up to 100%)
complete%>%
  filter(degree_awarded%in%c("bachelor's degree","associate degree"))%>%
  group_by(cip.2g,degree_awarded)%>%summarise(cnt=n())%>%
  ungroup()%>%#so that it's not prt within the second subgroup
  mutate(prt=round(cnt/sum(cnt),digits = 4))%>%select(-cnt)%>%
  pivot_wider(names_from = degree_awarded,values_from = prt, values_fill = 0)%>%
  View()#for copy paste

```

```{r report_bachelor_cip.prt}
#report bachelor separately (adding bachelor up to total 100%)
complete%>%
  filter(degree_awarded%in%c("bachelor's degree"))%>%
  group_by(cip.2g,.drop = FALSE)%>%#include all factor-levels in cip.2g
  summarise(cnt=n())%>%
  mutate(prt=round(cnt/sum(cnt),digits = 4))%>%select(-cnt)%>%
  View()#for copy paste: have to add 28&29 when reporting
```

```{r report_associate_cip.prt}
#report associate separately (adding associate up to total 100%)
complete%>%
  filter(degree_awarded%in%c("associate degree"))%>%
  group_by(cip.2g,.drop = FALSE)%>%#include all factor-levels in cip.2g
  summarise(cnt=n())%>%
  mutate(prt=round(cnt/sum(cnt),digits = 4))%>%select(-cnt)%>%
  View()#for copy paste

```

# CDS-B3 Complete by Degree

```{r report_degree.cnt}
#check mapping: complete%>%count(Degree,degree_awarded)
complete%>%count(degree_awarded)
```
