---
title: "Historical Trends of Faculty Tenure Status"
author: "Linli Zhou"
format: pptx
always_allow_html: true
editor: visual
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = TRUE, warning=FALSE, message=FALSE, fig.align = "center")
#theme
source("/Users/linlizhou/Documents/Rprojects/IR-Projects/theme_source.R")  #run code from saved r script
#load data
data<-readxl::read_excel("/Users/linlizhou/Documents/LASELL/Faculty Data for Analyst Candidates.xlsx")
```

# Research Questions

1.  How has the proportion of tenure-line (TL) and non-tenure (NT) faculty **changed over time**?

2.  How has the proportion of TL faculty in certain **rank, racial, or sex** groups changed over time?

3.  How has the proportion of TL and NTL faculty changed over time for different **departments**?

```{r clean, results='hide'}
#remove duplicated rows
data<-unique(data)#from 4003 to 3984 observations
#investigate duplicated ID/persons
unique(data$ID)%>%length()#1147 unique ID
data%>% group_by(ID) %>% summarise(cnt=n()) %>%arrange(-cnt) %>%filter(cnt>1) #815 duplicated IDs
#thus, need n_distinct ID in the following codes
```

# Trends

::: notes
* Tenure-line percentage has been increased since 2016 from 40% to 44% in 2021, with 2020 being the highest 45%. 
* Non-Tenure Faculty percentage has been decreased from 60% to 56%, with 2020 being the lowest 55%. 
* There are still 12% less Tenure-line Faculty than non-tenure.
:::

```{r unique TvsN across year}
data%>%group_by(Year, `Tenure Status`)%>%
summarise(cnt=n_distinct(ID))%>%mutate(prt=percent(cnt/sum(cnt),digits=0))%>%

ggplot(aes(color=factor(`Tenure Status`),x=factor(Year),y=prt,group=factor(`Tenure Status`)))+geom_line()+
geom_text(aes(label=prt),fontface="bold", size = 9)+
theme_lz_ppt()+
scale_y_continuous(breaks = seq(.4,.6,by=.05),labels = scales::percent)+
labs(title=str_wrap("Proportion of Faulcty in Different Tenured Status",50),x="",y="")+
scale_color_discrete(labels=c("Non-tenure","Tenure"),name="")+
theme(axis.text.y=element_blank())
```

# Trends Breakdown: Faculty Rank

::: notes
* Assistant professor tenure-line proportion dropped from 63% in 2016 to 57% in 2017 and became the lowest across professor ranks. However, the proportion but has been increasing ever since and reached 75% in 2021. 
* Professor experienced a slight drop from 68% in 2016 to 65% in 2018, but has increased ever since and reached 73% in 2021. 
* Associate professor has slight increase from 63% in 2016 to 66% in 2019, but dropped to 60% in 2021. 
:::

```{r tenured trend by rank}
#pivot table
data%>% filter(Rank=="Professor"|Rank=="Assistant Professor"| Rank=="Associate Professor")%>%
  group_by(Year, Rank,`Tenure Status`)%>%#2016 professor as a group -> proportions of (non) tenure for all professors in 2016
summarise(cnt=n_distinct(ID))%>%mutate(prt=percent(cnt/sum(cnt),digits=0))%>%filter(`Tenure Status`=="Tenure Line")%>%
  
#plot
ggplot(aes(color=factor(Rank),linetype=factor(Rank),x=factor(Year),y=prt,group=factor(Rank)))+geom_line()+
geom_text_repel(aes(label=prt),fontface="bold",size=6.5)+
  
#themes
scale_y_continuous(breaks = seq(.55,.75,by=.1),labels = scales::percent)+
scale_color_discrete(name="")+
scale_linetype_discrete(name="")+
 
theme_lz_ppt()+theme(axis.text.y=element_blank())+
labs(title="Tenure-line Faculty of Different Ranks",x="",y="")
```

# Trends Breakdown: Race

::: notes
* White faculties have the most stable tenure-line proportion -- within the 42-48% range. 
* Asian faculties experienced two dropped in 2018 and 2020 and only has 31-32% tenure-line proportion. The tenure-line proportion increased from 31% to 51% in 2021.

* Smaller racial groups have below 30% tenure-line proportions before 2018. However, their tenure-line proportion has been increasing since 2018 and reached 46-48% in 2021. 
+ International faculties have the lowest tenure-line proportion of 20% in 2016, but the proportion jumped to 50% in 2018 and 2021.
+ Hispanic faculties have increased tenure-line proportion from 33% in 2016 to 59% in 2020, and 55% in 2021, both are the highest among all racial groups in those two years. 
+ Black faculties' tenure-line proportion dropped from 50% in 2017 to 20% in 2018, but has been increasing by 7% each year to 44% in 2020 and kept stable at 45% in 2021.
:::

```{r facet two race bulk group,fig.width=15}
#race count
nrace<-data%>% filter( !(`Race/Ethnicity`%in% c("Unreported", "Two or More Races",NA)))%>%filter(`Tenure Status`=="Tenure Line")%>%
  group_by(`Race/Ethnicity`)%>%count()%>%arrange(-n)%>%mutate(race=factor(`Race/Ethnicity`))

#create two bulk group and pivot table
racepvt<-data%>%filter( !(`Race/Ethnicity`%in% c("Unreported", "Two or More Races",NA)))%>%mutate(RaceGroup=case_when(
  `Race/Ethnicity` %in% nrace$`Race/Ethnicity`[1:2] ~ "Larger Racial Group",
  `Race/Ethnicity` %in% nrace$`Race/Ethnicity`[3:5] ~ "Smaller Racial Group",))%>%
#pivot table  
  group_by(Year, `Race/Ethnicity`,RaceGroup,`Tenure Status`)%>%#2016 male as a group -> proportions of (non) tenure for all male professors in 2016
summarise(cnt=n_distinct(ID))%>%mutate(prt=percent(cnt/sum(cnt),digits=0))%>%filter(`Tenure Status`=="Tenure Line")

#max/min data label
#max.min<-racepvt%>%select(`Race/Ethnicity`,prt)%>%group_by(`Race/Ethnicity`)%>%summarise(max=max(prt),min=min(prt))%>%arrange(min)
  
#plot
racepvt%>%ggplot(aes(x=factor(Year),y=prt,color=factor(`Race/Ethnicity`),linetype=factor(`Race/Ethnicity`),group=factor(`Race/Ethnicity`)))+geom_line()+
  scale_color_manual(name="",limits=nrace$race, values = c("black","blue","chartreuse3","darkgoldenrod","brown1"),labels=c("White","Asian","International","Hispanic","Black"))+  
  scale_linetype_manual(name="",limits=nrace$race, values = c("solid","longdash","twodash","solid","longdash"),labels=c("White","Asian","International","Hispanic","Black"))+
  facet_wrap(~RaceGroup,labeller=labeller(RaceGroup= c(`Larger Racial Group`="Larger Racial Groups (Tenure-line Faculty>100)", `Smaller Racial Group`="Smaller Racial Groups (10<Tenure-line Faculty<100)") ) )+
  
geom_text_repel(aes(label=prt),size=5)+
#themes
scale_y_continuous(breaks = seq(.2,1,by=.2),labels = scales::percent)+
theme_lz_ppt()+theme(axis.text.y=element_text(size=12))+theme(panel.grid.major.y = element_line(color = "grey95"), panel.grid.minor.y = element_line(color = "grey95"))+#theme(legend.position = "right", legend.direction = "vertical")+
  guides(color = guide_legend(nrow = 1, byrow = TRUE))+
labs(title=str_wrap("Tenure-line Faculty in Different Racial Groups",80),x="",y="")
```

# Trends Breakdown: Legal Sex & Race

::: notes
* Hispanic and White faculties have a consistent gender gap with male faculties have higher tenure-line proportion than female faculties.
:::

```{r tenured trend by sex in different race, fig.width=15}
#pivot table
data%>% filter(`Race/Ethnicity`!="Unreported")%>% group_by(Year,`Race/Ethnicity`, `Tenure Status`,`Legal Sex`)%>%#2016 male as a group -> proportions of (non) tenure for all male professors in 2016
summarise(cnt=n_distinct(ID))%>%mutate(prt=percent(cnt/sum(cnt),digits=0))%>%filter(`Tenure Status`=="Tenure Line")%>%
#plot
ggplot(aes(color=factor(`Legal Sex`),x=factor(Year),y=prt,group=factor(`Legal Sex`)))+geom_line()+facet_wrap(~`Race/Ethnicity`)+
#geom_text_repel(aes(label=prt),fontface="bold",size=6.5)+
#themes
scale_y_continuous(breaks = seq(.2,.8,by=.2),labels = scales::percent)+
#scale_x_discrete(labels=c())
scale_color_discrete(name="")+
theme_lz_ppt()+theme(axis.text.y=element_text(size=12))+theme(panel.grid.major.y = element_line(color = "grey95"))+
labs(title="Gender Gaps for Tenure-line Faculty",x="",y="")
```

# Departments with Significant Changes (2016~2021)

```{r dep prop.year table}
#n dep; filter out small dep that has skewed prt
n10dep<-data%>%group_by(Department)%>%summarise(cnt=n())%>% filter(cnt>10)%>%arrange(cnt)

#tenure prop by department
dep.Tprop<-data%>%filter(Department %in% n10dep$Department)%>%
  group_by(Year,Department, `Tenure Status`)%>%
  summarise(cnt=n_distinct(ID))%>%mutate(prt=percent(cnt/sum(cnt),digits = 0))%>%
  arrange(Department)%>%filter(`Tenure Status`=="Tenure Line")%>%
  select(-`Tenure Status`,-cnt)#have to remove cnt because only have the same value can be seen as one group; while cnt for different years vary, making departments not considered as the same

#year as cols
dep.wide<-dep.Tprop%>%pivot_wider(names_from = Year,values_from = prt)%>%mutate(Change=`2021`-`2016`,Average=mean(c(`2016`,`2017`,`2018`,`2019`,`2020`,`2021`)))%>%arrange(-Average)
```

```{r change_avg.dep}
#average and rank and change
average.dep<-dep.wide%>%select(Department,Average,Change)%>%arrange(-Average)%>% ungroup%>%mutate(`Rank of Average`=rank(-Average))#needs to ungroup before row_number or rank

#sig change>10%; list of departments
change.dep<-dep.wide%>%select(Department,`2016`,`2021`,Change)%>%
  filter(Change>0.1 | Change<(-0.1))%>%arrange(-Change) #have to use () for -0.1

change.avgrank<-merge(change.dep,average.dep)%>%select(Department,Change,Average)%>%arrange(-Change)
#condformat(change.dep) %>% rule_fill_gradient(Change, low=rgb(1,0,0),high=rgb(0,1,0))#low=rgb(1,0,0),high=rgb(0,1,0) good red-yellow/white-green

change.avgrank%>%formattable(list(
  Change=color_tile("red","yellow"),#from red to sth in between to yellow ultimately
  Average=color_bar("lightblue"),
  Change=formatter("span", style = ~ style(color = ifelse(Change >0, "darkgreen", "red")),
                    ~ icontext(ifelse(Change <0,"arrow-down", ifelse(Change>0.2,"thumbs-up","arrow-up")), Change))#,#the last change is to show values of change after styles
  #`Rank of Average`= formatter("span",style=x~style(color=ifelse(x<10,"darkgreen",ifelse(x>20,"red","grey"))))
))#%>%kable("html",caption = "Changes and Averages of Tenure-line Proportion for Departments")
```



# Trends for Individual Departments (Interactive Dashboard)

```{r dep order}
#order based on tenure prt -- exclude those without any tenure
dep.order.t<-data%>%group_by(Department,`Tenure Status`)%>%
  summarise(cnt=n_distinct(ID))%>%mutate(prt=percent(cnt/sum(cnt),digits = 0))%>%
  filter(`Tenure Status`=="Tenure Line")%>%arrange(prt)%>%
  mutate(dep.f=factor(Department))
#excluded in order
order.exclude<-data[( data$Department %in% dep.order.t$dep.f ) == FALSE,] %>%group_by(Department)%>%
  summarise(cnt=n_distinct(ID)) %>% arrange(cnt) %>% mutate(dep.xf=factor(Department))
#full order based on prt of tenured
dep.order<-c(order.exclude$dep.xf,dep.order.t$dep.f)
```

```{r function trend.dep}
mylist<-dep.order

data%>%filter(Department %in% mylist ) %>%
  group_by(Year,Department,`Tenure Status`)%>%
  summarise(cnt=n_distinct(ID))%>%mutate(prt=percent(cnt/sum(cnt),digits = 0))%>%
    filter(`Tenure Status`=="Tenure Line")%>%
  
  ggplot(aes(x=Year,y=prt,color=Department,group=Department))+geom_line()+
  scale_color_discrete(limits = dep.order[dep.order %in% mylist])+
  scale_y_continuous(labels=scales::percent_format(accuracy = 1))+
  theme_lz_ppt()+theme(axis.text.y=element_text(size=18))+theme(panel.grid.major.y = element_line(color = "grey95"))+
  labs(x="",y="",title=str_wrap("Selected Departments' Trends of Tenure-Line Faculty Proportion",40))
```

```{r function plot.dep}
#make department count as ndep
ndep<-data%>%group_by(Department)%>%summarise(cnt=n_distinct(ID))%>%arrange(-cnt)#

#plot for each group
plot.dep<-function(min.input,max.input){
  group<-ndep[ndep$cnt%in%seq(min.input,max.input,by=1),1]
  mylist<-group$Department

  data%>%filter(Department %in% mylist ) %>%
  group_by(Department,`Tenure Status`)%>%
  summarise(cnt=n_distinct(ID))%>%mutate(prt=percent(cnt/sum(cnt),digits = 0))%>%
  ggplot(aes(x=Department,y=prt,fill=`Tenure Status`))+geom_bar(stat = "identity")+
  scale_x_discrete(limits = dep.order[dep.order %in% mylist])+
  scale_fill_discrete(name="",labels=c("Non-tenure","Tenure"))+
  theme_lz_ppt()+geom_text(aes(label=prt),position = position_stack(),hjust=1, color="white",size=6)+
  coord_flip()+theme(axis.text.x = element_blank())+
  theme(axis.text.y=element_text(size = 14),plot.title = element_text(size=18))+
  labs(x="",y="",title=str_wrap( 
    paste0("Selected Departments (",min.input, "<Count of Faculty<",max.input,")"),70))}
```

```{r, include=FALSE}
#apply function
plot.dep(31,147)

plot.dep(21,30)

plot.dep(6,20)

plot.dep(0,5)
```
